---
title: "Regressive Autism Analysis"
author: "Antoine Beauchamp"
date: today
format: 
  html:
    theme: flatly
    code-fold: true
    toc: true
    collapsible: true
    code-tools: true
    syntax-highlighting: github
    code-copy: true
    df-print: kable
    echo: false
editor: visual
lightbox: auto
---

# Initialization

```{r packages}
#| echo: false

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(emmeans))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(patchwork))
suppressPackageStartupMessages(library(rcartocolor))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(viridis))
```

```{r functions}
#| echo: false


compute_group_summaries <- function(x, groups) {
  
  x_summary <- x %>% 
    select(ID, Language, Other) %>% 
    left_join(groups, by = c("Language", "Other")) %>% 
    group_by(Group) %>% 
    count() %>% 
    ungroup()
  
  x_tot <- tibble(Group = "Total",
                  n = sum(x_summary$n))
  
  x_summary <- bind_rows(x_summary, x_tot)
  
  return(x_summary)
  
}


#' Evaluate model and empirical marginal means
#'
#' @param x (tibble) Tibble with columns "y", "Language", "Other"
#'
#' @returns (list) 
evaluate_model <- function(x, type = "linear") {
  
  tab <- table(x$Language, x$Other)
  
  n_00 <- tab[1,1]
  n_10 <- tab[2,1]
  n_01 <- tab[1,2]
  n_11 <- tab[2,2]
  
  N_any <- n_10 + n_01 + n_11
  
  w_10 <- n_10 / N_any
  w_01 <- n_01 / N_any
  w_11 <- n_11 / N_any
  
  contrast_vectors <- list(
    Language_vs_None  = c(-1,  1,  0,  0),
    Other_vs_None     = c(-1,  0,  1,  0),
    Both_vs_None      = c(-1,  0,  0,  1),
    Other_vs_Language = c( 0, -1,  1,  0),
    Both_vs_Language  = c( 0, -1,  0,  1),
    Both_vs_Other     = c( 0,  0, -1,  1),
    Any_vs_None       = c(-1, w_10, w_01, w_11),
    Any_vs_Language   = c( 0, w_10 - 1, w_01, w_11),
    Any_vs_Other      = c( 0, w_10, w_01 - 1, w_11),
    Any_vs_Both       = c( 0, w_10, w_01, w_11 - 1)
  )
  
  if (type == "linear") {
    model <- lm(y ~ Language*Other, data = x)
    emm <- emmeans(model, ~ Language*Other) 
  } else if (type == "logistic") {
    model <- glm(y ~ Language*Other, data = x, family = "binomial")
    emm <- emmeans(model, ~ Language*Other, type = "response") 
  } else if (type == "mixed-effects") {
    model <- lmer(y ~ Language*Other + (1|ID), data = x)
    emm <- emmeans(model, ~ Language*Other) 
  } else {
    stop()
  }
  
  df_contrasts <- emm %>% 
    contrast(method = contrast_vectors) %>% 
    as_tibble() %>% 
    separate(contrast, into = c("Comparison", "Reference"), sep = "_vs_") %>% 
    mutate(q.value = p.adjust(p.value, method = "fdr"))
  
  return(list(model = model, emmeans = emm, contrasts = df_contrasts))
  
}


#' Generate heatmap of linear hypothesis test stats
#'
#' @param x (tibble) Tibble containing results of linear hypothesis tests
#' @param threshold (numeric scalar)
#'
#' @returns
contrasts_heatmap <- function(x, threshold_lwr = -log10(0.05), threshold_upr = 10) {
  
  groups <- c("None", "Language", "Other", "Both", "Any")
  
  df_groups_grid <- expand_grid(Reference = groups,
                                Comparison = groups) 
  
  x <- x %>%   
    select(Reference, Comparison, q.value) %>% 
    mutate(NLQ = -log10(q.value)) %>% 
    right_join(df_groups_grid, by = c("Reference", "Comparison")) %>% 
    filter(Comparison != "None", Reference != "Any") %>% 
    mutate(Reference = factor(Reference, levels = groups),
           Comparison = factor(Comparison, levels = groups)) %>% 
    mutate(NLQ = ifelse(NLQ > threshold_upr, threshold_upr, NLQ)) %>% 
    mutate(exclude = is.na(NLQ))
  
  plt <- ggplot(x, aes(x = Comparison, y = fct_rev(Reference), fill = NLQ, col = exclude)) + 
    geom_tile() +
    scale_fill_gradientn(
      colours = c("grey80", viridis::magma(256, begin = 0.2, end = 0.9)),
      values  = scales::rescale(c(threshold_lwr, seq(threshold_lwr + 0.001, threshold_upr, length.out = 256))),
      limits  = c(threshold_lwr, threshold_upr),
      oob     = scales::squish,        # forces NLQ <= thr to thr
      na.value = "white"
    ) +
    scale_colour_manual(values = c("grey50", "white"), guide = "none") + 
    scale_x_discrete(expand = expansion(), position = "top") +
    scale_y_discrete(expand = expansion(), position = "right") +
    labs(x = "Comparison Group",
         y = "Reference Group",
         fill = "-log10(q-value)") + 
    theme(axis.line.x.bottom = element_blank(),
          axis.line.x.top = element_line(colour = "grey50"),
          axis.line.y.left   = element_blank(),
          axis.line.y.right = element_line(colour = "grey50"),
          # legend.position = c(0.02, 0.02),   # bottom-left inside panel
          legend.position = "bottom",
          legend.justification = c(0, 0),
          legend.background = element_rect(
            fill = scales::alpha("white", 0.8),
            colour = NA
          )) +
    theme(axis.title = element_text(size = 9),
          axis.text = element_text(size = 9),
          legend.title = element_text(size = 9))
  
  return(list(data = x, plot = plt))
}


regression_probs <- function(model, groups, point_size = 3, ylims = NULL, ybreaks = NULL) {

x <- as_tibble(model$emmeans) %>% 
  left_join(groups, by = c("Language", "Other"))

plt <- ggplot(x, aes(x = Group, y = prob)) +
  geom_point(size = point_size) +
  geom_pointrange(aes(ymin = asymp.LCL,
                      ymax = asymp.UCL)) +
  labs(x = "Regression Type",
       y = "Probability") +
  theme_bw() +
  theme(title = element_text(size = 9, hjust = 0.5))

  if (!is.null(ylims)) {
    plt <- plt + coord_cartesian(ylim = ylims)
  }
  
  if (!is.null(ybreaks)) {
    plt <- plt + scale_y_continuous(breaks = ybreaks)
  }
  
  return(plt)

}


regression_scatter <- function(model, groups, point_size = 1, point_jitter_width = 0.3, 
                               point_col = "grey20", point_alpha_values = rep(0.5, 4),
                               crossbar_alpha = 0.1, crossbar_col = "red3",
                               ylims = NULL, ybreaks = NULL, seed = 123) {
  
  if (class(model$model) == "lm") {
    x <- model$model$model
  } else if (class(model$model) == "lmerModLmerTest") {
    x <- attributes(model$model)$frame  
  }
  
  x <- left_join(x, groups, by = c("Language", "Other"))
  
  x_summary <- model$emmeans %>% 
    as_tibble() %>% 
    left_join(groups, by = c("Language", "Other"))
  
  set.seed(seed)
  plt <- ggplot(x, aes(x = Group, y = y, alpha = Group)) +
    geom_jitter(size = point_size, width = point_jitter_width, height = 0, col = point_col) + 
    geom_crossbar(data = x_summary, 
                  mapping = aes(x = Group, y = emmean, ymin = lower.CL, ymax = upper.CL),
                  alpha = crossbar_alpha, col = crossbar_col, fill = crossbar_col) + 
    scale_alpha_manual(values = point_alpha_values, guide = "none") +
    labs(x = "Regression Type") + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  if (!is.null(ylims)) {
    plt <- plt + coord_cartesian(ylim = ylims)
  }
  
  if (!is.null(ybreaks)) {
    plt <- plt + scale_y_continuous(breaks = ybreaks)
  }
  
  return(plt)
  
}
```

```{r import}
# Path to processed data directory
data_dir <- "data/processed/"

output_dir <- "figures"

# Import processed data
data_file <- "regressive_autism_data.csv"
data_file <- file.path(data_dir, data_file)
df_regressive_autism <- read_csv(data_file, show_col_types = FALSE)

# Regression groups
regressive_group_lvls <- c("None", "Language", "Other", "Both")

# Groups grid
df_regressive_groups <- expand_grid(Language = c(TRUE, FALSE),
                                    Other = c(TRUE, FALSE)) %>% 
  mutate(Group = case_when(Language & !Other ~ "Language",
                           !Language & Other ~ "Other",
                           Language & Other ~ "Both",
                           !Language & !Other ~ "None")) %>% 
  mutate(Group = factor(Group, levels = regressive_group_lvls))
```

# Sample overview

The set of participants with ADI regression information breaks down as follows:

```{r}
compute_group_summaries(x = df_regressive_autism, groups = df_regressive_groups)
```

```{r}
#| echo: false
#| eval: false

df_regressive_autism %>% 
  filter(is.na(Language))
```

```{r}
#| echo: false
#| eval: false

df_regressive_autism %>% 
  filter(is.na(Other))
```

------------------------------------------------------------------------

# Adaptive function

The subset of participants with adaptive function scores:

```{r}
# Filter for participants with adaptive function scores
df_adaptive <- df_regressive_autism %>% 
  select(ID, Language, Other, AdaptiveScore) %>% 
  filter(!is.na(AdaptiveScore))

# Construct data frame for model
df_adaptive_lm <- df_adaptive %>% 
  select(ID, y = AdaptiveScore, 
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other))

compute_group_summaries(x = df_adaptive_lm, groups = df_regressive_groups)
```

```{r, fig.width=9}
#| label: adaptive-func-heatmap

# Evaluate model
list_adaptive <- evaluate_model(x = df_adaptive_lm)

# Generate heatmap from group contrasts
list_adaptive_heatmap <- contrasts_heatmap(x = list_adaptive$contrasts)

plt_adaptive_heatmap <- list_adaptive_heatmap$plot


plt_adaptive_scatter <- regression_scatter(model = list_adaptive, 
                                           groups = df_regressive_groups,
                                           point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                           ylims = c(20, 130), 
                                           ybreaks = seq(0, 200, by = 10))

plt_adaptive_scatter <- plt_adaptive_scatter +
  labs(y = "Adaptive Function Composite Score")

plt_adaptive <- plt_adaptive_scatter + plt_adaptive_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Adaptive Function vs. Regression Status")

outfile <- "adaptive_function.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_adaptive)
invisible(dev.off())

plt_adaptive
```

**Linear regression output:**

```{r}
summary(list_adaptive$model)
```

------------------------------------------------------------------------

# Full-scale IQ

The subset of participants with IQ scores:

```{r}
# Filter for participants with adaptive function scores
df_IQ <- df_regressive_autism %>% 
  select(ID, Language, Other, IQ) %>% 
  filter(!is.na(IQ)) %>% 
  filter(!is.na(Language), !is.na(Other))

df_IQ_lm <- df_IQ %>% 
  select(ID, y = IQ, Language, Other)  

compute_group_summaries(x = df_IQ_lm, groups = df_regressive_groups)
```

```{r}
#| fig-width: 9 

list_IQ <- evaluate_model(x = df_IQ_lm)

list_IQ_heatmap <- contrasts_heatmap(x = list_IQ$contrasts)

plt_IQ_heatmap <- list_IQ_heatmap$plot 

plt_IQ_scatter <- regression_scatter(model = list_IQ, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.3, 0.5, 0.5, 0.5),
                                     ylims = c(40, 160), 
                                     ybreaks = seq(0, 200, by = 10))

plt_IQ_scatter <- plt_IQ_scatter +
  labs(y = "Full-scale IQ")

plt_IQ <- plt_IQ_scatter + plt_IQ_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "IQ vs. Regression Status")

outfile <- "IQ.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_IQ)
invisible(dev.off())

plt_IQ
```

**Linear regression output:**

```{r}
summary(list_IQ$model)
```

------------------------------------------------------------------------

# ADOS

The subset of participants with ADOS scores:

```{r}
df_ADOS_CSS <- df_regressive_autism %>% 
  select(ID, Language, Other, ADOS_CSS) %>% 
  filter(!is.na(ADOS_CSS), !is.na(Language), !is.na(Other))

df_ADOS_OTS <- df_regressive_autism %>% 
  select(ID, Language, Other, ADOS_OTS) %>% 
  filter(!is.na(ADOS_OTS), !is.na(Language), !is.na(Other))

df_ADOS_CSS_n <- compute_group_summaries(x = df_ADOS_CSS, groups = df_regressive_groups)
df_ADOS_OTS_n <- compute_group_summaries(x = df_ADOS_OTS, groups = df_regressive_groups)

df_ADOS_n <- left_join(rename(df_ADOS_OTS_n, OTS = n),
                       rename(df_ADOS_CSS_n, CSS = n),
                       by = "Group")

df_ADOS_n
```

```{r}
#| echo: false
#| eval: false

df_ADOS_OTS %>% 
  mutate(ADOS_zero = ADOS_OTS == 0) %>% 
  group_by(ADOS_zero) %>% 
  count()
```

3,767 participants have overall total scores (OTS) and 2,867 participants have calibrated standard scores (CSS). Moreover, among the participants with OTS scores, 3,373 have non-zero values and 394 have zero values.

## ADOS CSS

```{r}
#| fig-width: 9 

# Filter for participants with adaptive function scores
df_ADOS_CSS_lm <- df_ADOS_CSS %>% 
  select(ID, y = ADOS_CSS, 
         Language, Other)  

list_ADOS_CSS <- evaluate_model(x = df_ADOS_CSS_lm)

list_ADOS_CSS_heatmap <- contrasts_heatmap(x = list_ADOS_CSS$contrasts)

plt_ADOS_CSS_heatmap <- list_ADOS_CSS_heatmap$plot 

plt_ADOS_CSS_scatter <- regression_scatter(model = list_ADOS_CSS, 
                                           groups = df_regressive_groups,
                                           point_alpha_values = c(0.1, 0.4, 0.4, 0.4),
                                           ylims = c(0, 11),
                                           ybreaks = seq(1, 10, by = 1)) 

plt_ADOS_CSS_scatter <- plt_ADOS_CSS_scatter +
  labs(y = "ADOS CSS") +
  theme(panel.grid.minor.y = element_blank())


plt_ADOS_CSS <- plt_ADOS_CSS_scatter + plt_ADOS_CSS_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "ADOS Calibrated Standard Score vs. Regression Status")

outfile <- "ADOS_CSS.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ADOS_CSS)
invisible(dev.off())

plt_ADOS_CSS
```

**Linear regression output:**

```{r}
summary(list_ADOS_CSS$model)
```

## ADOS OTS with zeros excluded

```{r}
#| fig-width: 9 

# Filter for participants with adaptive function scores
df_ADOS_OTS_lm <- df_ADOS_OTS %>% 
  filter(ADOS_OTS > 0) %>% 
  select(ID, y = ADOS_OTS, 
         Language, Other)  

list_ADOS_OTS <- evaluate_model(x = df_ADOS_OTS_lm)

list_ADOS_OTS_heatmap <- contrasts_heatmap(x = list_ADOS_OTS$contrasts)

plt_ADOS_OTS_heatmap <- list_ADOS_OTS_heatmap$plot 

plt_ADOS_OTS_scatter <- regression_scatter(model = list_ADOS_OTS, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.1, 0.4, 0.4, 0.4),
                                     ylims = c(0, 30), 
                                     ybreaks = seq(0, 200, by = 2))

plt_ADOS_OTS_scatter <- plt_ADOS_OTS_scatter +
  labs(y = "ADOS OTS")

plt_ADOS_OTS <- plt_ADOS_OTS_scatter + plt_ADOS_OTS_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "ADOS Overall Total Score vs. Regression Status")

outfile <- "ADOS_OTS.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ADOS_OTS)
invisible(dev.off())

plt_ADOS_OTS
```

**Linear regression output:**

```{r}
summary(list_ADOS_OTS$model)
```

## Analysis of ADOS OTS zero scores

```{r}
#| echo: false
#| eval: false

tmp <- df_regressive_autism |> 
  filter(!is.na(ADOS)) |> 
  mutate(ADOS_zero = ADOS == 0)


tmp %>% 
  group_by(ADOS_zero, Regressive_Strictly_Language) %>% 
  count()
```

```{r}
#| echo: false
#| eval: false

chisq.test(x = tmp$Regressive_Strictly_Language, y = tmp$ADOS_zero)
```

```{r}
#| echo: false
#| eval: false

chisq.test(x = tmp$Regressive_Strictly_Other, y = tmp$ADOS_zero)
```

```{r}
#| echo: false
#| eval: false

cols_regressive <- c("Regressive_Strictly_Language", "Regressive_Strictly_Other", 
                     "Regressive_Both", "Regressive_Any")
df_ADOS_zeros_chi2 <- tibble(regression = cols_regressive,
                             chi2 = 0, pval = 0)
for (i in 1:nrow(df_ADOS_zeros_chi2)) {
  
  x <- tmp[[cols_regressive[i]]]
  y <- tmp[["ADOS_zero"]]
  
  chisq_out <- chisq.test(x = x, y = y, simulate.p.value = TRUE, B = 5000)
  
  df_ADOS_zeros_chi2[[i, "chi2"]] <- chisq_out$statistic
  df_ADOS_zeros_chi2[[i, "pval"]] <- chisq_out$p.value
  
}

df_ADOS_zeros_chi2
```

```{r ados-plot}
#| echo: false
#| eval: false

annotation_y <- 0.95

# adaptive_titles <- c("Language regressive", 
#                      "Other skill regressive", 
#                      "Language and other skill regressive",
#                      "Language or other skill regressive")
ADOS_titles <- c("Language", 
                 "Other skill", 
                 "Language and other skill",
                 "Language or other skill")

list_ADOS_zero_plts <- vector(mode = "list", length = nrow(df_ADOS_zeros_chi2))
for (i in 1:length(list_ADOS_zero_plts)) {
  
  cols <- c("ID", cols_regressive[i], "ADOS_zero")
  df_ADOS_zero_plt <- tmp[,cols]
  colnames(df_ADOS_zero_plt) <- c("ID", "Regressive", "ADOS_zero")
  
  # df_ADOS_zero_plt <- df_ADOS_zero_plt %>% 
  #   group_by(Regressive, ADOS_zero) %>% 
  #   count() %>% 
  #   ungroup() %>% 
  #   mutate(ADOS_nonzero = !ADOS_zero)
  
  df_ADOS_zero_plt <- df_ADOS_zero_plt %>% 
    group_by(Regressive) %>% 
    mutate(n_per_group = n()) %>% 
    ungroup() %>% 
    group_by(Regressive, ADOS_zero) %>%  
    mutate(n_per_zero_per_group = n()) %>%  
    ungroup() %>% 
    mutate(prop_per_zero_per_group = n_per_zero_per_group/n_per_group) %>% 
    mutate(ADOS_nonzero = !ADOS_zero) %>% 
    select(Regressive, ADOS_nonzero, n_per_group, n_per_zero_per_group, prop_per_zero_per_group) %>% 
    distinct() %>% 
    arrange(Regressive, ADOS_nonzero)
  
  df_ADOS_zero_annotation <- df_ADOS_zeros_chi2[i, ] %>% 
    mutate(p.label = ifelse(pval < 0.001, 
                            "p < 0.001", paste0("p = ", round(pval, 3)))) %>% 
    select(p.label) %>% 
    mutate(x = 1.5, y = annotation_y + 0.04)
  
  plt_ADOS_zero <- ggplot(df_ADOS_zero_plt, aes(x = Regressive, fill = ADOS_nonzero, y = prop_per_zero_per_group)) + 
    geom_col(position = "dodge") +
    annotate(geom = "segment", x = FALSE, xend = TRUE, y = annotation_y, color = "grey40") +
    geom_text(data = df_ADOS_zero_annotation, aes(x = x, y = y, label = p.label),
              inherit.aes = FALSE, 
              size = 3.5, color = "grey30") +
    scale_x_discrete(labels = c("Non-regressive", "Regressive")) +
    scale_fill_discrete(labels = c("ADOS = 0", "ADOS > 0")) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
    labs(x = NULL,
         y = "Proportion of participants per regression group",
         fill = NULL, 
         title = ADOS_titles[i]) + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  
  if (i > 1) {
    plt_ADOS_zero <- plt_ADOS_zero +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }
  
  list_ADOS_zero_plts[[i]] <- plt_ADOS_zero
  
}

fig_ADOS_zero <- (list_ADOS_zero_plts[[1]] | list_ADOS_zero_plts[[2]] | list_ADOS_zero_plts[[3]] | list_ADOS_zero_plts[[4]]) +
  plot_layout(guides = "collect")

outfile <- "ADOS_zero_regression.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(10, "in"),
    height = unit(6, "in"))
print(fig_ADOS_zero)
dev.off()
```

```{r}
#| echo: false
#| eval: false

cols <- c("ID", cols_regressive[i], "ADOS_zero")
df_ADOS_zero_plt <- tmp[,cols]
colnames(df_ADOS_zero_plt) <- c("ID", "Regressive", "ADOS_zero")

df_ADOS_zero_plt %>% 
  group_by(Regressive) %>% 
  mutate(n_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Regressive, ADOS_zero) %>%  
  mutate(n_per_zero_per_group = n()) %>%  
  ungroup() %>% 
  mutate(prop_per_zero_per_group = n_per_zero_per_group/n_per_group) %>% 
  mutate(ADOS_nonzero = !ADOS_zero) %>% 
  select(Regressive, ADOS_nonzero, n_per_group, n_per_zero_per_group, prop_per_zero_per_group) %>% 
  distinct() %>% 
  arrange(Regressive, ADOS_nonzero)
```

```{r}
#| echo: false
#| eval: false

tmp_adaptive <- tmp %>% 
  filter(!is.na(AdaptiveScore)) %>% 
  mutate(ADOS_zero = ifelse(ADOS_zero, "Yes", "No"),
         ADOS_zero = factor(ADOS_zero))

model_ADOS_zero_adaptive <- summary(lm(AdaptiveScore ~ ADOS_zero, data = tmp_adaptive))

df_ADOS_zero_adaptive_summary <- group_summary(tmp_adaptive$AdaptiveScore,
                                               groups = tmp_adaptive$ADOS_zero)
df_ADOS_zero_adaptive_summary <- df_ADOS_zero_adaptive_summary %>% 
  as_tibble(rownames = "ADOS_zero") %>% 
  mutate(ADOS_zero = factor(ADOS_zero))


set.seed(123)
plt_ADOS_zero_adaptive <- ggplot(tmp_adaptive, aes(x = ADOS_zero, y = AdaptiveScore)) +
  geom_jitter(size = 1, width = 0.3, height = 0, alpha = 0.4, col = "grey20") + 
  geom_crossbar(data = df_ADOS_zero_adaptive_summary, 
                mapping = aes(x = ADOS_zero, y = mu, ymin = lower, ymax = upper),
                alpha = 0.1, col = "red3", fill = "red3") + 
  annotate(geom = "segment", x = "No", xend = "Yes", y = 135, color = "grey40") +
  annotate(geom = "text", x = 1.5, y = 140, label = "p < 0.001") + 
  scale_x_discrete(labels = c("ADOS > 0", "ADOS = 0")) +
  scale_y_continuous(breaks = seq(0, 200, by = 10)) +
  labs(x = "Binarized ADOS score",
       y = "Adaptive Function Composite Score") + 
  theme_bw() 

outfile <- "ADOS_zero_adaptive_function.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(6, "in"),
    height = unit(6, "in"))
print(plt_ADOS_zero_adaptive)
dev.off()
```

```{r}
#| echo: false
#| eval: false

tmp_IQ <- tmp %>% 
  filter(!is.na(IQ)) %>% 
  mutate(ADOS_zero = ifelse(ADOS_zero, "Yes", "No"),
         ADOS_zero = factor(ADOS_zero))

tmp_IQ %>% 
  group_by(ADOS_zero) %>% 
  count()
```

Only 14 people with 0 on ADOS and IQ scores.

```{r}
#| echo: false
#| eval: false

tmp_IQ %>% 
  filter(ADOS_zero == "Yes") %>% 
  select(IQ) %>% 
  arrange(desc(IQ))
```

The scores that do exist are low.

### Autism diagnosis by ADI-R sub-domain scores

```{r}
#| echo: false
#| eval: false

# Initialize data frame to store outputs
df_ADIR_subdomains <- df_regressive_autism %>% 
  select(ID)

# Path to ADI-R data
path_ADIR <- "data/raw/ADI-R/"

ADIR_subdomains <- c("Onset", "RRB", "Communication", "Social")

# Sub-domain cutoff files for ADI WPS
files_wps <- c("ADIWPS_ADIAFAB_cutoff_1.xlsx",
               "ADIWPS_ADIAFBEH_cutoff_3.xlsx",
               "ADIWPS_ADIAFCOM_cutoff_7-8.xlsx",
               "ADIWPS_ADIAFSOC_cutoff_10.xlsx")

# Sub-domain cutoff files for ADI 1995
files_1995 <- c("ADI1995_ADIAFAB_cutoff_1.xlsx",
                "ADI1995_ADIAFBEH_cutoff_3.xlsx",
                "ADI1995_ADIAFCOM_cutoff_7-8.xlsx",
                "ADI1995_ADIAFSOC_cutoff_10.xlsx")

# Iterate over sub-domains
for (i in 1:length(ADIR_subdomains)) {
  
  # Import WPS data
  file_wps <- file.path(path_ADIR, files_wps[i])
  df_wps_all <- read_excel(file_wps)
  
  # Import 1995 data
  file_1995 <- file.path(path_ADIR, files_1995[i])
  df_1995_all <- read_excel(file_1995)
  
  # Clean up WPS data
  df_wps_all <- df_wps_all %>% 
    mutate(cutoff_pass = numeric_value == 1) %>% 
    select(ID = indexid, cutoff_pass) %>% 
    mutate(version = "WPS")
  
  # Clean up 1995 data
  df_1995_all <- df_1995_all %>% 
    mutate(cutoff_pass = numeric_value == 1) %>% 
    select(ID = indexid, cutoff_pass) %>% 
    mutate(version = "1995")
  
  # Collate WPS and 1995 data
  df_cutoff_all <- bind_rows(df_wps_all, df_1995_all)
  
  # Remove duplicate entries
  df_cutoff_all <- df_cutoff_all %>% 
    distinct()
  
  # Identify participants with data from both versions
  ids_multiple_versions <- df_cutoff_all %>%
    select(ID, version) %>% 
    distinct() %>% 
    group_by(ID) %>% 
    count() %>% 
    filter(n > 1) %>% 
    pull(ID)
  
  # For participants with both versions, use 1995 version. 
  # Include all participants with only 1995 version
  df_cutoff_1995 <- bind_rows(
    df_cutoff_all %>% 
      filter(ID %in% ids_multiple_versions,
             version == "1995"),
    df_cutoff_all %>% 
      filter(!(ID %in% ids_multiple_versions),
             version == "1995"))
  
  # For participants with only WPS, use that
  df_cutoff_wps <- df_cutoff_all %>% 
    filter(!(ID %in% ids_multiple_versions),
           version == "WPS")
  
  # Combine 1995 and WPS data
  df_cutoff <- bind_rows(df_cutoff_1995, 
                         df_cutoff_wps)
  
  # Identify participants with multiple distinct values
  ids_multiple <- df_cutoff %>% 
    group_by(ID) %>% 
    count() %>% 
    filter(n > 1) %>% 
    pull(ID) %>% 
    unique()
  
  # For participants with both TRUE and FALSE, set to TRUE
  df_cutoff <- df_cutoff %>% 
    mutate(cutoff_pass = ifelse(ID %in% ids_multiple, TRUE, cutoff_pass)) %>% 
    distinct()
  
  # Subset columns and rename with sub-domain
  df_cutoff <- df_cutoff %>% 
    select(ID, cutoff_pass)
  colnames(df_cutoff)[2] <- ADIR_subdomains[i]
  
  # Join to final data frame
  df_ADIR_subdomains <- df_ADIR_subdomains %>% 
    left_join(df_cutoff, by = "ID")
  
}
```

```{r}
#| echo: false
#| eval: false

# Convert to long format
df_ADIR_subdomains_long <- df_ADIR_subdomains %>% 
  pivot_longer(cols = -ID, names_to = "subdomain", values_to = "pass")  

df_ADIR_subdomains_missing <- df_ADIR_subdomains_long %>% 
  mutate(missing = is.na(pass)) %>% 
  group_by(ID) %>% 
  summarise(n_missing = sum(missing)) %>% 
  ungroup()

df_ADIR_subdomains_missing %>% 
  filter(n_missing > 0) %>% 
  group_by(n_missing) %>% 
  count()
```

```{r}
#| echo: false
#| eval: false

ids_missing_subdomains <- df_ADIR_subdomains_missing %>% 
  filter(n_missing > 0) %>% 
  pull(ID)

df_regressive_autism %>% 
  filter(ID %in% ids_missing_subdomains)
```

```{r}
#| echo: false
#| eval: false

df_ADIR_subdomains_pass <- df_ADIR_subdomains_long %>% 
  group_by(ID) %>% 
  summarise(n_pass = sum(pass),
            n_pass_drop_na = sum(pass, na.rm = FALSE)) %>% 
  ungroup()
```

```{r}
#| echo: false
#| eval: false

# Filter all ADI participants who have ADOS
df_ADOS <- df_regressive_autism %>% 
  select(ID, contains("Regressive"), ADOS) %>% 
  filter(!is.na(ADOS))

# Filter for participants with ADOS = 0
df_ADOS_zeros <- df_ADOS %>% 
  filter(ADOS == 0)

df_ADOS_zeros <- df_ADOS_zeros %>% 
  left_join(df_ADIR_subdomains_pass, by = "ID")

df_ADOS_zeros %>% 
  group_by(n_pass) %>% 
  count()
```

```{r}
#| echo: false
#| eval: false

df_ADOS_zeros %>% 
  filter(is.na(n_pass)) %>% 
  select(ID, n_pass, n_pass_drop_na)
```

------------------------------------------------------------------------

# ADHD

```{r}
# file_ADHD <- "data/processed/ADHD/ADHD.csv"
# df_ADHD_only <- read_csv(file_ADHD, show_col_types = FALSE)
# 
# n_ADHD <- nrow(df_ADHD_only)
# n_intersect <- df_regressive_autism %>% 
#   filter(!is.na(ADHD)) %>% 
#   nrow()
# 
# tibble(`ADI-R` = n_ADIR, ADHD = n_ADHD, Intersection = n_intersect)
```

There are 1,304 participants with ADHD information:

```{r}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(ADHD) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(ADHD = ifelse(ADHD, "Yes", "No"))
```

Broken down by regression group:

```{r}
df_ADHD <- df_regressive_autism %>% 
  select(ID, Language, Other, ADHD) %>% 
  filter(!is.na(ADHD), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_ADHD, groups = df_regressive_groups)
```

```{r fig.width = 9}
df_ADHD_lr <- df_ADHD %>% 
  select(ID, y = ADHD, 
         Language, Other) 

list_ADHD <- evaluate_model(x = df_ADHD_lr, type = "logistic")


list_ADHD_heatmap <- contrasts_heatmap(x = list_ADHD$contrasts)

plt_ADHD_heatmap <- list_ADHD_heatmap$plot 

plt_ADHD_probs <- regression_probs(model = list_ADHD, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_ADHD <- plt_ADHD_probs + plt_ADHD_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "ADHD vs. Regression Status")

outfile <- "ADHD.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ADHD)
invisible(dev.off())

plt_ADHD
```

**Logistic regression output:**

```{r}
summary(list_ADHD$model)
```

```{r}
#| echo: false
#| eval: false

df_ADHD %>% 
  group_by(ADHD) %>% 
  summarise(N = n(), prop = N/nrow(.),
            .groups = "drop")
```

```{r}
#| echo: false
#| eval: false

df_ADHD_lr %>% 
  group_by(Language, Other) %>% 
  mutate(N_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Language, Other, y) %>% 
  mutate(N = n()) %>% 
  ungroup() %>% 
  select(-ID) %>% 
  distinct() %>% 
  mutate(prop = N/N_per_group) %>% 
  select(Language, Other, y, N_per_group, N, prop) %>% 
  arrange(Language, Other, y) %>% 
  filter(y)
```

------------------------------------------------------------------------

# Anxiety

There are 1,080 participants with anxiety information:

```{r}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Anxiety) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Anxiety = ifelse(Anxiety, "Yes", "No"))
```

Broken down by regression group:

```{r}
df_anxiety <- df_regressive_autism %>% 
  select(ID, Language, Other, Anxiety) %>% 
  filter(!is.na(Anxiety), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_anxiety, groups = df_regressive_groups)
```

```{r fig.width = 9}
df_anxiety_lr <- df_anxiety %>% 
  select(ID, y = Anxiety, 
         Language, Other) 

list_anxiety <- evaluate_model(x = df_anxiety_lr, type = "logistic")


list_anxiety_heatmap <- contrasts_heatmap(x = list_anxiety$contrasts)

plt_anxiety_heatmap <- list_anxiety_heatmap$plot 

plt_anxiety_probs <- regression_probs(model = list_anxiety, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_anxiety <- plt_anxiety_probs + plt_anxiety_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Anxiety vs. Regression Status")

outfile <- "anxiety.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_anxiety)
invisible(dev.off())

plt_anxiety
```

**Logistic regression output:**

```{r}
summary(list_anxiety$model)
```

------------------------------------------------------------------------

# Depression


There are 832 participants with depression information:

```{r}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Depression) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Depression = ifelse(Depression, "Yes", "No"))
```


Broken down by regression group:

```{r}
df_depression <- df_regressive_autism %>% 
  select(ID, Language, Other, Depression) %>% 
  filter(!is.na(Depression), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_depression, groups = df_regressive_groups)
```


```{r fig.width = 9}
df_depression_lr <- df_depression %>% 
  select(ID, y = Depression, 
         Language, Other) 

list_depression <- evaluate_model(x = df_depression_lr, type = "logistic")


list_depression_heatmap <- contrasts_heatmap(x = list_depression$contrasts)

plt_depression_heatmap <- list_depression_heatmap$plot 

plt_depression_probs <- regression_probs(model = list_depression, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_depression <- plt_depression_probs + plt_depression_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Depression vs. Regression Status")

outfile <- "depression.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_depression)
invisible(dev.off())

plt_depression
```

------------------------------------------------------------------------

# Sleep

There are 767 participants with sleep information:

```{r}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Sleep) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Sleep = ifelse(Sleep, "Yes", "No"))
```


Broken down by regression group:

```{r}
df_sleep <- df_regressive_autism %>% 
  select(ID, Language, Other, Sleep) %>% 
  filter(!is.na(Sleep), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_sleep, groups = df_regressive_groups)
```


```{r fig.width = 9}
df_sleep_lr <- df_sleep %>% 
  select(ID, y = Sleep, 
         Language, Other) 

list_sleep <- evaluate_model(x = df_sleep_lr, type = "logistic")


list_sleep_heatmap <- contrasts_heatmap(x = list_sleep$contrasts)

plt_sleep_heatmap <- list_sleep_heatmap$plot 

plt_sleep_probs <- regression_probs(model = list_sleep, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_sleep <- plt_sleep_probs + plt_sleep_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Sleep Problems vs. Regression Status")

outfile <- "sleep.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_sleep)
invisible(dev.off())

plt_sleep
```


------------------------------------------------------------------------

# Seizures

There are 454 participants with seizure information:

```{r}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Seizure) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Seizure = ifelse(Seizure, "Yes", "No"))
```

Broken down by regression group:

```{r}
df_seizures <- df_regressive_autism %>% 
  select(ID, Language, Other, Seizure, Seizure_Date, DOB, ADIR_Age) %>% 
  filter(!is.na(Seizure), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_seizures, groups = df_regressive_groups)
```

```{r fig.width = 9}
df_seizures_lr <- df_seizures %>% 
  select(ID, y = Seizure, 
         Language, Other) 

list_seizures <- evaluate_model(x = df_seizures_lr, type = "logistic")


list_seizures_heatmap <- contrasts_heatmap(x = list_seizures$contrasts)

plt_seizures_heatmap <- list_seizures_heatmap$plot 

plt_seizures_probs <- regression_probs(model = list_seizures, 
                                       groups = df_regressive_groups,
                                       ybreaks = seq(0, 1, by = 0.1),
                                       ylims = c(0, 1))

plt_seizures <- plt_seizures_probs + plt_seizures_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Seizures vs. Regression Status")

outfile <- "seizures_overall.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_seizures)
invisible(dev.off())

plt_seizures
```

## Seizures in three age bins

The distributions of ages among participants with seizure information:

```{r fig.width = 9}
df_seizures_age <- df_seizures %>% 
  mutate(Seizure_Date = ifelse(Seizure_Date == "1900-01-01", NA, Seizure_Date)) %>% 
  mutate(Seizure_Date = as.Date(Seizure_Date)) %>% 
  mutate(Seizure_Age = time_length(interval(DOB, Seizure_Date), "years")) %>% 
  mutate(Seizure_Age = ifelse(is.na(Seizure_Age), ADIR_Age, Seizure_Age)) %>%
  filter(Seizure_Age > 0)

ggplot(df_seizures_age, aes(x = Seizure_Age, fill = Seizure)) + 
  geom_histogram(position = "dodge", binwidth = 2) +
  labs(x = "Age") + 
  scale_x_continuous(breaks = seq(0, 50, 5)) + 
  scale_y_continuous(breaks = seq(0, 100, 10)) + 
  scale_fill_discrete(labels = c("No", "Yes")) + 
  theme_bw()
```

If we split the seizure ages into three bins, the numbers are as follows:

```{r}
df_seizures_binned <- df_seizures_age %>% 
  mutate(AgeBin = case_when(Seizure_Age < 5 ~ "< 5",
                            Seizure_Age >= 5 & Seizure_Age < 12 ~ "5-12",
                            Seizure_Age >= 12 ~ ">= 12"))

df_seizures_binned <- df_seizures_binned %>% 
  filter(!is.na(AgeBin))

df_seizures_binned <- df_seizures_binned %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", "5-12", ">= 12")))

df_seizures_binned %>% 
  group_by(AgeBin) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(`Age Bin` = c("Under 5", "5 to 12", "Over 12")) %>% 
  select(`Age Bin`, n)
```

The association between seizures and regression status in each of the three bins:

```{r}
df_seizures_binned_lr <- df_seizures_binned %>% 
  select(ID, y = Seizure, 
         Language, Other, AgeBin) %>% 
  filter(!is.na(Language), !is.na(Other))

list_seizures_binned_inputs <- split(df_seizures_binned_lr, f = df_seizures_binned_lr$AgeBin)

list_seizures_binned <- map(list_seizures_binned_inputs, .f = evaluate_model, type = "logistic")

```

```{r fig.width = 9}
df_seizures_binned_plt <- map_dfr(list_seizures_binned, 
                                  .f = function(x) {as_tibble(x[["emmeans"]])},
                                  .id = "AgeBin")

df_seizures_binned_plt <- df_seizures_binned_plt %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", "5-12", ">= 12"))) %>% 
  mutate(AgeLabel = case_when(AgeBin == "< 5" ~ "Under 5",
                              AgeBin == "5-12" ~ "5 to 12",
                              AgeBin == ">= 12" ~ "Over 12"),
         AgeLabel = factor(AgeLabel, levels = c("Under 5", "5 to 12", "Over 12")))

plt_lvls <- c("None", "Language", "Other", "Both")

plt_seizures_probs_binned <- ggplot(df_seizures_binned_plt, 
                                    aes(x = interaction(Language, Other),
                                        y = prob)) + 
  # geom_point(position = position_dodge(width = 0.2)) +
  # geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
  #                 position = position_dodge(width = 0.3)) +
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL)) +
  facet_grid(.~AgeLabel) + 
  coord_cartesian(ylim = c(0, 1)) + 
  scale_x_discrete(labels = plt_lvls) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) + 
  labs(x = "Regression Type",
       y = "Probability of seizures") +
  theme_bw()


df_seizures_binned_heatmap <- map_dfr(list_seizures_binned,
                                      .f = function(x) {contrasts_heatmap(x = x[["contrasts"]])[["data"]]}, 
                                      .id = "AgeBin")

df_seizures_binned_heatmap <- df_seizures_binned_heatmap %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", "5-12", ">= 12"))) %>% 
  mutate(AgeLabel = case_when(AgeBin == "< 5" ~ "Under 5",
                              AgeBin == "5-12" ~ "5 to 12",
                              AgeBin == ">= 12" ~ "Over 12"),
         AgeLabel = factor(AgeLabel, levels = c("Under 5", "5 to 12", "Over 12")))

threshold_lwr <- -log10(0.05)
threshold_upr <- 10

plt_seizures_heatmap_binned <- ggplot(df_seizures_binned_heatmap,
                                      aes(x = Comparison, y = fct_rev(Reference), fill = NLQ, col = exclude)) + 
  geom_tile() +
  facet_grid(.~AgeLabel) +
  scale_fill_gradientn(
    colours = c("grey80", viridis::magma(256, begin = 0.2, end = 0.9)),
    values  = scales::rescale(c(threshold_lwr, seq(threshold_lwr + 0.001, threshold_upr, length.out = 256))),
    limits  = c(threshold_lwr, threshold_upr),
    oob     = scales::squish,        # forces NLQ <= thr to thr
    na.value = "white"
  ) +
  scale_colour_manual(values = c("grey50", "white"), guide = "none") + 
  scale_x_discrete(expand = expansion(), position = "top") +
  scale_y_discrete(expand = expansion(), position = "right") +
  labs(x = "Comparison Group",
       y = "Reference Group",
       fill = "-log10(q-value)") + 
  theme(axis.line.x.bottom = element_blank(),
        axis.line.x.top = element_line(colour = "grey50"),
        axis.line.y.left   = element_blank(),
        axis.line.y.right = element_line(colour = "grey50"),
        legend.position = "bottom")
        # legend.position = c(0.02, 0.02),   # bottom-left inside panel
        # legend.justification = c(0, 0),
        # legend.background = element_rect(
        #   fill = scales::alpha("white", 0.8),
        #   colour = NA
        # ))


plt_seizures_binned <- plt_seizures_probs_binned / plt_seizures_heatmap_binned

outfile <- "seizures_age_binned.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(6, "in"))
print(plt_seizures_binned)
invisible(dev.off())

plt_seizures_binned
```

## Controlling for age

```{r}
#| echo: false
#| eval: false

df_seizures_lr_age <- df_seizures_age %>%
  select(ID, y = Seizure, 
         Language, Other, Age = Seizure_Age) %>% 
  filter(!is.na(Language), !is.na(Other), !is.na(Age)) 

df_age_quantiles <- tibble(probs = seq(0, 1, by = 0.01))
df_age_quantiles$Age <- quantile(x = df_seizures_lr_age$Age, probs = df_age_quantiles$probs)

ggplot(df_age_quantiles, aes(x = Age, y = probs)) + 
  geom_line() +
  scale_x_continuous(breaks = seq(0, 50, by = 5)) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) + 
  theme_bw()
```

```{r}
#| echo: false
#| eval: false

library(splines)

df_seizures_lr_age <- df_seizures_lr_age %>% 
  filter(Age <= 25) %>% 
  mutate(Age_Centered = Age - mean(Age))

# mod <- glm(y ~ Age_Centered + Language*Other,
#            data = df_seizures_lr_age,
#            family = "binomial")

mod <- glm(y ~ ns(Age_Centered, df = 3) + Language*Other,
           data = df_seizures_lr_age,
           family = "binomial")

summary(mod)
```

```{r}
#| echo: false
#| eval: false

range(df_seizures_lr_age$Age)
```

```{r}
#| echo: false
#| eval: false

age_mean <- mean(df_seizures_lr_age$Age)

age_seq <- seq(1, 30, by = 1)

age_seq_centered <- age_seq - age_mean

df_predict_input <- expand_grid(Age_Centered = age_seq_centered,
                                Language = c(FALSE, TRUE),
                                Other = c(FALSE, TRUE))

pred_link <- predict(mod, newdata = df_predict_input, type = "link", se.fit = TRUE)

df_predict_input$OR <- pred_link$fit
df_predict_input$OR_SE  <- pred_link$se.fit

df_predict_input <- df_predict_input %>% 
  mutate(OR_lwr = OR - 1.96*OR_SE,
         OR_upr = OR + 1.96*OR_SE) 


df_predict_input <- df_predict_input %>% 
  mutate(prob = plogis(OR),
         prob_lwr = plogis(OR_lwr),
         prob_upr = plogis(OR_upr))

df_predict_input <- df_predict_input %>% 
  mutate(group = case_when(!Language & !Other ~ "None",
                           Language & !Other ~ "Language",
                           !Language & Other ~ "Other",
                           Language & Other ~ "Both"),
         group = factor(group, levels = c("None", "Language", "Other", "Both")))
```

```{r}
#| echo: false
#| eval: false

df_plot <- df_predict_input %>% 
  filter(group %in% c("None", "Both"))

ggplot(df_plot, aes(x = Age_Centered + age_mean, y = OR, fill = group)) + 
  geom_ribbon(mapping = aes(ymin = OR_lwr, ymax = OR_upr),
              alpha = 0.3) +
  geom_line() +
  scale_x_continuous(breaks = seq(-100, 100, by = 5)) + 
  scale_y_continuous(breaks = seq(-10, 10, by = 1)) + 
  labs(x = "Age",
       y = "log(Odds Ratio)") + 
  theme_bw()
```

```{r}
#| echo: false
#| eval: false

ggplot(df_plot, aes(x = Age_Centered + age_mean, y = prob, fill = group)) + 
  geom_ribbon(mapping = aes(ymin = prob_lwr, ymax = prob_upr),
              alpha = 0.3) +
  geom_line() +
  scale_x_continuous(breaks = seq(-100, 100, by = 5)) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) + 
  labs(x = "Age",
       y = "Probability") + 
  theme_bw()
```

```{r}
#| echo: false
#| eval: false

emm <- emmeans(mod, ~ Language*Other | Age_Centered, at = list(Age_Centered = age_seq_centered))


emm_contrast <- contrast(emm,
                         method = list("Both vs None" = c(-1, 0, 0, 1)))

df_contrasts <- as_tibble(emm_contrast)
df_contrasts <- df_contrasts %>%
  mutate(lower.CL = estimate - 1.96 * SE,
         upper.CL = estimate + 1.96 * SE)

df_contrasts <- df_contrasts %>% 
  mutate(OR = exp(estimate),
         OR_lower = exp(lower.CL),
         OR_upper = exp(upper.CL))

ggplot(df_contrasts, aes(x = Age_Centered + age_mean, y = estimate)) + 
  geom_ribbon(mapping = aes(ymin = lower.CL, ymax = upper.CL),
              alpha = 0.3) + 
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", col = "red") +
  theme_bw()
```

## Controlling for IQ

```{r}
#| echo: false
#| eval: false

df_seizures_lr_IQ <- df_seizures %>%
  select(ID, y = Seizure, 
         Language = Regressive_Language, 
         Other = Regressive_Other, Age = Seizure_Age, IQ) %>% 
  filter(!is.na(Language), !is.na(Other), !is.na(Age), !is.na(IQ)) 

nrow(df_seizures_lr_IQ)
```

```{r}
#| echo: false
#| eval: false

df_seizures_lr_IQ %>% 
  group_by(Language, Other) %>% 
  mutate(N_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Language, Other, y) %>% 
  mutate(N = n()) %>% 
  ungroup() %>% 
  select(-ID) %>% 
  distinct() %>% 
  mutate(prop = N/N_per_group) %>% 
  select(Language, Other, y, N_per_group, N, prop) %>% 
  arrange(Language, Other, y) %>% 
  filter(y) %>% 
  distinct()
```

------------------------------------------------------------------------

# Prematurity

There are 703 participants with prematurity information:

```{r}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Prematurity) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Prematurity = ifelse(Prematurity, "Yes", "No"))
```


Broken down by regression group:

```{r}
df_prematurity <- df_regressive_autism %>% 
  select(ID, Language, Other, Prematurity) %>% 
  filter(!is.na(Prematurity), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_prematurity, groups = df_regressive_groups)
```


```{r fig.width = 9}
df_prematurity_lr <- df_prematurity %>% 
  select(ID, y = Prematurity, 
         Language, Other) 

list_prematurity <- evaluate_model(x = df_prematurity_lr, type = "logistic")


list_prematurity_heatmap <- contrasts_heatmap(x = list_prematurity$contrasts)

plt_prematurity_heatmap <- list_prematurity_heatmap$plot 

plt_prematurity_probs <- regression_probs(model = list_prematurity, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_prematurity <- plt_prematurity_probs + plt_prematurity_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Prematurity vs. Regression Status")

outfile <- "prematurity.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_prematurity)
invisible(dev.off())

plt_prematurity
```


------------------------------------------------------------------------

# Sensory processing

To evaluate sensory processing we used the **Short Sensory Profile (SSP)**. The subset of participants with SSP scores breaks down as follows:

```{r}
df_SSP <- df_regressive_autism %>%
  select(ID, Language, Other, contains("SSP")) %>% 
  filter(!is.na(SSP_TOTAL)) %>% 
  filter(!is.na(Language), !is.na(Other))

# Construct data frame for model
df_SSP_lm <- df_SSP %>% 
  select(ID, y = SSP_TOTAL, 
         Language, Other) 

compute_group_summaries(x = df_SSP_lm, groups = df_regressive_groups)
```

## SSP Total Score

```{r}
#| fig-width: 9 

list_SSP_TOT <- evaluate_model(x = df_SSP_lm)

list_SSP_TOT_heatmap <- contrasts_heatmap(x = list_SSP_TOT$contrasts)

plt_SSP_TOT_heatmap <- list_SSP_TOT_heatmap$plot 

plt_SSP_TOT_scatter <- regression_scatter(model = list_SSP_TOT, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(50, 200),
                                     ybreaks = seq(0, 200, by = 10))

plt_SSP_TOT_scatter <- plt_SSP_TOT_scatter +
  labs(y = "SSP Total Score")

plt_SSP_TOT <- plt_SSP_TOT_scatter + plt_SSP_TOT_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SSP Total vs. Regression Status")

outfile <- "SSP_TOT.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SSP_TOT)
invisible(dev.off())

plt_SSP_TOT
```

## SSP Auditory Filtering

```{r}
#| fig-width: 9 

# Construct data frame for model
df_SSP_AUD_FILT_lm <- df_SSP %>% 
  select(ID, y = SSP_AUD_FILTER, 
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other))

list_SSP_AUD_FILT <- evaluate_model(x = df_SSP_AUD_FILT_lm)

list_SSP_AUD_FILT_heatmap <- contrasts_heatmap(x = list_SSP_AUD_FILT$contrasts)

plt_SSP_AUD_FILT_heatmap <- list_SSP_AUD_FILT_heatmap$plot 

plt_SSP_AUD_FILT_scatter <- regression_scatter(model = list_SSP_AUD_FILT, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 35),
                                     ybreaks = seq(0, 200, by = 5))

plt_SSP_AUD_FILT_scatter <- plt_SSP_AUD_FILT_scatter +
  labs(y = "SSP Auditory Filtering Score")

plt_SSP_AUD_FILT <- plt_SSP_AUD_FILT_scatter + plt_SSP_AUD_FILT_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SSP Auditory Filtering vs. Regression Status")

outfile <- "SSP_AUD_FILT.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SSP_AUD_FILT)
invisible(dev.off())

plt_SSP_AUD_FILT
```

## SSP Visual-Auditory

```{r}
#| fig-width: 9 

# Construct data frame for model
df_SSP_VIS_AUD_lm <- df_SSP %>% 
  select(ID, y = SSP_VIS_AUD, 
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other))

list_SSP_VIS_AUD <- evaluate_model(x = df_SSP_VIS_AUD_lm)

list_SSP_VIS_AUD_heatmap <- contrasts_heatmap(x = list_SSP_VIS_AUD$contrasts)

plt_SSP_VIS_AUD_heatmap <- list_SSP_VIS_AUD_heatmap$plot 

plt_SSP_VIS_AUD_scatter <- regression_scatter(model = list_SSP_VIS_AUD, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 30),
                                     ybreaks = seq(0, 200, by = 5))

plt_SSP_VIS_AUD_scatter <- plt_SSP_VIS_AUD_scatter +
  labs(y = "SSP Visual/Auditory Score")

plt_SSP_VIS_AUD <- plt_SSP_VIS_AUD_scatter + plt_SSP_VIS_AUD_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SSP Visual/Auditory vs. Regression Status")

outfile <- "SSP_VIS_AUD.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SSP_VIS_AUD)
invisible(dev.off())

plt_SSP_VIS_AUD
```

------------------------------------------------------------------------

# Socialization

To evaluate socialization we used the **Social Responsiveness Scale (SRS)**. The subset of participants with SRS scores breaks down as follows:

```{r}
df_SRS <- df_regressive_autism %>%
  select(ID, Language, Other, contains("SRS")) %>% 
  filter(!is.na(SRS_Total)) %>% 
  filter(!is.na(Language), !is.na(Other))

compute_group_summaries(x = df_SRS, groups = df_regressive_groups)
```

## SRS Total Score

```{r}
#| fig-width: 9 

# Construct data frame for model
df_SRS_lm <- df_SRS %>% 
  select(ID, y = SRS_Total, 
         Language, Other) 

list_SRS <- evaluate_model(x = df_SRS_lm)

list_SRS_heatmap <- contrasts_heatmap(x = list_SRS$contrasts)

plt_SRS_heatmap <- list_SRS_heatmap$plot 

plt_SRS_scatter <- regression_scatter(model = list_SRS, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ybreaks = seq(0, 200, by = 10))

plt_SRS_scatter <- plt_SRS_scatter +
  labs(y = "SRS Total Score")

plt_SRS <- plt_SRS_scatter + plt_SRS_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Social Responsiveness Questionnaire (SRS) vs. Regression Status")

outfile <- "SRS.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SRS)
invisible(dev.off())

plt_SRS
```

## Custom Total Score

The custom total score is the sum of Social Awareness, Social Cognition, Social Communication and Social Motivation, excluding repetitive behaviours.

```{r}
#| fig-width: 9 

df_SRS_custom_lm <- df_SRS %>% 
  mutate(y = SRS_SocialAware + SRS_SocialCog + SRS_SocialComm + SRS_SocialMotiv) %>% 
  select(ID, y, Language, Other) %>% 
  filter(!is.na(y))

list_SRS_custom <- evaluate_model(x = df_SRS_custom_lm)

list_SRS_custom_heatmap <- contrasts_heatmap(x = list_SRS_custom$contrasts)

plt_SRS_custom_heatmap <- list_SRS_custom_heatmap$plot 

plt_SRS_custom_scatter <- regression_scatter(model = list_SRS_custom, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ybreaks = seq(0, 1000, by = 20))

plt_SRS_custom_scatter <- plt_SRS_custom_scatter +
  labs(y = "SRS Custom Total Score")

plt_SRS_custom <- plt_SRS_custom_scatter + plt_SRS_custom_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Social Responsiveness Questionnaire (SRS) vs. Regression Status")

outfile <- "SRS_custom.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SRS_custom)
invisible(dev.off())

plt_SRS_custom
```

------------------------------------------------------------------------

# Language

To evaluate language, we used the **Children's Communication Checklist (CCC)**. The subset of participants with CCC scores breaks down as follows:

```{r}
df_language <- df_regressive_autism %>%
  select(ID, Language, Other, contains("CCC"), IQ)

df_language <- df_language %>% 
  mutate(Structural_1 = CCC_Speech + CCC_Syntax + CCC_Semantics + CCC_Coherence,
         Pragmatic_1 = CCC_Inapp_Init + CCC_Context + CCC_NonVerbalComm) %>% 
  mutate(Structural_2 = CCC_Speech + CCC_Syntax + CCC_Semantics,
         Pragmatic_2 = CCC_Inapp_Init + CCC_Context + CCC_NonVerbalComm + CCC_Coherence) 

df_language <- df_language %>% 
  filter(!is.na(Language), !is.na(Other), !is.na(Structural_1))

compute_group_summaries(x = df_language, groups = df_regressive_groups)
```

## Structural Language

The structural language score is the sum of Speech, Syntax and Semantics. Additionally, in version 1, Coherence is counted towards Structural. In version 2, Coherence is counted towards Pragmatic.

```{r}
#| fig-width: 9 

# Construct data frame for model
df_lang_v1_struct_lm <- df_language %>% 
  select(ID, y = Structural_1, 
         Language, Other) 

list_lang_v1_struct <- evaluate_model(x = df_lang_v1_struct_lm)

list_lang_v1_struct_heatmap <- contrasts_heatmap(x = list_lang_v1_struct$contrasts)

plt_lang_v1_struct_heatmap <- list_lang_v1_struct_heatmap$plot 

plt_lang_v1_struct_scatter <- regression_scatter(model = list_lang_v1_struct, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 60), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v1_struct_scatter <- plt_lang_v1_struct_scatter +
  labs(y = "Structural Language Score")

plt_lang_v1_struct <- plt_lang_v1_struct_scatter + plt_lang_v1_struct_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Structural Language (v1) vs. Regression Status")

outfile <- "lang_v1_struct.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v1_struct)
invisible(dev.off())

plt_lang_v1_struct
```

```{r}
#| fig-width: 9 

# Construct data frame for model
df_lang_v2_struct_lm <- df_language %>% 
  select(ID, y = Structural_2, 
         Language, Other) 

list_lang_v2_struct <- evaluate_model(x = df_lang_v2_struct_lm)

list_lang_v2_struct_heatmap <- contrasts_heatmap(x = list_lang_v2_struct$contrasts)

plt_lang_v2_struct_heatmap <- list_lang_v2_struct_heatmap$plot 

plt_lang_v2_struct_scatter <- regression_scatter(model = list_lang_v2_struct, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 60), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v2_struct_scatter <- plt_lang_v2_struct_scatter +
  labs(y = "Structural Language Score")

plt_lang_v2_struct <- plt_lang_v2_struct_scatter + plt_lang_v2_struct_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Structural Language (v2) vs. Regression Status")

outfile <- "lang_v2_struct.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v2_struct)
invisible(dev.off())

plt_lang_v2_struct
```

## Pragmatic Language

In version 1, Coherence is counted towards Structural. In version 2, Coherence is counted towards Pragmatic.

```{r}
#| fig-width: 9 

# Conprag data frame for model
df_lang_v1_prag_lm <- df_language %>% 
  select(ID, y = Pragmatic_1, 
         Language, Other) 

list_lang_v1_prag <- evaluate_model(x = df_lang_v1_prag_lm)

list_lang_v1_prag_heatmap <- contrasts_heatmap(x = list_lang_v1_prag$contrasts)

plt_lang_v1_prag_heatmap <- list_lang_v1_prag_heatmap$plot 

plt_lang_v1_prag_scatter <- regression_scatter(model = list_lang_v1_prag, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 50), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v1_prag_scatter <- plt_lang_v1_prag_scatter +
  labs(y = "Pragmatic Language Score")

plt_lang_v1_prag <- plt_lang_v1_prag_scatter + plt_lang_v1_prag_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Pragmatic Language (v1) vs. Regression Status")

outfile <- "lang_v1_prag.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v1_prag)
invisible(dev.off())

plt_lang_v1_prag
```

```{r}
#| fig-width: 9 

# Construct data frame for model
df_lang_v2_prag_lm <- df_language %>% 
  select(ID, y = Pragmatic_2, 
         Language, Other) 

list_lang_v2_prag <- evaluate_model(x = df_lang_v2_prag_lm)

list_lang_v2_prag_heatmap <- contrasts_heatmap(x = list_lang_v2_prag$contrasts)

plt_lang_v2_prag_heatmap <- list_lang_v2_prag_heatmap$plot 

plt_lang_v2_prag_scatter <- regression_scatter(model = list_lang_v2_prag, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 50), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v2_prag_scatter <- plt_lang_v2_prag_scatter +
  labs(y = "Pragmatic Language Score")

plt_lang_v2_prag <- plt_lang_v2_prag_scatter + plt_lang_v2_prag_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Pragmatic Language (v2) vs. Regression Status")

outfile <- "lang_v2_prag.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v2_prag)
invisible(dev.off())

plt_lang_v2_prag
```

## SIDC

```{r}
#| echo: false
#| eval: false

# Construct data frame for model
df_SIDC_lm <- df_language %>% 
  select(ID, y = CCC_SIDC, IQ,
         Language = Regressive_Language, 
         Other = Regressive_Other) %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  filter(!is.na(y))

# Evaluate model
list_SIDC <- evaluate_model(x = df_SIDC_lm)
summary(list_SIDC$model)
```

```{r}
#| echo: false
#| eval: false

cols <- c("Regressive_Language", "Regressive_Other")

cols_new <- cols %>% 
  str_remove("Regressive_")  

cols <- c("ID", cols, "CCC_SIDC")
cols_new <- c("ID", cols_new, "SIDC")

plt_lvls <- c("None", "Language", "Other", "Both")

df_SIDC_plt <- df_language %>% 
  filter(!is.na(Regressive_Language), !is.na(Regressive_Other)) %>% 
  filter(!is.na(CCC_SIDC))

df_SIDC_plt <- df_SIDC_plt[,cols]
colnames(df_SIDC_plt) <- cols_new

df_SIDC_plt <- df_SIDC_plt %>% 
  mutate(Group = case_when(Language & !Other ~ "Language",
                           !Language & Other ~ "Other",
                           Language & Other ~ "Both",
                           !Language & !Other ~ "None")) %>% 
  mutate(Group = factor(Group, levels = plt_lvls))

df_SIDC_plt_summary <- group_summary(x = df_SIDC_plt$SIDC, 
                                     groups = df_SIDC_plt$Group)
df_SIDC_plt_summary <- df_SIDC_plt_summary %>% 
  as_tibble(rownames = "Group") %>% 
  mutate(Group = factor(Group, levels = plt_lvls))

set.seed(123)
plt_SIDC_scatter <- ggplot(df_SIDC_plt, aes(x = Group, y = SIDC, alpha = Group)) +
  geom_jitter(size = 1, width = 0.3, height = 0, col = "grey20") + 
  geom_crossbar(data = df_SIDC_plt_summary, 
                mapping = aes(x = Group, y = mu, ymin = lower, ymax = upper),
                alpha = 0.1, col = "red3", fill = "red3") + 
  # coord_cartesian(ylim = c(20, 130)) + 
  scale_x_discrete() +
  scale_y_continuous(breaks = seq(-200, 200, by = 5)) +
  scale_alpha_manual(values = c(0.2, 0.4, 0.4, 0.4), guide = "none") + 
  labs(x = "Regression Type",
       y = "Social Interaction Deviance Composite",
       title = "Social Interaction Deviance Composite (SIDC) vs. Regression Status") + 
  theme_bw() +
  theme(title = element_text(size = 9, hjust = 0.5))

outfile <- "language_SIDC_scatter.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(6, "in"),
    height = unit(4, "in"))
print(plt_SIDC_scatter)
dev.off()
```

```{r}
#| echo: false
#| eval: false

# Generate heatmap from group contrasts
list_SIDC_heatmap <- contrasts_heatmap(x = list_SIDC$contrasts)

plt_SIDC_heatmap <- list_SIDC_heatmap$plot +
  labs(title = "SIDC vs. Regression Status")

outfile <- "language_SIDC_heatmap.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(4, "in"),
    height = unit(4, "in"))
print(plt_SIDC_heatmap)
dev.off()
```

```{r}
#| echo: false
#| eval: false

df_SIDC_IQ_lm <- df_SIDC_lm %>% 
  filter(!is.na(IQ))

mod <- lm(y ~ Language*Other + IQ, data = df_SIDC_IQ_lm)
summary(mod)
```

------------------------------------------------------------------------

# Repetitive behaviours

To evaluate repetitive behaviours, we used the **RBS-R**. The subset of participants with RBS-R scores breaks down as follows:

```{r}
file <- "data/processed/RBS-R/RBS.csv"
df_rbs <- read_csv(file, show_col_types = FALSE)

df_rbs %>% 
  select(ID, y = RBSR_RBSCPT) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

## RBS-R original sub-domains

### Compulsive Behaviour

```{r fig.width = 9}
df_rbs_cpt <- df_rbs %>% 
  select(ID, y = RBSR_RBSCPT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_cpt <- evaluate_model(x = df_rbs_cpt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_cpt_heatmap <- contrasts_heatmap(x = list_rbs_cpt$contrasts)

plt_rbs_cpt_heatmap <- list_rbs_cpt_heatmap$plot


plt_rbs_cpt_scatter <- regression_scatter(model = list_rbs_cpt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          ylims = c(0, 25))

plt_rbs_cpt_scatter <- plt_rbs_cpt_scatter +
labs(y = "RBS-R Compulsive Behaviour")

plt_rbs_cpt <- plt_rbs_cpt_scatter + plt_rbs_cpt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Compulsive Behaviour vs. Regression Status")

outfile <- "rbs_cpt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_cpt)
invisible(dev.off())

plt_rbs_cpt
```

### Restricted Behaviour

```{r fig.width = 9}
df_rbs_rst <- df_rbs %>% 
  select(ID, y = RBSR_RBSRST) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_rst <- evaluate_model(x = df_rbs_rst, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_rst_heatmap <- contrasts_heatmap(x = list_rbs_rst$contrasts)

plt_rbs_rst_heatmap <- list_rbs_rst_heatmap$plot


plt_rbs_rst_scatter <- regression_scatter(model = list_rbs_rst, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_rst_scatter <- plt_rbs_rst_scatter +
labs(y = "RBS-R Restricted Behaviour")

plt_rbs_rst <- plt_rbs_rst_scatter + plt_rbs_rst_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Restricted Behaviour vs. Regression Status")

outfile <- "rbs_rst.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_rst)
invisible(dev.off())

plt_rbs_rst
```

### Ritualistic Behaviour

```{r fig.width = 9}
df_rbs_rtt <- df_rbs %>% 
  select(ID, y = RBSR_RBSRTT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_rtt <- evaluate_model(x = df_rbs_rtt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_rtt_heatmap <- contrasts_heatmap(x = list_rbs_rtt$contrasts)

plt_rbs_rtt_heatmap <- list_rbs_rtt_heatmap$plot


plt_rbs_rtt_scatter <- regression_scatter(model = list_rbs_rtt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_rtt_scatter <- plt_rbs_rtt_scatter +
labs(y = "RBS-R Ritual Behaviour")

plt_rbs_rtt <- plt_rbs_rtt_scatter + plt_rbs_rtt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Ritual Behaviour vs. Regression Status")

outfile <- "rbs_rtt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_rtt)
invisible(dev.off())

plt_rbs_rtt
```

### Self-Injurious Behaviour

```{r fig.width = 9}
df_rbs_sit <- df_rbs %>% 
  select(ID, y = RBSR_RBSSIT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_sit <- evaluate_model(x = df_rbs_sit, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_sit_heatmap <- contrasts_heatmap(x = list_rbs_sit$contrasts)

plt_rbs_sit_heatmap <- list_rbs_sit_heatmap$plot


plt_rbs_sit_scatter <- regression_scatter(model = list_rbs_sit, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_sit_scatter <- plt_rbs_sit_scatter +
labs(y = "RBS-R Self-Injurious Behaviour")

plt_rbs_sit <- plt_rbs_sit_scatter + plt_rbs_sit_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Self-Injurious Behaviour vs. Regression Status")

outfile <- "rbs_sit.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_sit)
invisible(dev.off())

plt_rbs_sit
```

### Sameness Behaviour

```{r fig.width = 9}
df_rbs_smt <- df_rbs %>% 
  select(ID, y = RBSR_RBSSMT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_smt <- evaluate_model(x = df_rbs_smt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_smt_heatmap <- contrasts_heatmap(x = list_rbs_smt$contrasts)

plt_rbs_smt_heatmap <- list_rbs_smt_heatmap$plot


plt_rbs_smt_scatter <- regression_scatter(model = list_rbs_smt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_smt_scatter <- plt_rbs_smt_scatter +
labs(y = "RBS-R Sameness Behaviour")

plt_rbs_smt <- plt_rbs_smt_scatter + plt_rbs_smt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Sameness Behaviour vs. Regression Status")

outfile <- "rbs_smt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_smt)
invisible(dev.off())

plt_rbs_smt
```

### Stereotyped Behaviour

```{r fig.width = 9}
df_rbs_stt <- df_rbs %>% 
  select(ID, y = RBSR_RBSSTT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_stt <- evaluate_model(x = df_rbs_stt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_stt_heatmap <- contrasts_heatmap(x = list_rbs_stt$contrasts)

plt_rbs_stt_heatmap <- list_rbs_stt_heatmap$plot


plt_rbs_stt_scatter <- regression_scatter(model = list_rbs_stt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_stt_scatter <- plt_rbs_stt_scatter +
labs(y = "RBS-R Stereotyped Behaviour")

plt_rbs_stt <- plt_rbs_stt_scatter + plt_rbs_stt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Stereotyped Behaviour vs. Regression Status")

outfile <- "rbs_stt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_stt)
invisible(dev.off())

plt_rbs_stt
```

## RBS-R five-factor model

In the five-factor model, the Ritualistic and Sameness sub-domains are summed together. The remaining sub-domains are left as is.

```{r fig.width = 9}
df_rbs_rit_smt <- df_rbs %>% 
  mutate(y = RBSR_RBSRTT + RBSR_RBSSMT) %>% 
  select(ID, y) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_rit_smt <- evaluate_model(x = df_rbs_rit_smt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_rit_smt_heatmap <- contrasts_heatmap(x = list_rbs_rit_smt$contrasts)

plt_rbs_rit_smt_heatmap <- list_rbs_rit_smt_heatmap$plot


plt_rbs_rit_smt_scatter <- regression_scatter(model = list_rbs_rit_smt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_rit_smt_scatter <- plt_rbs_rit_smt_scatter +
labs(y = "RBS-R Ritualistic/Sameness Behaviour")

plt_rbs_rit_smt <- plt_rbs_rit_smt_scatter + plt_rbs_rit_smt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Ritualistic/Sameness Behaviour vs. Regression Status")

outfile <- "rbs_5_factor_rit_smt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_rit_smt)
invisible(dev.off())

plt_rbs_rit_smt
```

## RBS-R four-factor model

In the five-factor model, the Compulsive, Ritualistic and Sameness sub-domains are summed together. The remaining sub-domains are left as is.

```{r fig.width = 9}
df_rbs_cpt_rit_smt <- df_rbs %>% 
  mutate(y = RBSR_RBSCPT + RBSR_RBSRTT + RBSR_RBSSMT) %>% 
  select(ID, y) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_cpt_rit_smt <- evaluate_model(x = df_rbs_cpt_rit_smt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_cpt_rit_smt_heatmap <- contrasts_heatmap(x = list_rbs_cpt_rit_smt$contrasts)

plt_rbs_cpt_rit_smt_heatmap <- list_rbs_cpt_rit_smt_heatmap$plot


plt_rbs_cpt_rit_smt_scatter <- regression_scatter(model = list_rbs_cpt_rit_smt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_cpt_rit_smt_scatter <- plt_rbs_cpt_rit_smt_scatter +
labs(y = "RBS-R Compulsive/Ritualistic/Sameness Behaviour")

plt_rbs_cpt_rit_smt <- plt_rbs_cpt_rit_smt_scatter + plt_rbs_cpt_rit_smt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Compulsive/Ritualistic/Sameness Behaviour vs. Regression Status") 

outfile <- "rbs_4_factor_cpt_rit_smt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_cpt_rit_smt)
invisible(dev.off())

plt_rbs_cpt_rit_smt
```
