---
title: "Regressive Autism Analysis"
author: "Antoine Beauchamp"
date: today
format: 
  html:
    theme: flatly
    code-fold: true
    toc: true
    collapsible: true
    code-tools: true
    syntax-highlighting: github
    code-copy: true
    df-print: kable
    echo: false
    embed-resources: true
editor: visual
lightbox: auto
---

# Initialization

```{r packages}
#| echo: false

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(emmeans))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(patchwork))
suppressPackageStartupMessages(library(rcartocolor))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(viridis))
```

```{r functions}
#| echo: false


#' Compute regression group summaries
#'
#' @param x (tibble) Data frame with regression status information
#' @param groups (tibble) Data frame containing group labels
#'
#' @returns (tibble) Tibble with group summary data
compute_group_summaries <- function(x, groups) {
  
  # Compute group numbers
  x_summary <- x %>% 
    select(ID, Language, Other) %>% 
    left_join(groups, by = c("Language", "Other")) %>% 
    group_by(Group) %>% 
    count() %>% 
    ungroup()
  
  # Compute total sample size
  x_tot <- tibble(Group = "Total", n = sum(x_summary$n))
  
  # Combine group numbers with total
  x_summary <- bind_rows(x_summary, x_tot)
  
  return(x_summary)
  
}


#' Evaluate model and empirical marginal means
#'
#' @param x (tibble) Tibble with columns "y", "Language", "Other"
#'
#' @returns (list) 
evaluate_model <- function(x, type = "linear") {
  
  # Confusion matrix of Language and Other vars
  tab <- table(x$Language, x$Other)
  
  # Extract matrix cells
  n_00 <- tab[1,1]
  n_10 <- tab[2,1]
  n_01 <- tab[1,2]
  n_11 <- tab[2,2]
  
  # Total number of participants with any regression
  N_any <- n_10 + n_01 + n_11
  
  # Proportions of any regression formed by each group
  w_10 <- n_10 / N_any
  w_01 <- n_01 / N_any
  w_11 <- n_11 / N_any
  
  # Define contrast vectors
  contrast_vectors <- list(
    Language_vs_None  = c(-1,  1,  0,  0),
    Other_vs_None     = c(-1,  0,  1,  0),
    Both_vs_None      = c(-1,  0,  0,  1),
    Other_vs_Language = c( 0, -1,  1,  0),
    Both_vs_Language  = c( 0, -1,  0,  1),
    Both_vs_Other     = c( 0,  0, -1,  1),
    Any_vs_None       = c(-1, w_10, w_01, w_11),
    Any_vs_Language   = c( 0, w_10 - 1, w_01, w_11),
    Any_vs_Other      = c( 0, w_10, w_01 - 1, w_11),
    Any_vs_Both       = c( 0, w_10, w_01, w_11 - 1)
  )
  
  # Evaluate model and contrasts
  if (type == "linear") {
    model <- lm(y ~ Language*Other, data = x)
    emm <- emmeans(model, ~ Language*Other) 
  } else if (type == "logistic") {
    model <- glm(y ~ Language*Other, data = x, family = "binomial")
    emm <- emmeans(model, ~ Language*Other, type = "response") 
  } else if (type == "mixed-effects") {
    model <- lmer(y ~ Language*Other + (1|ID), data = x)
    emm <- emmeans(model, ~ Language*Other) 
  } else {
    stop()
  }
  
  # Combine information for contrasts and adjust for MC
  df_contrasts <- emm %>% 
    contrast(method = contrast_vectors) %>% 
    as_tibble() %>% 
    separate(contrast, into = c("Comparison", "Reference"), sep = "_vs_") %>% 
    mutate(q.value = p.adjust(p.value, method = "fdr"))
  
  return(list(model = model, emmeans = emm, contrasts = df_contrasts, type = type))
  
}


#' Generate heatmap of linear hypothesis test stats
#'
#' @param x (tibble) Tibble containing results of linear hypothesis tests
#' @param threshold_lwr (numeric scalar) Lower threshold for colour scale
#' @param threshold_upr (numeric scalar) Upper threshold for colour scale
#'
#' @returns (list) List containing ggplot and data used to plot
contrasts_heatmap <- function(x, threshold_lwr = -log10(0.05), threshold_upr = 10) {
  
  groups <- c("None", "Language", "Other", "Both", "Any")
  
  df_groups_grid <- expand_grid(Reference = groups,
                                Comparison = groups) 
  
  x <- x %>%   
    select(Reference, Comparison, q.value) %>% 
    mutate(NLQ = -log10(q.value)) %>% 
    right_join(df_groups_grid, by = c("Reference", "Comparison")) %>% 
    filter(Comparison != "None", Reference != "Any") %>% 
    mutate(Reference = factor(Reference, levels = groups),
           Comparison = factor(Comparison, levels = groups)) %>% 
    mutate(NLQ = ifelse(NLQ > threshold_upr, threshold_upr, NLQ)) %>% 
    mutate(exclude = is.na(NLQ))
  
  plt <- ggplot(x, aes(x = Comparison, y = fct_rev(Reference), fill = NLQ, col = exclude)) + 
    geom_tile() +
    scale_fill_gradientn(
      colours = c("grey80", viridis::magma(256, begin = 0.2, end = 0.9)),
      values  = scales::rescale(c(threshold_lwr, seq(threshold_lwr + 0.001, threshold_upr, length.out = 256))),
      limits  = c(threshold_lwr, threshold_upr),
      oob     = scales::squish,        # forces NLQ <= thr to thr
      na.value = "white"
    ) +
    scale_colour_manual(values = c("grey50", "white"), guide = "none") + 
    scale_x_discrete(expand = expansion(), position = "top") +
    scale_y_discrete(expand = expansion(), position = "right") +
    labs(x = "Comparison Group",
         y = "Reference Group",
         fill = "-log10(q-value)") + 
    theme(axis.line.x.bottom = element_blank(),
          axis.line.x.top = element_line(colour = "grey50"),
          axis.line.y.left   = element_blank(),
          axis.line.y.right = element_line(colour = "grey50"),
          # legend.position = c(0.02, 0.02),   # bottom-left inside panel
          legend.position = "bottom",
          legend.justification = c(0, 0),
          legend.background = element_rect(
            fill = scales::alpha("white", 0.8),
            colour = NA
          )) +
    theme(axis.title = element_text(size = 9),
          axis.text = element_text(size = 9),
          legend.title = element_text(size = 9))
  
  return(list(data = x, plot = plt))
}


regression_probs <- function(model, groups, point_size = 3, ylims = NULL, ybreaks = NULL) {

x <- as_tibble(model$emmeans) %>% 
  left_join(groups, by = c("Language", "Other"))

plt <- ggplot(x, aes(x = Group, y = prob)) +
  geom_point(size = point_size) +
  geom_pointrange(aes(ymin = asymp.LCL,
                      ymax = asymp.UCL)) +
  labs(x = "Regression Type",
       y = "Probability") +
  theme_bw() +
  theme(title = element_text(size = 9, hjust = 0.5))

  if (!is.null(ylims)) {
    plt <- plt + coord_cartesian(ylim = ylims)
  }
  
  if (!is.null(ybreaks)) {
    plt <- plt + scale_y_continuous(breaks = ybreaks)
  }
  
  return(plt)

}


regression_scatter <- function(model, groups, point_size = 1, point_jitter_width = 0.3, 
                               point_col = "grey20", point_alpha_values = rep(0.5, 4),
                               crossbar_alpha = 0.1, crossbar_col = "red3",
                               ylims = NULL, ybreaks = NULL, seed = 123) {
  
  if (class(model$model) == "lm") {
    x <- model$model$model
  } else if (class(model$model) == "lmerModLmerTest") {
    x <- attributes(model$model)$frame  
  }
  
  x <- left_join(x, groups, by = c("Language", "Other"))
  
  x_summary <- model$emmeans %>% 
    as_tibble() %>% 
    left_join(groups, by = c("Language", "Other"))
  
  set.seed(seed)
  plt <- ggplot(x, aes(x = Group, y = y, alpha = Group)) +
    geom_jitter(size = point_size, width = point_jitter_width, height = 0, col = point_col) + 
    geom_crossbar(data = x_summary, 
                  mapping = aes(x = Group, y = emmean, ymin = lower.CL, ymax = upper.CL),
                  alpha = crossbar_alpha, col = crossbar_col, fill = crossbar_col) + 
    scale_alpha_manual(values = point_alpha_values, guide = "none") +
    labs(x = "Regression Type") + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  if (!is.null(ylims)) {
    plt <- plt + coord_cartesian(ylim = ylims)
  }
  
  if (!is.null(ybreaks)) {
    plt <- plt + scale_y_continuous(breaks = ybreaks)
  }
  
  return(plt)
  
}
```

```{r import}
# Path to processed data directory
data_dir <- "data/processed/"

output_dir <- "figures"

# Import processed data
data_file <- "regressive_autism_data.csv"
data_file <- file.path(data_dir, data_file)
df_regressive_autism <- read_csv(data_file, show_col_types = FALSE)

# Regression groups
regressive_group_lvls <- c("None", "Language", "Other", "Both")

# Groups grid
df_regressive_groups <- expand_grid(Language = c(TRUE, FALSE),
                                    Other = c(TRUE, FALSE)) %>% 
  mutate(Group = case_when(Language & !Other ~ "Language",
                           !Language & Other ~ "Other",
                           Language & Other ~ "Both",
                           !Language & !Other ~ "None")) %>% 
  mutate(Group = factor(Group, levels = regressive_group_lvls))
```

# Sample overview

The set of participants with ADI regression information breaks down as follows:

```{r sample-numbers}
compute_group_summaries(x = df_regressive_autism, 
                        groups = df_regressive_groups)
```

```{r sample-language-missing}
#| echo: false
#| eval: false

df_regressive_autism %>% 
  filter(is.na(Language))
```

```{r sample-other-missing}
#| echo: false
#| eval: false

df_regressive_autism %>% 
  filter(is.na(Other))
```

------------------------------------------------------------------------

# Demographics

```{r}
mssng_file <- "data/MSSNG_DB7_metadata.tsv"
df_mssng_metadata <- as_tibble(read.csv(mssng_file, sep = "\t"))

df_mssng_metadata <- df_mssng_metadata %>% 
  select(ID = Individual.ID, Sex_MSSNG = Sex, 
         Ancestry = Predicted.ancestry, 
         Type = Family.type, Cohort) %>% 
  mutate(Sex_MSSNG = ifelse(Sex_MSSNG == "male", "M", "F"))

df_demographics <- df_regressive_autism %>% 
  select(ID, Language, Other, ADIR_Age, Sex) %>% 
  left_join(df_mssng_metadata, by = "ID") %>% 
  mutate(Sex = ifelse(is.na(Sex), Sex_MSSNG, Sex)) %>% 
  select(-Sex_MSSNG) %>% 
  mutate(Sex = ifelse(Sex == "M", "Male", "Female")) %>% 
  mutate(Regression = Language | Other) %>%
  mutate(Regression = ifelse(Regression, "Regressive", "Non-regressive"))

```

## Age

```{r, fig.width=9}
df_age_lm <- df_regressive_autism %>% 
  filter(!is.na(ADIR_Age)) %>% 
  select(ID, Language, Other, y = ADIR_Age) %>% 
  filter(!is.na(Language), !is.na(Other))


# Evaluate model
list_age <- evaluate_model(x = df_age_lm)

# Generate heatmap from group contrasts
list_age_heatmap <- contrasts_heatmap(x = list_age$contrasts)

plt_age_heatmap <- list_age_heatmap$plot


plt_age_scatter <- regression_scatter(model = list_age, 
                                      groups = df_regressive_groups,
                                      ybreaks = seq(0, 200, by = 5), 
                                      point_alpha_values = c(0.25, 0.5, 0.5, 0.5))

plt_age_scatter <- plt_age_scatter +
  labs(y = "Age")

plt_age <- plt_age_scatter + plt_age_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Age vs. Regression Status")

outfile <- "age.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_age)
invisible(dev.off())

plt_age
```

```{r}
df_age_groups <- df_demographics %>% 
  filter(!is.na(ADIR_Age)) %>% 
  filter(!is.na(Regression)) %>% 
  group_by(Regression) %>% 
  summarise(Age_mean = round(mean(ADIR_Age), 2),
            age_sd = round(sd(ADIR_Age), 2)) %>% 
  ungroup() %>% 
  mutate(Label = paste0(Age_mean, " (", age_sd, ")")) %>% 
  select(Regression, Label) %>% 
  pivot_wider(names_from = "Regression", values_from = "Label")

df_age_total <- df_demographics %>% 
  filter(!is.na(ADIR_Age)) %>% 
  filter(!is.na(Regression)) %>% 
  summarise(Age_mean = round(mean(ADIR_Age), 2),
            age_sd = round(sd(ADIR_Age), 2)) %>% 
  ungroup() %>% 
  mutate(Total = paste0(Age_mean, " (", age_sd, ")")) %>% 
  select(Total)

df_age_stats <- bind_cols(df_age_groups, df_age_total) %>%
  mutate(Measure = "Age", Group = NA) %>%
  mutate(Total = as.character(Total)) %>% 
  select(Measure, Group, `Non-regressive`, Regressive, Total)

df_age_stats
```

## Age of regression onset

```{r age-of-onset}
file <- "data/processed/Onset/age_of_onset.csv"
df_onset <- read_csv(file, show_col_types = FALSE)

age_onset_mean <- df_onset %>% 
  pull(Age_Onset) %>% 
  mean()

message("Mean age of onset: ", round(age_onset_mean, 1), " months")
```

------------------------------------------------------------------------

## Sex

```{r}
df_sex_total <- df_demographics %>% 
  filter(!is.na(Regression)) %>% 
  mutate(n_total = nrow(.)) %>% 
  group_by(Sex) %>% 
  summarise(Total = n()) %>% 
  ungroup()

df_sex_groups <- df_demographics %>%
  filter(!is.na(Regression)) %>% 
  select(Sex, Regression) %>% 
  group_by(Regression) %>% 
  mutate(n_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Regression, Sex) %>% 
  mutate(n = n(),
         prop = n/n_per_group) %>% 
  ungroup() %>% 
  select(Regression, Sex, n, prop) %>% 
  distinct() %>% 
  mutate(percent = round(prop*100, 1)) %>% 
  mutate(Label = paste0(n, " (", percent, "%)")) %>% 
  select(Regression, Sex, Label) %>% 
  pivot_wider(id_cols = "Sex", names_from = "Regression", values_from = "Label")

df_sex_stats <- df_sex_groups %>% 
  left_join(df_sex_total, by = "Sex") %>% 
  mutate(Sex = ifelse(is.na(Sex), "Missing", Sex)) %>% 
  mutate(Measure = "Sex at birth (N, %)") %>%
  mutate(Total = as.character(Total)) %>% 
  select(Measure, Group = Sex, `Non-regressive`, Regressive, Total)

df_sex_stats
```

```{r, fig.width = 9}
# df_sex_lr <- df_sex %>%
#   mutate(y = Sex == "F")
# 
# list_sex <- evaluate_model(x = df_sex_lr, type = "logistic")
# 
# 
# list_sex_heatmap <- contrasts_heatmap(x = list_sex$contrasts)
# 
# plt_sex_heatmap <- list_sex_heatmap$plot 
# 
# plt_sex_probs <- regression_probs(model = list_sex, 
#                                    groups = df_regressive_groups,
#                                    ybreaks = seq(0, 1, by = 0.1),
#                                    ylims = c(0, 0.5))
# 
# plt_sex_probs <- plt_sex_probs + 
#   labs(y = "Probability (Female)")
# 
# plt_sex <- plt_sex_probs + plt_sex_heatmap +
#   plot_layout(widths = c(0.7, 0.3)) +
#   plot_annotation(title = "Sex vs. Regression Status")
# 
# outfile <- "sex.pdf"
# outfile <- file.path(output_dir, outfile)
# pdf(file = outfile, 
#     width = unit(10, "in"),
#     height = unit(4.5, "in"))
# print(plt_sex)
# invisible(dev.off())
# 
# plt_sex
```

## Ancestry

```{r}
df_ancestry_total <- df_demographics %>% 
  filter(!is.na(Regression)) %>% 
  mutate(n_total = nrow(.)) %>% 
  group_by(Ancestry) %>% 
  summarise(Total = n()) %>% 
  ungroup()

df_ancestry_groups <- df_demographics %>%
  filter(!is.na(Regression)) %>% 
  select(Ancestry, Regression) %>% 
  group_by(Regression) %>% 
  mutate(n_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Regression, Ancestry) %>% 
  mutate(n = n(),
         prop = n/n_per_group) %>% 
  ungroup() %>% 
  select(Regression, Ancestry, n, prop) %>% 
  distinct() %>% 
  mutate(percent = round(prop*100, 1)) %>% 
  mutate(Label = paste0(n, " (", percent, "%)")) %>% 
  select(Regression, Ancestry, Label) %>% 
  pivot_wider(id_cols = "Ancestry", names_from = "Regression", values_from = "Label")

df_ancestry_stats <- df_ancestry_groups %>% 
  left_join(df_ancestry_total, by = "Ancestry") %>% 
  mutate(Ancestry = ifelse(is.na(Ancestry), "Missing", Ancestry)) %>% 
  mutate(Measure = "Predicted Ancestry (N, %)") %>%
  mutate(Total = as.character(Total)) %>% 
  select(Measure, Group = Ancestry, `Non-regressive`, Regressive, Total)

df_ancestry_stats
```

## Family Type

```{r}
df_type_total <- df_demographics %>% 
  filter(!is.na(Regression)) %>% 
  mutate(n_total = nrow(.)) %>% 
  group_by(Type) %>% 
  summarise(Total = n()) %>% 
  ungroup()

df_type_groups <- df_demographics %>%
  filter(!is.na(Regression)) %>% 
  select(Type, Regression) %>% 
  group_by(Regression) %>% 
  mutate(n_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Regression, Type) %>% 
  mutate(n = n(),
         prop = n/n_per_group) %>% 
  ungroup() %>% 
  select(Regression, Type, n, prop) %>% 
  distinct() %>% 
  mutate(percent = round(prop*100, 1)) %>% 
  mutate(Label = paste0(n, " (", percent, "%)")) %>% 
  select(Regression, Type, Label) %>% 
  pivot_wider(id_cols = "Type", names_from = "Regression", values_from = "Label")

df_type_stats <- df_type_groups %>% 
  left_join(df_type_total, by = "Type") %>% 
  mutate(Type = ifelse(is.na(Type), "Missing", Type)) %>% 
  mutate(Measure = "Family Type (N, %)") %>%
  mutate(Total = as.character(Total)) %>% 
  select(Measure, Group = Type, `Non-regressive`, Regressive, Total)

df_type_stats
```

## Cohort

```{r}
df_cohort_total <- df_demographics %>% 
  filter(!is.na(Regression)) %>% 
  mutate(n_total = nrow(.)) %>% 
  group_by(Cohort) %>% 
  summarise(Total = n()) %>% 
  ungroup() %>% 
  arrange(Cohort)

df_cohort_groups <- df_demographics %>%
  filter(!is.na(Regression)) %>% 
  select(Cohort, Regression) %>% 
  group_by(Regression) %>% 
  mutate(n_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Regression, Cohort) %>% 
  mutate(n = n(),
         prop = n/n_per_group) %>% 
  ungroup() %>% 
  select(Regression, Cohort, n, prop) %>% 
  distinct() %>% 
  mutate(percent = round(prop*100, 1)) %>% 
  mutate(Label = paste0(n, " (", percent, "%)")) %>% 
  select(Regression, Cohort, Label) %>% 
  pivot_wider(id_cols = "Cohort", names_from = "Regression", values_from = "Label") %>% 
  arrange(Cohort)

df_cohort_stats <- df_cohort_groups %>% 
  left_join(df_cohort_total, by = "Cohort") %>% 
  mutate(Cohort = ifelse(is.na(Cohort), "Missing", Cohort)) %>% 
  mutate(Measure = "MSSNG Cohort (N, %)") %>%
  mutate(Total = as.character(Total)) %>% 
  select(Measure, Group = Cohort, `Non-regressive`, Regressive, Total)

df_cohort_stats
```

## Demographics Table 1

```{r}
df_demographics_stats <- bind_rows(df_age_stats, 
                                   df_sex_stats,
                                   df_ancestry_stats,
                                   df_type_stats,
                                   df_cohort_stats)

outfile <- "demographics_table_1.csv"
outfile <- file.path("data", outfile)
write_csv(df_demographics_stats, outfile)
```

------------------------------------------------------------------------

# Adaptive function

## Composite Score

The subset of participants with adaptive function scores:

```{r adaptive-function}
# Filter for participants with adaptive function scores
df_adaptive <- df_regressive_autism %>% 
  select(ID, Language, Other, AdaptiveScore) %>% 
  filter(!is.na(AdaptiveScore))

# Construct data frame for model
df_adaptive_lm <- df_adaptive %>% 
  select(ID, y = AdaptiveScore, 
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other))

compute_group_summaries(x = df_adaptive_lm, groups = df_regressive_groups)
```

```{r, fig.width=9}
#| label: adaptive-function-plot

# Evaluate model
list_adaptive <- evaluate_model(x = df_adaptive_lm)

# Generate heatmap from group contrasts
list_adaptive_heatmap <- contrasts_heatmap(x = list_adaptive$contrasts)

plt_adaptive_heatmap <- list_adaptive_heatmap$plot


plt_adaptive_scatter <- regression_scatter(model = list_adaptive, 
                                           groups = df_regressive_groups,
                                           point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                           ylims = c(20, 130), 
                                           ybreaks = seq(0, 200, by = 10))

plt_adaptive_scatter <- plt_adaptive_scatter +
  labs(y = "Adaptive Function Composite Score")

plt_adaptive <- plt_adaptive_scatter + plt_adaptive_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Adaptive Function vs. Regression Status")

outfile <- "adaptive_function.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_adaptive)
invisible(dev.off())

plt_adaptive
```

**Linear regression output:**

```{r adaptive-function-model}
summary(list_adaptive$model)
```

## Social Adaptive Function

```{r social-adaptive}
# Filter for participants with adaptive function scores
df_adaptive_soc <- df_regressive_autism %>% 
  select(ID, Language, Other, SocialAdaptiveScore) %>% 
  filter(!is.na(SocialAdaptiveScore))

# Construct data frame for model
df_adaptive_soc_lm <- df_adaptive_soc %>% 
  select(ID, y = SocialAdaptiveScore, 
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other))

compute_group_summaries(x = df_adaptive_soc_lm, groups = df_regressive_groups)
```

```{r, fig.width=9}
#| label: social-adaptive-plot

# Evaluate model
list_adaptive_soc <- evaluate_model(x = df_adaptive_soc_lm)

# Generate heatmap from group contrasts
list_adaptive_soc_heatmap <- contrasts_heatmap(x = list_adaptive_soc$contrasts)

plt_adaptive_soc_heatmap <- list_adaptive_soc_heatmap$plot


plt_adaptive_soc_scatter <- regression_scatter(model = list_adaptive_soc, 
                                           groups = df_regressive_groups,
                                           point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                           ylims = c(20, 130), 
                                           ybreaks = seq(0, 200, by = 10))

plt_adaptive_soc_scatter <- plt_adaptive_soc_scatter +
  labs(y = "Social Adaptive Function Score")

plt_adaptive_soc <- plt_adaptive_soc_scatter + plt_adaptive_soc_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Social Adaptive Function vs. Regression Status")

outfile <- "social_adaptive_function.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_adaptive_soc)
invisible(dev.off())

plt_adaptive_soc
```

------------------------------------------------------------------------

# Full-scale IQ

The subset of participants with IQ scores:

```{r iq}
# Filter for participants with adaptive function scores
df_IQ <- df_regressive_autism %>% 
  select(ID, Language, Other, IQ) %>% 
  filter(!is.na(IQ)) %>% 
  filter(!is.na(Language), !is.na(Other))

df_IQ_lm <- df_IQ %>% 
  select(ID, y = IQ, Language, Other)  

compute_group_summaries(x = df_IQ_lm, groups = df_regressive_groups)
```

```{r iq-plot}
#| fig-width: 9 

list_IQ <- evaluate_model(x = df_IQ_lm)

list_IQ_heatmap <- contrasts_heatmap(x = list_IQ$contrasts)

plt_IQ_heatmap <- list_IQ_heatmap$plot 

plt_IQ_scatter <- regression_scatter(model = list_IQ, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.3, 0.5, 0.5, 0.5),
                                     ylims = c(40, 160), 
                                     ybreaks = seq(0, 200, by = 10))

plt_IQ_scatter <- plt_IQ_scatter +
  labs(y = "Full-scale IQ")

plt_IQ <- plt_IQ_scatter + plt_IQ_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "IQ vs. Regression Status")

outfile <- "IQ.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_IQ)
invisible(dev.off())

plt_IQ
```

**Linear regression output:**

```{r iq-model}
summary(list_IQ$model)
```

------------------------------------------------------------------------

# ADOS

The subset of participants with ADOS scores:

```{r ados-overview}
df_ADOS_CSS <- df_regressive_autism %>% 
  select(ID, Language, Other, ADOS_CSS) %>% 
  filter(!is.na(ADOS_CSS), !is.na(Language), !is.na(Other))

df_ADOS_OTS <- df_regressive_autism %>% 
  select(ID, Language, Other, ADOS_OTS) %>% 
  filter(!is.na(ADOS_OTS), !is.na(Language), !is.na(Other))

df_ADOS_CSS_n <- compute_group_summaries(x = df_ADOS_CSS, groups = df_regressive_groups)
df_ADOS_OTS_n <- compute_group_summaries(x = df_ADOS_OTS, groups = df_regressive_groups)

df_ADOS_n <- left_join(rename(df_ADOS_OTS_n, OTS = n),
                       rename(df_ADOS_CSS_n, CSS = n),
                       by = "Group")

df_ADOS_n
```

3,767 participants have overall total scores (OTS) and 2,867 participants have calibrated standard scores (CSS). Among the participants with OTS scores, some have zero values:

```{r ados-ots-zeros}
df_ADOS_OTS %>% 
  mutate(ADOS_zero = ADOS_OTS == 0) %>% 
  group_by(ADOS_zero) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(`ADOS Scores` = ifelse(ADOS_zero, "OTS = 0", "OTS > 0")) %>% 
  select(`ADOS Scores`, n)
```

3,373 participants have non-zero OTS scores and 394 have zero scores.

## ADOS CSS

```{r ados-css-plot}
#| fig-width: 9 

# Filter for participants with adaptive function scores
df_ADOS_CSS_lm <- df_ADOS_CSS %>% 
  select(ID, y = ADOS_CSS, 
         Language, Other)  

list_ADOS_CSS <- evaluate_model(x = df_ADOS_CSS_lm)

list_ADOS_CSS_heatmap <- contrasts_heatmap(x = list_ADOS_CSS$contrasts)

plt_ADOS_CSS_heatmap <- list_ADOS_CSS_heatmap$plot 

plt_ADOS_CSS_scatter <- regression_scatter(model = list_ADOS_CSS, 
                                           groups = df_regressive_groups,
                                           point_alpha_values = c(0.1, 0.4, 0.4, 0.4),
                                           ylims = c(0, 11),
                                           ybreaks = seq(1, 10, by = 1)) 

plt_ADOS_CSS_scatter <- plt_ADOS_CSS_scatter +
  labs(y = "ADOS CSS") +
  theme(panel.grid.minor.y = element_blank())


plt_ADOS_CSS <- plt_ADOS_CSS_scatter + plt_ADOS_CSS_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "ADOS Calibrated Standard Score vs. Regression Status")

outfile <- "ADOS_CSS.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ADOS_CSS)
invisible(dev.off())

plt_ADOS_CSS
```

**Linear regression output:**

```{r ados-css-model}
summary(list_ADOS_CSS$model)
```

## ADOS OTS with zeros excluded

```{r ados-ots-plot}
#| fig-width: 9 

# Filter for participants with adaptive function scores
df_ADOS_OTS_lm <- df_ADOS_OTS %>% 
  filter(ADOS_OTS > 0) %>% 
  select(ID, y = ADOS_OTS, 
         Language, Other)  

list_ADOS_OTS <- evaluate_model(x = df_ADOS_OTS_lm)

list_ADOS_OTS_heatmap <- contrasts_heatmap(x = list_ADOS_OTS$contrasts)

plt_ADOS_OTS_heatmap <- list_ADOS_OTS_heatmap$plot 

plt_ADOS_OTS_scatter <- regression_scatter(model = list_ADOS_OTS, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.1, 0.4, 0.4, 0.4),
                                     ylims = c(0, 30), 
                                     ybreaks = seq(0, 200, by = 2))

plt_ADOS_OTS_scatter <- plt_ADOS_OTS_scatter +
  labs(y = "ADOS OTS")

plt_ADOS_OTS <- plt_ADOS_OTS_scatter + plt_ADOS_OTS_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "ADOS Overall Total Score vs. Regression Status")

outfile <- "ADOS_OTS.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ADOS_OTS)
invisible(dev.off())

plt_ADOS_OTS
```

**Linear regression output:**

```{r ados-ots-model}
summary(list_ADOS_OTS$model)
```

## Analysis of ADOS OTS zero scores

```{r}
#| echo: false
#| eval: false

tmp <- df_regressive_autism |> 
  filter(!is.na(ADOS)) |> 
  mutate(ADOS_zero = ADOS == 0)


tmp %>% 
  group_by(ADOS_zero, Regressive_Strictly_Language) %>% 
  count()
```

```{r}
#| echo: false
#| eval: false

chisq.test(x = tmp$Regressive_Strictly_Language, y = tmp$ADOS_zero)
```

```{r}
#| echo: false
#| eval: false

chisq.test(x = tmp$Regressive_Strictly_Other, y = tmp$ADOS_zero)
```

```{r}
#| echo: false
#| eval: false

cols_regressive <- c("Regressive_Strictly_Language", "Regressive_Strictly_Other", 
                     "Regressive_Both", "Regressive_Any")
df_ADOS_zeros_chi2 <- tibble(regression = cols_regressive,
                             chi2 = 0, pval = 0)
for (i in 1:nrow(df_ADOS_zeros_chi2)) {
  
  x <- tmp[[cols_regressive[i]]]
  y <- tmp[["ADOS_zero"]]
  
  chisq_out <- chisq.test(x = x, y = y, simulate.p.value = TRUE, B = 5000)
  
  df_ADOS_zeros_chi2[[i, "chi2"]] <- chisq_out$statistic
  df_ADOS_zeros_chi2[[i, "pval"]] <- chisq_out$p.value
  
}

df_ADOS_zeros_chi2
```

```{r ados-plot}
#| echo: false
#| eval: false

annotation_y <- 0.95

# adaptive_titles <- c("Language regressive", 
#                      "Other skill regressive", 
#                      "Language and other skill regressive",
#                      "Language or other skill regressive")
ADOS_titles <- c("Language", 
                 "Other skill", 
                 "Language and other skill",
                 "Language or other skill")

list_ADOS_zero_plts <- vector(mode = "list", length = nrow(df_ADOS_zeros_chi2))
for (i in 1:length(list_ADOS_zero_plts)) {
  
  cols <- c("ID", cols_regressive[i], "ADOS_zero")
  df_ADOS_zero_plt <- tmp[,cols]
  colnames(df_ADOS_zero_plt) <- c("ID", "Regressive", "ADOS_zero")
  
  # df_ADOS_zero_plt <- df_ADOS_zero_plt %>% 
  #   group_by(Regressive, ADOS_zero) %>% 
  #   count() %>% 
  #   ungroup() %>% 
  #   mutate(ADOS_nonzero = !ADOS_zero)
  
  df_ADOS_zero_plt <- df_ADOS_zero_plt %>% 
    group_by(Regressive) %>% 
    mutate(n_per_group = n()) %>% 
    ungroup() %>% 
    group_by(Regressive, ADOS_zero) %>%  
    mutate(n_per_zero_per_group = n()) %>%  
    ungroup() %>% 
    mutate(prop_per_zero_per_group = n_per_zero_per_group/n_per_group) %>% 
    mutate(ADOS_nonzero = !ADOS_zero) %>% 
    select(Regressive, ADOS_nonzero, n_per_group, n_per_zero_per_group, prop_per_zero_per_group) %>% 
    distinct() %>% 
    arrange(Regressive, ADOS_nonzero)
  
  df_ADOS_zero_annotation <- df_ADOS_zeros_chi2[i, ] %>% 
    mutate(p.label = ifelse(pval < 0.001, 
                            "p < 0.001", paste0("p = ", round(pval, 3)))) %>% 
    select(p.label) %>% 
    mutate(x = 1.5, y = annotation_y + 0.04)
  
  plt_ADOS_zero <- ggplot(df_ADOS_zero_plt, aes(x = Regressive, fill = ADOS_nonzero, y = prop_per_zero_per_group)) + 
    geom_col(position = "dodge") +
    annotate(geom = "segment", x = FALSE, xend = TRUE, y = annotation_y, color = "grey40") +
    geom_text(data = df_ADOS_zero_annotation, aes(x = x, y = y, label = p.label),
              inherit.aes = FALSE, 
              size = 3.5, color = "grey30") +
    scale_x_discrete(labels = c("Non-regressive", "Regressive")) +
    scale_fill_discrete(labels = c("ADOS = 0", "ADOS > 0")) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
    labs(x = NULL,
         y = "Proportion of participants per regression group",
         fill = NULL, 
         title = ADOS_titles[i]) + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  
  if (i > 1) {
    plt_ADOS_zero <- plt_ADOS_zero +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }
  
  list_ADOS_zero_plts[[i]] <- plt_ADOS_zero
  
}

fig_ADOS_zero <- (list_ADOS_zero_plts[[1]] | list_ADOS_zero_plts[[2]] | list_ADOS_zero_plts[[3]] | list_ADOS_zero_plts[[4]]) +
  plot_layout(guides = "collect")

outfile <- "ADOS_zero_regression.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(10, "in"),
    height = unit(6, "in"))
print(fig_ADOS_zero)
dev.off()
```

```{r}
#| echo: false
#| eval: false

cols <- c("ID", cols_regressive[i], "ADOS_zero")
df_ADOS_zero_plt <- tmp[,cols]
colnames(df_ADOS_zero_plt) <- c("ID", "Regressive", "ADOS_zero")

df_ADOS_zero_plt %>% 
  group_by(Regressive) %>% 
  mutate(n_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Regressive, ADOS_zero) %>%  
  mutate(n_per_zero_per_group = n()) %>%  
  ungroup() %>% 
  mutate(prop_per_zero_per_group = n_per_zero_per_group/n_per_group) %>% 
  mutate(ADOS_nonzero = !ADOS_zero) %>% 
  select(Regressive, ADOS_nonzero, n_per_group, n_per_zero_per_group, prop_per_zero_per_group) %>% 
  distinct() %>% 
  arrange(Regressive, ADOS_nonzero)
```

```{r}
#| echo: false
#| eval: false

tmp_adaptive <- tmp %>% 
  filter(!is.na(AdaptiveScore)) %>% 
  mutate(ADOS_zero = ifelse(ADOS_zero, "Yes", "No"),
         ADOS_zero = factor(ADOS_zero))

model_ADOS_zero_adaptive <- summary(lm(AdaptiveScore ~ ADOS_zero, data = tmp_adaptive))

df_ADOS_zero_adaptive_summary <- group_summary(tmp_adaptive$AdaptiveScore,
                                               groups = tmp_adaptive$ADOS_zero)
df_ADOS_zero_adaptive_summary <- df_ADOS_zero_adaptive_summary %>% 
  as_tibble(rownames = "ADOS_zero") %>% 
  mutate(ADOS_zero = factor(ADOS_zero))


set.seed(123)
plt_ADOS_zero_adaptive <- ggplot(tmp_adaptive, aes(x = ADOS_zero, y = AdaptiveScore)) +
  geom_jitter(size = 1, width = 0.3, height = 0, alpha = 0.4, col = "grey20") + 
  geom_crossbar(data = df_ADOS_zero_adaptive_summary, 
                mapping = aes(x = ADOS_zero, y = mu, ymin = lower, ymax = upper),
                alpha = 0.1, col = "red3", fill = "red3") + 
  annotate(geom = "segment", x = "No", xend = "Yes", y = 135, color = "grey40") +
  annotate(geom = "text", x = 1.5, y = 140, label = "p < 0.001") + 
  scale_x_discrete(labels = c("ADOS > 0", "ADOS = 0")) +
  scale_y_continuous(breaks = seq(0, 200, by = 10)) +
  labs(x = "Binarized ADOS score",
       y = "Adaptive Function Composite Score") + 
  theme_bw() 

outfile <- "ADOS_zero_adaptive_function.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(6, "in"),
    height = unit(6, "in"))
print(plt_ADOS_zero_adaptive)
dev.off()
```

```{r}
#| echo: false
#| eval: false

tmp_IQ <- tmp %>% 
  filter(!is.na(IQ)) %>% 
  mutate(ADOS_zero = ifelse(ADOS_zero, "Yes", "No"),
         ADOS_zero = factor(ADOS_zero))

tmp_IQ %>% 
  group_by(ADOS_zero) %>% 
  count()
```

```{r}
#| echo: false
#| eval: false

tmp_IQ %>% 
  filter(ADOS_zero == "Yes") %>% 
  select(IQ) %>% 
  arrange(desc(IQ))
```

### Autism diagnosis by ADI-R sub-domain scores

```{r}
#| echo: false
#| eval: false

# Initialize data frame to store outputs
df_ADIR_subdomains <- df_regressive_autism %>% 
  select(ID)

# Path to ADI-R data
path_ADIR <- "data/raw/ADI-R/"

ADIR_subdomains <- c("Onset", "RRB", "Communication", "Social")

# Sub-domain cutoff files for ADI WPS
files_wps <- c("ADIWPS_ADIAFAB_cutoff_1.xlsx",
               "ADIWPS_ADIAFBEH_cutoff_3.xlsx",
               "ADIWPS_ADIAFCOM_cutoff_7-8.xlsx",
               "ADIWPS_ADIAFSOC_cutoff_10.xlsx")

# Sub-domain cutoff files for ADI 1995
files_1995 <- c("ADI1995_ADIAFAB_cutoff_1.xlsx",
                "ADI1995_ADIAFBEH_cutoff_3.xlsx",
                "ADI1995_ADIAFCOM_cutoff_7-8.xlsx",
                "ADI1995_ADIAFSOC_cutoff_10.xlsx")

# Iterate over sub-domains
for (i in 1:length(ADIR_subdomains)) {
  
  # Import WPS data
  file_wps <- file.path(path_ADIR, files_wps[i])
  df_wps_all <- read_excel(file_wps)
  
  # Import 1995 data
  file_1995 <- file.path(path_ADIR, files_1995[i])
  df_1995_all <- read_excel(file_1995)
  
  # Clean up WPS data
  df_wps_all <- df_wps_all %>% 
    mutate(cutoff_pass = numeric_value == 1) %>% 
    select(ID = indexid, cutoff_pass) %>% 
    mutate(version = "WPS")
  
  # Clean up 1995 data
  df_1995_all <- df_1995_all %>% 
    mutate(cutoff_pass = numeric_value == 1) %>% 
    select(ID = indexid, cutoff_pass) %>% 
    mutate(version = "1995")
  
  # Collate WPS and 1995 data
  df_cutoff_all <- bind_rows(df_wps_all, df_1995_all)
  
  # Remove duplicate entries
  df_cutoff_all <- df_cutoff_all %>% 
    distinct()
  
  # Identify participants with data from both versions
  ids_multiple_versions <- df_cutoff_all %>%
    select(ID, version) %>% 
    distinct() %>% 
    group_by(ID) %>% 
    count() %>% 
    filter(n > 1) %>% 
    pull(ID)
  
  # For participants with both versions, use 1995 version. 
  # Include all participants with only 1995 version
  df_cutoff_1995 <- bind_rows(
    df_cutoff_all %>% 
      filter(ID %in% ids_multiple_versions,
             version == "1995"),
    df_cutoff_all %>% 
      filter(!(ID %in% ids_multiple_versions),
             version == "1995"))
  
  # For participants with only WPS, use that
  df_cutoff_wps <- df_cutoff_all %>% 
    filter(!(ID %in% ids_multiple_versions),
           version == "WPS")
  
  # Combine 1995 and WPS data
  df_cutoff <- bind_rows(df_cutoff_1995, 
                         df_cutoff_wps)
  
  # Identify participants with multiple distinct values
  ids_multiple <- df_cutoff %>% 
    group_by(ID) %>% 
    count() %>% 
    filter(n > 1) %>% 
    pull(ID) %>% 
    unique()
  
  # For participants with both TRUE and FALSE, set to TRUE
  df_cutoff <- df_cutoff %>% 
    mutate(cutoff_pass = ifelse(ID %in% ids_multiple, TRUE, cutoff_pass)) %>% 
    distinct()
  
  # Subset columns and rename with sub-domain
  df_cutoff <- df_cutoff %>% 
    select(ID, cutoff_pass)
  colnames(df_cutoff)[2] <- ADIR_subdomains[i]
  
  # Join to final data frame
  df_ADIR_subdomains <- df_ADIR_subdomains %>% 
    left_join(df_cutoff, by = "ID")
  
}
```

```{r}
#| echo: false
#| eval: false

# Convert to long format
df_ADIR_subdomains_long <- df_ADIR_subdomains %>% 
  pivot_longer(cols = -ID, names_to = "subdomain", values_to = "pass")  

df_ADIR_subdomains_missing <- df_ADIR_subdomains_long %>% 
  mutate(missing = is.na(pass)) %>% 
  group_by(ID) %>% 
  summarise(n_missing = sum(missing)) %>% 
  ungroup()

df_ADIR_subdomains_missing %>% 
  filter(n_missing > 0) %>% 
  group_by(n_missing) %>% 
  count()
```

```{r}
#| echo: false
#| eval: false

ids_missing_subdomains <- df_ADIR_subdomains_missing %>% 
  filter(n_missing > 0) %>% 
  pull(ID)

df_regressive_autism %>% 
  filter(ID %in% ids_missing_subdomains)
```

```{r}
#| echo: false
#| eval: false

df_ADIR_subdomains_pass <- df_ADIR_subdomains_long %>% 
  group_by(ID) %>% 
  summarise(n_pass = sum(pass),
            n_pass_drop_na = sum(pass, na.rm = FALSE)) %>% 
  ungroup()
```

```{r}
#| echo: false
#| eval: false

# Filter all ADI participants who have ADOS
df_ADOS <- df_regressive_autism %>% 
  select(ID, contains("Regressive"), ADOS) %>% 
  filter(!is.na(ADOS))

# Filter for participants with ADOS = 0
df_ADOS_zeros <- df_ADOS %>% 
  filter(ADOS == 0)

df_ADOS_zeros <- df_ADOS_zeros %>% 
  left_join(df_ADIR_subdomains_pass, by = "ID")

df_ADOS_zeros %>% 
  group_by(n_pass) %>% 
  count()
```

```{r}
#| echo: false
#| eval: false

df_ADOS_zeros %>% 
  filter(is.na(n_pass)) %>% 
  select(ID, n_pass, n_pass_drop_na)
```

------------------------------------------------------------------------

# ADHD

There are 1,304 participants with ADHD information:

```{r adhd-numbers-1}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(ADHD) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(ADHD = ifelse(ADHD, "Yes", "No"))
```

Broken down by regression group:

```{r adhd-numbers-2}
df_ADHD <- df_regressive_autism %>% 
  select(ID, Language, Other, ADHD) %>% 
  filter(!is.na(ADHD), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_ADHD, groups = df_regressive_groups)
```

```{r adhd-plot, fig.width = 9}
df_ADHD_lr <- df_ADHD %>% 
  select(ID, y = ADHD, 
         Language, Other) 

list_ADHD <- evaluate_model(x = df_ADHD_lr, type = "logistic")


list_ADHD_heatmap <- contrasts_heatmap(x = list_ADHD$contrasts)

plt_ADHD_heatmap <- list_ADHD_heatmap$plot 

plt_ADHD_probs <- regression_probs(model = list_ADHD, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_ADHD <- plt_ADHD_probs + plt_ADHD_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "ADHD vs. Regression Status")

outfile <- "ADHD.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ADHD)
invisible(dev.off())

plt_ADHD
```

**Logistic regression output:**

```{r adhd-model}
summary(list_ADHD$model)
```

```{r}
#| echo: false
#| eval: false

df_ADHD %>% 
  group_by(ADHD) %>% 
  summarise(N = n(), prop = N/nrow(.),
            .groups = "drop")
```

```{r}
#| echo: false
#| eval: false

df_ADHD_lr %>% 
  group_by(Language, Other) %>% 
  mutate(N_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Language, Other, y) %>% 
  mutate(N = n()) %>% 
  ungroup() %>% 
  select(-ID) %>% 
  distinct() %>% 
  mutate(prop = N/N_per_group) %>% 
  select(Language, Other, y, N_per_group, N, prop) %>% 
  arrange(Language, Other, y) %>% 
  filter(y)
```

------------------------------------------------------------------------

# Anxiety

There are 1,080 participants with anxiety information:

```{r anxiety-numbers-1}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Anxiety) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Anxiety = ifelse(Anxiety, "Yes", "No"))
```

Broken down by regression group:

```{r anxiety-numbers-2}
df_anxiety <- df_regressive_autism %>% 
  select(ID, Language, Other, Anxiety) %>% 
  filter(!is.na(Anxiety), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_anxiety, groups = df_regressive_groups)
```

```{r anxiety-plot, fig.width = 9}
df_anxiety_lr <- df_anxiety %>% 
  select(ID, y = Anxiety, 
         Language, Other) 

list_anxiety <- evaluate_model(x = df_anxiety_lr, type = "logistic")


list_anxiety_heatmap <- contrasts_heatmap(x = list_anxiety$contrasts)

plt_anxiety_heatmap <- list_anxiety_heatmap$plot 

plt_anxiety_probs <- regression_probs(model = list_anxiety, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_anxiety <- plt_anxiety_probs + plt_anxiety_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Anxiety vs. Regression Status")

outfile <- "anxiety.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_anxiety)
invisible(dev.off())

plt_anxiety
```

**Logistic regression output:**

```{r anxiety-model}
summary(list_anxiety$model)
```

## Continuous anxiety scores

### CBCL Anxious Problems

```{r anxiety-cbcl-numbers}
file <- "data/processed/Anxiety/anxiety_cbcl.csv"
df_anxiety_cbcl <- read_csv(file, show_col_types = FALSE)

df_anxiety_cbcl %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(CBCL_AP_TS), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r anxiety-cbcl-plot, fig.width = 9}
df_anxiety_cbcl_lm <- df_anxiety_cbcl %>% 
  select(ID, y = CBCL_AP_TS) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_anxiety_cbcl <- evaluate_model(x = df_anxiety_cbcl_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_anxiety_cbcl_heatmap <- contrasts_heatmap(x = list_anxiety_cbcl$contrasts)

plt_anxiety_cbcl_heatmap <- list_anxiety_cbcl_heatmap$plot


plt_anxiety_cbcl_scatter <- regression_scatter(model = list_anxiety_cbcl, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          ylims = c(50, 90),
                                          ybreaks = seq(0, 100, by = 10))

plt_anxiety_cbcl_scatter <- plt_anxiety_cbcl_scatter +
labs(y = "CBCL Anxious Problems T-score")

plt_anxiety_cbcl <- plt_anxiety_cbcl_scatter + plt_anxiety_cbcl_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "CBCL Anxious Problems vs. Regression Status")

outfile <- "anxiety_cbcl.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_anxiety_cbcl)
invisible(dev.off())

plt_anxiety_cbcl
```

### RCADS Generalized Anxiety

```{r anxiety-rcads}
file <- "data/processed/Anxiety/anxiety_rcads.csv"
df_anxiety_rcads <- read_csv(file, show_col_types = FALSE)

df_anxiety_rcads %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(score), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r anxiety-rcads-plot, fig.width = 9}
df_anxiety_rcads_lm <- df_anxiety_rcads %>% 
  select(ID, y = score) %>% 
  group_by(ID) %>% 
  summarise(y = mean(y)) %>% 
  ungroup() %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_anxiety_rcads <- evaluate_model(x = df_anxiety_rcads_lm, type = "linear")

# Generate heatmap from group contrasts
list_anxiety_rcads_heatmap <- contrasts_heatmap(x = list_anxiety_rcads$contrasts)

plt_anxiety_rcads_heatmap <- list_anxiety_rcads_heatmap$plot


plt_anxiety_rcads_scatter <- regression_scatter(model = list_anxiety_rcads, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          # ylims = c(50, 90),
                                          ybreaks = seq(0, 100, by = 10))

plt_anxiety_rcads_scatter <- plt_anxiety_rcads_scatter +
labs(y = "RCADS GA T-score")

plt_anxiety_rcads <- plt_anxiety_rcads_scatter + plt_anxiety_rcads_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RCADS Generalized Anxiety vs. Regression Status")

outfile <- "anxiety_rcads.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_anxiety_rcads)
invisible(dev.off())

plt_anxiety_rcads
```

### SPENCEP Total Score

```{r anxiety-spence}
file <- "data/processed/Anxiety/anxiety_spencep.csv"
df_anxiety_spencep <- read_csv(file, show_col_types = FALSE)

df_anxiety_spencep %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(score), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r anxiety-spence-plot, fig.width = 9}
df_anxiety_spencep_lm <- df_anxiety_spencep %>% 
  select(ID, y = score) %>% 
  group_by(ID) %>% 
  summarise(y = mean(y)) %>% 
  ungroup() %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_anxiety_spencep <- evaluate_model(x = df_anxiety_spencep_lm, type = "linear")

# Generate heatmap from group contrasts
list_anxiety_spencep_heatmap <- contrasts_heatmap(x = list_anxiety_spencep$contrasts)

plt_anxiety_spencep_heatmap <- list_anxiety_spencep_heatmap$plot


plt_anxiety_spencep_scatter <- regression_scatter(model = list_anxiety_spencep, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          # ylims = c(50, 90),
                                          ybreaks = seq(0, 100, by = 10))

plt_anxiety_spencep_scatter <- plt_anxiety_spencep_scatter +
labs(y = "SPENCE Total Score")

plt_anxiety_spencep <- plt_anxiety_spencep_scatter + plt_anxiety_spencep_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SPENCE Total Score vs. Regression Status")

outfile <- "anxiety_spencep.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_anxiety_spencep)
invisible(dev.off())

plt_anxiety_spencep
```

------------------------------------------------------------------------

# Depression

There are 832 participants with depression information:

```{r depression-numbers-1}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Depression) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Depression = ifelse(Depression, "Yes", "No"))
```

Broken down by regression group:

```{r depression-numbers-2}
df_depression <- df_regressive_autism %>% 
  select(ID, Language, Other, Depression) %>% 
  filter(!is.na(Depression), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_depression, groups = df_regressive_groups)
```

```{r depression-plot, fig.width = 9}
df_depression_lr <- df_depression %>% 
  select(ID, y = Depression, 
         Language, Other) 

list_depression <- evaluate_model(x = df_depression_lr, type = "logistic")


list_depression_heatmap <- contrasts_heatmap(x = list_depression$contrasts)

plt_depression_heatmap <- list_depression_heatmap$plot 

plt_depression_probs <- regression_probs(model = list_depression, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_depression <- plt_depression_probs + plt_depression_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Depression vs. Regression Status")

outfile <- "depression.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_depression)
invisible(dev.off())

plt_depression
```

## Continuous depression scores

### CBCL Affective Problems

```{r depression-cbcl-numbers}
file <- "data/processed/Depression/depression_cbcl.csv"
df_depression_cbcl <- read_csv(file, show_col_types = FALSE)

df_depression_cbcl %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(CBCL_AP_TS), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r depression-cbcl-plot, fig.width = 9}
df_depression_cbcl_lm <- df_depression_cbcl %>% 
  select(ID, y = CBCL_AP_TS) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_depression_cbcl <- evaluate_model(x = df_depression_cbcl_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_depression_cbcl_heatmap <- contrasts_heatmap(x = list_depression_cbcl$contrasts)

plt_depression_cbcl_heatmap <- list_depression_cbcl_heatmap$plot


plt_depression_cbcl_scatter <- regression_scatter(model = list_depression_cbcl, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          ylims = c(50, 90),
                                          ybreaks = seq(0, 100, by = 10))

plt_depression_cbcl_scatter <- plt_depression_cbcl_scatter +
labs(y = "CBCL Anxious Problems T-score")

plt_depression_cbcl <- plt_depression_cbcl_scatter + plt_depression_cbcl_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "CBCL Anxious Problems vs. Regression Status")

outfile <- "depression_cbcl.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_depression_cbcl)
invisible(dev.off())

plt_depression_cbcl
```

### RCADS Depression

```{r depression-rcads-numbers}
file <- "data/processed/Depression/depression_rcads.csv"
df_depression_rcads <- read_csv(file, show_col_types = FALSE)

df_depression_rcads %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(score), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r depression-rcads-plot, fig.width = 9}
df_depression_rcads_lm <- df_depression_rcads %>% 
  select(ID, y = score) %>% 
  group_by(ID) %>% 
  summarise(y = mean(y)) %>% 
  ungroup() %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_depression_rcads <- evaluate_model(x = df_depression_rcads_lm, type = "linear")

# Generate heatmap from group contrasts
list_depression_rcads_heatmap <- contrasts_heatmap(x = list_depression_rcads$contrasts)

plt_depression_rcads_heatmap <- list_depression_rcads_heatmap$plot


plt_depression_rcads_scatter <- regression_scatter(model = list_depression_rcads, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          # ylims = c(50, 90),
                                          ybreaks = seq(0, 100, by = 10))

plt_depression_rcads_scatter <- plt_depression_rcads_scatter +
labs(y = "RCADS D T-score")

plt_depression_rcads <- plt_depression_rcads_scatter + plt_depression_rcads_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RCADS Depression vs. Regression Status")

outfile <- "depression_rcads.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_depression_rcads)
invisible(dev.off())

plt_depression_rcads
```

------------------------------------------------------------------------

# Sleep

There are 767 participants with sleep information:

```{r sleep-numbers-1}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Sleep) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Sleep = ifelse(Sleep, "Yes", "No"))
```

Broken down by regression group:

```{r sleep-numbers-2}
df_sleep <- df_regressive_autism %>% 
  select(ID, Language, Other, Sleep) %>% 
  filter(!is.na(Sleep), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_sleep, groups = df_regressive_groups)
```

```{r sleep-plot, fig.width = 9}
df_sleep_lr <- df_sleep %>% 
  select(ID, y = Sleep, 
         Language, Other) 

list_sleep <- evaluate_model(x = df_sleep_lr, type = "logistic")


list_sleep_heatmap <- contrasts_heatmap(x = list_sleep$contrasts)

plt_sleep_heatmap <- list_sleep_heatmap$plot 

plt_sleep_probs <- regression_probs(model = list_sleep, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_sleep <- plt_sleep_probs + plt_sleep_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Sleep Problems vs. Regression Status")

outfile <- "sleep.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_sleep)
invisible(dev.off())

plt_sleep
```

------------------------------------------------------------------------

# Seizures

There are 4,160 participants with seizure information:

```{r seizures-numbers-1}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Seizure) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Seizure = ifelse(Seizure, "Yes", "No"))
```

Broken down by regression group:

```{r seizures-numbers-2}
df_seizures <- df_regressive_autism %>% 
  select(ID, Language, Other, Seizure, Seizure_Date, DOB, ADIR_Age) %>% 
  filter(!is.na(Seizure), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_seizures, groups = df_regressive_groups)
```

```{r seizures-plot, fig.width = 9}
df_seizures_lr <- df_seizures %>% 
  select(ID, y = Seizure, 
         Language, Other) 

list_seizures <- evaluate_model(x = df_seizures_lr, type = "logistic")


list_seizures_heatmap <- contrasts_heatmap(x = list_seizures$contrasts)

plt_seizures_heatmap <- list_seizures_heatmap$plot 

plt_seizures_probs <- regression_probs(model = list_seizures, 
                                       groups = df_regressive_groups,
                                       ybreaks = seq(0, 1, by = 0.01),
                                       ylims = c(0, 0.12))

plt_seizures <- plt_seizures_probs + plt_seizures_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Seizures vs. Regression Status")

outfile <- "seizures_overall.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_seizures)
invisible(dev.off())

plt_seizures
```

## Seizures in three age bins

The distributions of ages among participants with seizure information:

```{r seizures-age-dist, fig.width = 9}
df_seizures_age <- df_seizures %>% 
  mutate(Seizure_Date = ifelse(Seizure_Date == "1900-01-01", NA, Seizure_Date)) %>% 
  mutate(Seizure_Date = as.Date(Seizure_Date)) %>% 
  mutate(Seizure_Age = time_length(interval(DOB, Seizure_Date), "years")) %>% 
  mutate(Seizure_Age = ifelse(is.na(Seizure_Age), ADIR_Age, Seizure_Age)) %>%
  filter(Seizure_Age > 0)

ggplot(df_seizures_age, aes(x = Seizure_Age, fill = Seizure, y = after_stat(density))) + 
  geom_histogram(position = "dodge", binwidth = 2) +
  labs(x = "Age") + 
  scale_x_continuous(breaks = seq(0, 50, 5)) + 
  # scale_y_continuous(breaks = seq(0, 100, 10)) + 
  scale_fill_discrete(labels = c("No", "Yes")) + 
  theme_bw()
```

If we split the seizure ages into three bins, the numbers are as follows:

```{r seizures-age-binned-3}
df_seizures_binned <- df_seizures_age %>% 
  mutate(AgeBin = case_when(Seizure_Age < 5 ~ "< 5",
                            Seizure_Age >= 5 & Seizure_Age < 12 ~ "5-12",
                            Seizure_Age >= 12 ~ ">= 12"))

df_seizures_binned <- df_seizures_binned %>% 
  filter(!is.na(AgeBin))

df_seizures_binned <- df_seizures_binned %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", "5-12", ">= 12")))

df_seizures_binned %>% 
  group_by(AgeBin) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(`Age Bin` = c("Under 5", "5 to 12", "Over 12")) %>% 
  select(`Age Bin`, n)
```

The association between seizures and regression status in each of the three bins:

```{r}
df_seizures_binned_lr <- df_seizures_binned %>% 
  select(ID, y = Seizure, 
         Language, Other, AgeBin) %>% 
  filter(!is.na(Language), !is.na(Other))

list_seizures_binned_inputs <- split(df_seizures_binned_lr, f = df_seizures_binned_lr$AgeBin)

list_seizures_binned <- map(list_seizures_binned_inputs, .f = evaluate_model, type = "logistic")

```

```{r fig.width = 9}
df_seizures_binned_plt <- map_dfr(list_seizures_binned, 
                                  .f = function(x) {as_tibble(x[["emmeans"]])},
                                  .id = "AgeBin")

df_seizures_binned_plt <- df_seizures_binned_plt %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", "5-12", ">= 12"))) %>% 
  mutate(AgeLabel = case_when(AgeBin == "< 5" ~ "Under 5",
                              AgeBin == "5-12" ~ "5 to 12",
                              AgeBin == ">= 12" ~ "Over 12"),
         AgeLabel = factor(AgeLabel, levels = c("Under 5", "5 to 12", "Over 12")))

plt_lvls <- c("None", "Language", "Other", "Both")

plt_seizures_probs_binned <- ggplot(df_seizures_binned_plt, 
                                    aes(x = interaction(Language, Other),
                                        y = prob)) + 
  # geom_point(position = position_dodge(width = 0.2)) +
  # geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
  #                 position = position_dodge(width = 0.3)) +
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL)) +
  facet_grid(.~AgeLabel) + 
  coord_cartesian(ylim = c(0, 0.3)) + 
  scale_x_discrete(labels = plt_lvls) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) + 
  labs(x = "Regression Type",
       y = "Probability of seizures") +
  theme_bw()


df_seizures_binned_heatmap <- map_dfr(list_seizures_binned,
                                      .f = function(x) {contrasts_heatmap(x = x[["contrasts"]])[["data"]]}, 
                                      .id = "AgeBin")

df_seizures_binned_heatmap <- df_seizures_binned_heatmap %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", "5-12", ">= 12"))) %>% 
  mutate(AgeLabel = case_when(AgeBin == "< 5" ~ "Under 5",
                              AgeBin == "5-12" ~ "5 to 12",
                              AgeBin == ">= 12" ~ "Over 12"),
         AgeLabel = factor(AgeLabel, levels = c("Under 5", "5 to 12", "Over 12")))

threshold_lwr <- -log10(0.05)
threshold_upr <- 10

plt_seizures_heatmap_binned <- ggplot(df_seizures_binned_heatmap,
                                      aes(x = Comparison, y = fct_rev(Reference), fill = NLQ, col = exclude)) + 
  geom_tile() +
  facet_grid(.~AgeLabel) +
  scale_fill_gradientn(
    colours = c("grey80", viridis::magma(256, begin = 0.2, end = 0.9)),
    values  = scales::rescale(c(threshold_lwr, seq(threshold_lwr + 0.001, threshold_upr, length.out = 256))),
    limits  = c(threshold_lwr, threshold_upr),
    oob     = scales::squish,        # forces NLQ <= thr to thr
    na.value = "white"
  ) +
  scale_colour_manual(values = c("grey50", "white"), guide = "none") + 
  scale_x_discrete(expand = expansion(), position = "top") +
  scale_y_discrete(expand = expansion(), position = "right") +
  labs(x = "Comparison Group",
       y = "Reference Group",
       fill = "-log10(q-value)") + 
  theme(axis.line.x.bottom = element_blank(),
        axis.line.x.top = element_line(colour = "grey50"),
        axis.line.y.left   = element_blank(),
        axis.line.y.right = element_line(colour = "grey50"),
        legend.position = "bottom")
        # legend.position = c(0.02, 0.02),   # bottom-left inside panel
        # legend.justification = c(0, 0),
        # legend.background = element_rect(
        #   fill = scales::alpha("white", 0.8),
        #   colour = NA
        # ))


plt_seizures_binned <- plt_seizures_probs_binned / plt_seizures_heatmap_binned

outfile <- "seizures_age_binned_3.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(6, "in"))
print(plt_seizures_binned)
invisible(dev.off())

plt_seizures_binned
```

## Seizures in two age bins

If we split the seizure ages into two bins, the numbers are as follows:

```{r}
df_seizures_binned <- df_seizures_age %>% 
  mutate(AgeBin = case_when(Seizure_Age < 5 ~ "< 5",
                            Seizure_Age >= 5 ~ ">= 5"))

df_seizures_binned <- df_seizures_binned %>% 
  filter(!is.na(AgeBin))

df_seizures_binned <- df_seizures_binned %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", ">= 5")))

df_seizures_binned %>% 
  group_by(AgeBin) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(`Age Bin` = c("Under 5", "Over 5")) %>% 
  select(`Age Bin`, n)
```

The association between seizures and regression status in each of the two bins:

```{r}
df_seizures_binned_lr <- df_seizures_binned %>% 
  select(ID, y = Seizure, 
         Language, Other, AgeBin) %>% 
  filter(!is.na(Language), !is.na(Other))

list_seizures_binned_inputs <- split(df_seizures_binned_lr, f = df_seizures_binned_lr$AgeBin)

list_seizures_binned <- map(list_seizures_binned_inputs, .f = evaluate_model, type = "logistic")

```

```{r fig.width = 9}
df_seizures_binned_plt <- map_dfr(list_seizures_binned, 
                                  .f = function(x) {as_tibble(x[["emmeans"]])},
                                  .id = "AgeBin")

df_seizures_binned_plt <- df_seizures_binned_plt %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", ">= 5"))) %>% 
  mutate(AgeLabel = case_when(AgeBin == "< 5" ~ "Under 5",
                              AgeBin == ">= 5" ~ "Over 5"),
         AgeLabel = factor(AgeLabel, levels = c("Under 5", "Over 5")))

plt_lvls <- c("None", "Language", "Other", "Both")

plt_seizures_probs_binned <- ggplot(df_seizures_binned_plt, 
                                    aes(x = interaction(Language, Other),
                                        y = prob)) + 
  # geom_point(position = position_dodge(width = 0.2)) +
  # geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL),
  #                 position = position_dodge(width = 0.3)) +
  geom_pointrange(aes(ymin = asymp.LCL, ymax = asymp.UCL)) +
  facet_grid(.~AgeLabel) + 
  coord_cartesian(ylim = c(0, 0.3)) + 
  scale_x_discrete(labels = plt_lvls) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) + 
  labs(x = "Regression Type",
       y = "Probability of seizures") +
  theme_bw()


df_seizures_binned_heatmap <- map_dfr(list_seizures_binned,
                                      .f = function(x) {contrasts_heatmap(x = x[["contrasts"]])[["data"]]}, 
                                      .id = "AgeBin")

df_seizures_binned_heatmap <- df_seizures_binned_heatmap %>% 
  mutate(AgeBin = factor(AgeBin, levels = c("< 5", ">= 5"))) %>% 
  mutate(AgeLabel = case_when(AgeBin == "< 5" ~ "Under 5",
                              AgeBin == ">= 5" ~ "Over 5"),
         AgeLabel = factor(AgeLabel, levels = c("Under 5", "Over 5")))

threshold_lwr <- -log10(0.05)
threshold_upr <- 10

plt_seizures_heatmap_binned <- ggplot(df_seizures_binned_heatmap,
                                      aes(x = Comparison, y = fct_rev(Reference), fill = NLQ, col = exclude)) + 
  geom_tile() +
  facet_grid(.~AgeLabel) +
  scale_fill_gradientn(
    colours = c("grey80", viridis::magma(256, begin = 0.2, end = 0.9)),
    values  = scales::rescale(c(threshold_lwr, seq(threshold_lwr + 0.001, threshold_upr, length.out = 256))),
    limits  = c(threshold_lwr, threshold_upr),
    oob     = scales::squish,        # forces NLQ <= thr to thr
    na.value = "white"
  ) +
  scale_colour_manual(values = c("grey50", "white"), guide = "none") + 
  scale_x_discrete(expand = expansion(), position = "top") +
  scale_y_discrete(expand = expansion(), position = "right") +
  labs(x = "Comparison Group",
       y = "Reference Group",
       fill = "-log10(q-value)") + 
  theme(axis.line.x.bottom = element_blank(),
        axis.line.x.top = element_line(colour = "grey50"),
        axis.line.y.left   = element_blank(),
        axis.line.y.right = element_line(colour = "grey50"),
        legend.position = "bottom")
        # legend.position = c(0.02, 0.02),   # bottom-left inside panel
        # legend.justification = c(0, 0),
        # legend.background = element_rect(
        #   fill = scales::alpha("white", 0.8),
        #   colour = NA
        # ))


plt_seizures_binned <- plt_seizures_probs_binned / plt_seizures_heatmap_binned

outfile <- "seizures_age_binned_2.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(6, "in"))
print(plt_seizures_binned)
invisible(dev.off())

plt_seizures_binned
```

## Controlling for age

```{r}
#| echo: false
#| eval: false

df_seizures_lr_age <- df_seizures_age %>%
  select(ID, y = Seizure, 
         Language, Other, Age = Seizure_Age) %>% 
  filter(!is.na(Language), !is.na(Other), !is.na(Age)) 

df_age_quantiles <- tibble(probs = seq(0, 1, by = 0.01))
df_age_quantiles$Age <- quantile(x = df_seizures_lr_age$Age, probs = df_age_quantiles$probs)

ggplot(df_age_quantiles, aes(x = Age, y = probs)) + 
  geom_line() +
  scale_x_continuous(breaks = seq(0, 50, by = 5)) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) + 
  theme_bw()
```

```{r}
#| echo: false
#| eval: false

library(splines)

df_seizures_lr_age <- df_seizures_lr_age %>% 
  filter(Age <= 25) %>% 
  mutate(Age_Centered = Age - mean(Age))

# mod <- glm(y ~ Age_Centered + Language*Other,
#            data = df_seizures_lr_age,
#            family = "binomial")

mod <- glm(y ~ ns(Age_Centered, df = 3) + Language*Other,
           data = df_seizures_lr_age,
           family = "binomial")

summary(mod)
```

```{r}
#| echo: false
#| eval: false

range(df_seizures_lr_age$Age)
```

```{r}
#| echo: false
#| eval: false

age_mean <- mean(df_seizures_lr_age$Age)

age_seq <- seq(1, 30, by = 1)

age_seq_centered <- age_seq - age_mean

df_predict_input <- expand_grid(Age_Centered = age_seq_centered,
                                Language = c(FALSE, TRUE),
                                Other = c(FALSE, TRUE))

pred_link <- predict(mod, newdata = df_predict_input, type = "link", se.fit = TRUE)

df_predict_input$OR <- pred_link$fit
df_predict_input$OR_SE  <- pred_link$se.fit

df_predict_input <- df_predict_input %>% 
  mutate(OR_lwr = OR - 1.96*OR_SE,
         OR_upr = OR + 1.96*OR_SE) 


df_predict_input <- df_predict_input %>% 
  mutate(prob = plogis(OR),
         prob_lwr = plogis(OR_lwr),
         prob_upr = plogis(OR_upr))

df_predict_input <- df_predict_input %>% 
  mutate(group = case_when(!Language & !Other ~ "None",
                           Language & !Other ~ "Language",
                           !Language & Other ~ "Other",
                           Language & Other ~ "Both"),
         group = factor(group, levels = c("None", "Language", "Other", "Both")))
```

```{r}
#| echo: false
#| eval: false

df_plot <- df_predict_input %>% 
  filter(group %in% c("None", "Both"))

ggplot(df_plot, aes(x = Age_Centered + age_mean, y = OR, fill = group)) + 
  geom_ribbon(mapping = aes(ymin = OR_lwr, ymax = OR_upr),
              alpha = 0.3) +
  geom_line() +
  scale_x_continuous(breaks = seq(-100, 100, by = 5)) + 
  scale_y_continuous(breaks = seq(-10, 10, by = 1)) + 
  labs(x = "Age",
       y = "log(Odds Ratio)") + 
  theme_bw()
```

```{r}
#| echo: false
#| eval: false

ggplot(df_plot, aes(x = Age_Centered + age_mean, y = prob, fill = group)) + 
  geom_ribbon(mapping = aes(ymin = prob_lwr, ymax = prob_upr),
              alpha = 0.3) +
  geom_line() +
  scale_x_continuous(breaks = seq(-100, 100, by = 5)) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) + 
  labs(x = "Age",
       y = "Probability") + 
  theme_bw()
```

```{r}
#| echo: false
#| eval: false

emm <- emmeans(mod, ~ Language*Other | Age_Centered, at = list(Age_Centered = age_seq_centered))


emm_contrast <- contrast(emm,
                         method = list("Both vs None" = c(-1, 0, 0, 1)))

df_contrasts <- as_tibble(emm_contrast)
df_contrasts <- df_contrasts %>%
  mutate(lower.CL = estimate - 1.96 * SE,
         upper.CL = estimate + 1.96 * SE)

df_contrasts <- df_contrasts %>% 
  mutate(OR = exp(estimate),
         OR_lower = exp(lower.CL),
         OR_upper = exp(upper.CL))

ggplot(df_contrasts, aes(x = Age_Centered + age_mean, y = estimate)) + 
  geom_ribbon(mapping = aes(ymin = lower.CL, ymax = upper.CL),
              alpha = 0.3) + 
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", col = "red") +
  theme_bw()
```

## Controlling for IQ

```{r}
#| echo: false
#| eval: false

df_seizures_lr_IQ <- df_seizures %>%
  select(ID, y = Seizure, 
         Language = Regressive_Language, 
         Other = Regressive_Other, Age = Seizure_Age, IQ) %>% 
  filter(!is.na(Language), !is.na(Other), !is.na(Age), !is.na(IQ)) 

nrow(df_seizures_lr_IQ)
```

```{r}
#| echo: false
#| eval: false

df_seizures_lr_IQ %>% 
  group_by(Language, Other) %>% 
  mutate(N_per_group = n()) %>% 
  ungroup() %>% 
  group_by(Language, Other, y) %>% 
  mutate(N = n()) %>% 
  ungroup() %>% 
  select(-ID) %>% 
  distinct() %>% 
  mutate(prop = N/N_per_group) %>% 
  select(Language, Other, y, N_per_group, N, prop) %>% 
  arrange(Language, Other, y) %>% 
  filter(y) %>% 
  distinct()
```

------------------------------------------------------------------------

# Prematurity

There are 703 participants with prematurity information:

```{r}
df_regressive_autism %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  group_by(Prematurity) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(Prematurity = ifelse(Prematurity, "Yes", "No"))
```

Broken down by regression group:

```{r}
df_prematurity <- df_regressive_autism %>% 
  select(ID, Language, Other, Prematurity) %>% 
  filter(!is.na(Prematurity), !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_prematurity, groups = df_regressive_groups)
```

```{r fig.width = 9}
df_prematurity_lr <- df_prematurity %>% 
  select(ID, y = Prematurity, 
         Language, Other) 

list_prematurity <- evaluate_model(x = df_prematurity_lr, type = "logistic")


list_prematurity_heatmap <- contrasts_heatmap(x = list_prematurity$contrasts)

plt_prematurity_heatmap <- list_prematurity_heatmap$plot 

plt_prematurity_probs <- regression_probs(model = list_prematurity, 
                                   groups = df_regressive_groups,
                                   ybreaks = seq(0, 1, by = 0.1),
                                   ylims = c(0, 1))

plt_prematurity <- plt_prematurity_probs + plt_prematurity_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Prematurity vs. Regression Status")

outfile <- "prematurity.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_prematurity)
invisible(dev.off())

plt_prematurity
```

------------------------------------------------------------------------

# Sensory processing

To evaluate sensory processing we used the **Short Sensory Profile (SSP)**. The subset of participants with SSP scores breaks down as follows:

```{r}
df_SSP <- df_regressive_autism %>%
  select(ID, Language, Other, contains("SSP")) %>% 
  filter(!is.na(SSP_TOTAL)) %>% 
  filter(!is.na(Language), !is.na(Other))

# Construct data frame for model
df_SSP_lm <- df_SSP %>% 
  select(ID, y = SSP_TOTAL, 
         Language, Other) 

compute_group_summaries(x = df_SSP_lm, groups = df_regressive_groups)
```

## SSP Total Score

```{r}
#| fig-width: 9 

list_SSP_TOT <- evaluate_model(x = df_SSP_lm)

list_SSP_TOT_heatmap <- contrasts_heatmap(x = list_SSP_TOT$contrasts)

plt_SSP_TOT_heatmap <- list_SSP_TOT_heatmap$plot 

plt_SSP_TOT_scatter <- regression_scatter(model = list_SSP_TOT, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(50, 200),
                                     ybreaks = seq(0, 200, by = 10))

plt_SSP_TOT_scatter <- plt_SSP_TOT_scatter +
  labs(y = "SSP Total Score")

plt_SSP_TOT <- plt_SSP_TOT_scatter + plt_SSP_TOT_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SSP Total vs. Regression Status")

outfile <- "SSP_TOT.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SSP_TOT)
invisible(dev.off())

plt_SSP_TOT
```

## SSP Auditory Filtering

```{r}
#| fig-width: 9 

# Construct data frame for model
df_SSP_AUD_FILT_lm <- df_SSP %>% 
  select(ID, y = SSP_AUD_FILTER, 
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other))

list_SSP_AUD_FILT <- evaluate_model(x = df_SSP_AUD_FILT_lm)

list_SSP_AUD_FILT_heatmap <- contrasts_heatmap(x = list_SSP_AUD_FILT$contrasts)

plt_SSP_AUD_FILT_heatmap <- list_SSP_AUD_FILT_heatmap$plot 

plt_SSP_AUD_FILT_scatter <- regression_scatter(model = list_SSP_AUD_FILT, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 35),
                                     ybreaks = seq(0, 200, by = 5))

plt_SSP_AUD_FILT_scatter <- plt_SSP_AUD_FILT_scatter +
  labs(y = "SSP Auditory Filtering Score")

plt_SSP_AUD_FILT <- plt_SSP_AUD_FILT_scatter + plt_SSP_AUD_FILT_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SSP Auditory Filtering vs. Regression Status")

outfile <- "SSP_AUD_FILT.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SSP_AUD_FILT)
invisible(dev.off())

plt_SSP_AUD_FILT
```

## SSP Visual-Auditory

```{r}
#| fig-width: 9 

# Construct data frame for model
df_SSP_VIS_AUD_lm <- df_SSP %>% 
  select(ID, y = SSP_VIS_AUD, 
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other))

list_SSP_VIS_AUD <- evaluate_model(x = df_SSP_VIS_AUD_lm)

list_SSP_VIS_AUD_heatmap <- contrasts_heatmap(x = list_SSP_VIS_AUD$contrasts)

plt_SSP_VIS_AUD_heatmap <- list_SSP_VIS_AUD_heatmap$plot 

plt_SSP_VIS_AUD_scatter <- regression_scatter(model = list_SSP_VIS_AUD, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 30),
                                     ybreaks = seq(0, 200, by = 5))

plt_SSP_VIS_AUD_scatter <- plt_SSP_VIS_AUD_scatter +
  labs(y = "SSP Visual/Auditory Score")

plt_SSP_VIS_AUD <- plt_SSP_VIS_AUD_scatter + plt_SSP_VIS_AUD_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SSP Visual/Auditory vs. Regression Status")

outfile <- "SSP_VIS_AUD.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SSP_VIS_AUD)
invisible(dev.off())

plt_SSP_VIS_AUD
```

------------------------------------------------------------------------

# Socialization

To evaluate socialization we used the **Social Responsiveness Scale (SRS)**. The subset of participants with SRS scores breaks down as follows:

```{r}
df_SRS <- df_regressive_autism %>%
  select(ID, Language, Other, contains("SRS")) %>% 
  filter(!is.na(SRS_Total)) %>% 
  filter(!is.na(Language), !is.na(Other))

compute_group_summaries(x = df_SRS, groups = df_regressive_groups)
```

## SRS Total Score

```{r}
#| fig-width: 9 

# Construct data frame for model
df_SRS_lm <- df_SRS %>% 
  select(ID, y = SRS_Total, 
         Language, Other) 

list_SRS <- evaluate_model(x = df_SRS_lm)

list_SRS_heatmap <- contrasts_heatmap(x = list_SRS$contrasts)

plt_SRS_heatmap <- list_SRS_heatmap$plot 

plt_SRS_scatter <- regression_scatter(model = list_SRS, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ybreaks = seq(0, 200, by = 10))

plt_SRS_scatter <- plt_SRS_scatter +
  labs(y = "SRS Total Score")

plt_SRS <- plt_SRS_scatter + plt_SRS_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Social Responsiveness Questionnaire (SRS) vs. Regression Status")

outfile <- "SRS.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SRS)
invisible(dev.off())

plt_SRS
```

## SRS Custom Total Score

The custom total score is the sum of Social Awareness, Social Cognition, Social Communication and Social Motivation, excluding repetitive behaviours.

```{r}
#| fig-width: 9 

df_SRS_custom_lm <- df_SRS %>% 
  mutate(y = SRS_SocialAware + SRS_SocialCog + SRS_SocialComm + SRS_SocialMotiv) %>% 
  select(ID, y, Language, Other) %>% 
  filter(!is.na(y))

list_SRS_custom <- evaluate_model(x = df_SRS_custom_lm)

list_SRS_custom_heatmap <- contrasts_heatmap(x = list_SRS_custom$contrasts)

plt_SRS_custom_heatmap <- list_SRS_custom_heatmap$plot 

plt_SRS_custom_scatter <- regression_scatter(model = list_SRS_custom, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ybreaks = seq(0, 1000, by = 20))

plt_SRS_custom_scatter <- plt_SRS_custom_scatter +
  labs(y = "SRS Custom Total Score")

plt_SRS_custom <- plt_SRS_custom_scatter + plt_SRS_custom_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Social Responsiveness Questionnaire (SRS) vs. Regression Status")

outfile <- "SRS_custom.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SRS_custom)
invisible(dev.off())

plt_SRS_custom
```

## Controlling for IQ

```{r}
df_SRS_IQ <- df_regressive_autism %>%
  select(ID, Language, Other, contains("SRS"), IQ) %>% 
  filter(!is.na(SRS_Total), !is.na(IQ), 
         !is.na(Language), !is.na(Other))

compute_group_summaries(x = df_SRS_IQ, groups = df_regressive_groups)
```

```{r}
model <- lm(SRS_Total ~ Language*Other + IQ, data = df_SRS_IQ)
summary(model)
```

## SCQ Total Score

```{r}
file <- "data/raw/SCQ/SCQ_SCQTOT Total score.xlsx"
df_scq <- read_excel(file)

df_scq %>% 
  select(ID = indexid, y = numeric_value) %>% 
    inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r fig.width = 9}
df_scq_lm <- df_scq %>% 
  select(ID = indexid, y = numeric_value) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_scq <- evaluate_model(x = df_scq_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_scq_heatmap <- contrasts_heatmap(x = list_scq$contrasts)

plt_scq_heatmap <- list_scq_heatmap$plot


plt_scq_scatter <- regression_scatter(model = list_scq, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_scq_scatter <- plt_scq_scatter +
labs(y = "SCQ Total Score")

plt_scq <- plt_scq_scatter + plt_scq_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SCQ vs. Regression Status")

outfile <- "scq.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_scq)
invisible(dev.off())

plt_scq
```

------------------------------------------------------------------------

# Language

To evaluate language, we used the **Children's Communication Checklist (CCC)**. The subset of participants with CCC scores breaks down as follows:

```{r}
df_language <- df_regressive_autism %>%
  select(ID, Language, Other, contains("CCC"), IQ)

df_language <- df_language %>% 
  mutate(Structural_1 = CCC_Speech + CCC_Syntax + CCC_Semantics + CCC_Coherence,
         Pragmatic_1 = CCC_Inapp_Init + CCC_Context + CCC_NonVerbalComm + CCC_Stereotyped) %>% 
  mutate(Structural_2 = CCC_Speech + CCC_Syntax + CCC_Semantics,
         Pragmatic_2 = CCC_Inapp_Init + CCC_Context + CCC_NonVerbalComm + CCC_Stereotyped + CCC_Coherence) 

df_language <- df_language %>% 
  filter(!is.na(Language), !is.na(Other), !is.na(Structural_1))

compute_group_summaries(x = df_language, groups = df_regressive_groups)
```

## Structural Language

The structural language score is the sum of Speech, Syntax and Semantics. Additionally, in version 1, Coherence is counted towards Structural. In version 2, Coherence is counted towards Pragmatic.

```{r}
#| fig-width: 9 

# Construct data frame for model
df_lang_v1_struct_lm <- df_language %>% 
  select(ID, y = Structural_1, 
         Language, Other) 

list_lang_v1_struct <- evaluate_model(x = df_lang_v1_struct_lm)

list_lang_v1_struct_heatmap <- contrasts_heatmap(x = list_lang_v1_struct$contrasts)

plt_lang_v1_struct_heatmap <- list_lang_v1_struct_heatmap$plot 

plt_lang_v1_struct_scatter <- regression_scatter(model = list_lang_v1_struct, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 60), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v1_struct_scatter <- plt_lang_v1_struct_scatter +
  labs(y = "Structural Language Score")

plt_lang_v1_struct <- plt_lang_v1_struct_scatter + plt_lang_v1_struct_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Structural Language (v1) vs. Regression Status")

outfile <- "lang_v1_struct.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v1_struct)
invisible(dev.off())

plt_lang_v1_struct
```

```{r}
#| fig-width: 9 

# Construct data frame for model
df_lang_v2_struct_lm <- df_language %>% 
  select(ID, y = Structural_2, 
         Language, Other) 

list_lang_v2_struct <- evaluate_model(x = df_lang_v2_struct_lm)

list_lang_v2_struct_heatmap <- contrasts_heatmap(x = list_lang_v2_struct$contrasts)

plt_lang_v2_struct_heatmap <- list_lang_v2_struct_heatmap$plot 

plt_lang_v2_struct_scatter <- regression_scatter(model = list_lang_v2_struct, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 60), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v2_struct_scatter <- plt_lang_v2_struct_scatter +
  labs(y = "Structural Language Score")

plt_lang_v2_struct <- plt_lang_v2_struct_scatter + plt_lang_v2_struct_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Structural Language (v2) vs. Regression Status")

outfile <- "lang_v2_struct.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v2_struct)
invisible(dev.off())

plt_lang_v2_struct
```

## Pragmatic Language

In version 1, Coherence is counted towards Structural. In version 2, Coherence is counted towards Pragmatic.

```{r}
#| fig-width: 9 

# Conprag data frame for model
df_lang_v1_prag_lm <- df_language %>% 
  select(ID, y = Pragmatic_1, 
         Language, Other) 

list_lang_v1_prag <- evaluate_model(x = df_lang_v1_prag_lm)

list_lang_v1_prag_heatmap <- contrasts_heatmap(x = list_lang_v1_prag$contrasts)

plt_lang_v1_prag_heatmap <- list_lang_v1_prag_heatmap$plot 

plt_lang_v1_prag_scatter <- regression_scatter(model = list_lang_v1_prag, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 50), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v1_prag_scatter <- plt_lang_v1_prag_scatter +
  labs(y = "Pragmatic Language Score")

plt_lang_v1_prag <- plt_lang_v1_prag_scatter + plt_lang_v1_prag_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Pragmatic Language (v1) vs. Regression Status")

outfile <- "lang_v1_prag.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v1_prag)
invisible(dev.off())

plt_lang_v1_prag
```

```{r}
#| fig-width: 9 

# Construct data frame for model
df_lang_v2_prag_lm <- df_language %>% 
  select(ID, y = Pragmatic_2, 
         Language, Other) 

list_lang_v2_prag <- evaluate_model(x = df_lang_v2_prag_lm)

list_lang_v2_prag_heatmap <- contrasts_heatmap(x = list_lang_v2_prag$contrasts)

plt_lang_v2_prag_heatmap <- list_lang_v2_prag_heatmap$plot 

plt_lang_v2_prag_scatter <- regression_scatter(model = list_lang_v2_prag, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(0, 50), 
                                     ybreaks = seq(0, 200, by = 10))

plt_lang_v2_prag_scatter <- plt_lang_v2_prag_scatter +
  labs(y = "Pragmatic Language Score")

plt_lang_v2_prag <- plt_lang_v2_prag_scatter + plt_lang_v2_prag_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "Pragmatic Language (v2) vs. Regression Status")

outfile <- "lang_v2_prag.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_lang_v2_prag)
invisible(dev.off())

plt_lang_v2_prag
```

## SIDC

```{r}
#| fig-width: 9 

# Construct data frame for model
df_SIDC_lm <- df_language %>% 
  select(ID, y = CCC_SIDC, IQ,
         Language, Other) %>% 
  filter(!is.na(Language), !is.na(Other)) %>% 
  filter(!is.na(y))

# Evaluate model
list_SIDC <- evaluate_model(x = df_SIDC_lm)

list_SIDC_heatmap <- contrasts_heatmap(x = list_SIDC$contrasts)

plt_SIDC_heatmap <- list_SIDC_heatmap$plot 

plt_SIDC_scatter <- regression_scatter(model = list_SIDC, 
                                     groups = df_regressive_groups,
                                     point_alpha_values = c(0.5, 0.5, 0.5, 0.5),
                                     ylims = c(-35, 35),
                                     ybreaks = seq(-200, 200, by = 10))

plt_SIDC_scatter <- plt_SIDC_scatter +
  labs(y = "SIDC Score")

plt_SIDC <- plt_SIDC_scatter + plt_SIDC_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "SIDC vs. Regression Status")

outfile <- "lang_SIDC.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_SIDC)
invisible(dev.off())

plt_SIDC
```

## CTOPP

### Phonological Awareness

```{r}
file <- "data/raw/CTOPP/CTOPP_CTPACS Phonological Awareness Composite Score.xlsx"
df_ctopp_pa  <- read_excel(file) %>% 
  select(ID = indexid, score = numeric_value) %>% 
  filter(!is.na(score))

df_ctopp_pa <- df_ctopp_pa %>% 
  group_by(ID) %>% 
  summarise(score = mean(score)) %>% 
  ungroup()

df_ctopp_pa <- df_ctopp_pa %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_ctopp_pa <- evaluate_model(x = df_ctopp_pa, type = "linear")

# Generate heatmap from group contrasts
list_ctopp_pa_heatmap <- contrasts_heatmap(x = list_ctopp_pa$contrasts)

plt_ctopp_pa_heatmap <- list_ctopp_pa_heatmap$plot

plt_ctopp_pa_scatter <- regression_scatter(model = list_ctopp_pa, 
                                          groups = df_regressive_groups)

plt_ctopp_pa_scatter <- plt_ctopp_pa_scatter +
labs(y = "CTOPP Phonological Awareness")

plt_ctopp_pa <- plt_ctopp_pa_scatter + plt_ctopp_pa_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "CTOPP vs. Regression Status")

outfile <- "ctopp_pa.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ctopp_pa)
invisible(dev.off())

plt_ctopp_pa
```

### Phonological Memory

```{r}
file <- "data/raw/CTOPP/CTOPP_CTPMCS Phonological Memory Composite score.xlsx"
df_ctopp_pm  <- read_excel(file) %>% 
  select(ID = indexid, score = numeric_value) %>% 
  filter(!is.na(score))

df_ctopp_pm <- df_ctopp_pm %>% 
  group_by(ID) %>% 
  summarise(score = mean(score)) %>% 
  ungroup()

df_ctopp_pm <- df_ctopp_pm %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_ctopp_pm <- evaluate_model(x = df_ctopp_pm, type = "linear")

# Generate heatmap from group contrasts
list_ctopp_pm_heatmap <- contrasts_heatmap(x = list_ctopp_pm$contrasts)

plt_ctopp_pm_heatmap <- list_ctopp_pm_heatmap$plot

plt_ctopp_pm_scatter <- regression_scatter(model = list_ctopp_pm, 
                                          groups = df_regressive_groups)

plt_ctopp_pm_scatter <- plt_ctopp_pm_scatter +
labs(y = "CTOPP Phonological Memory")

plt_ctopp_pm <- plt_ctopp_pm_scatter + plt_ctopp_pm_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "CTOPP vs. Regression Status")

outfile <- "ctopp_pm.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ctopp_pm)
invisible(dev.off())

plt_ctopp_pm
```

### Rapid Naming

```{r}
file <- "data/raw/CTOPP/CTOPP_CTRNCS Rapid naming Composite score.xlsx"
df_ctopp_rn  <- read_excel(file) %>% 
  select(ID = indexid, score = numeric_value) %>% 
  filter(!is.na(score))

df_ctopp_rn <- df_ctopp_rn %>% 
  group_by(ID) %>% 
  summarise(score = mean(score)) %>% 
  ungroup()

df_ctopp_rn <- df_ctopp_rn %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_ctopp_rn <- evaluate_model(x = df_ctopp_rn, type = "linear")

# Generate heatmap from group contrasts
list_ctopp_rn_heatmap <- contrasts_heatmap(x = list_ctopp_rn$contrasts)

plt_ctopp_rn_heatmap <- list_ctopp_rn_heatmap$plot

plt_ctopp_rn_scatter <- regression_scatter(model = list_ctopp_rn, 
                                          groups = df_regressive_groups)

plt_ctopp_rn_scatter <- plt_ctopp_rn_scatter +
labs(y = "CTOPP Rapid Naming")

plt_ctopp_rn <- plt_ctopp_rn_scatter + plt_ctopp_rn_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "CTOPP vs. Regression Status")

outfile <- "ctopp_rn.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_ctopp_rn)
invisible(dev.off())

plt_ctopp_rn
```

## OWLS-2

### Oral Expression

```{r}
file <- "data/raw/Language/OWLS/Oral Expression standard score 2nd edition.xlsx"
df_owls2_oe <- readxl::read_excel(file) %>% 
  select(ID = indexid, score = numeric_value)

df_owls2_oe %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r}
df_owls2_oe_lm <- df_owls2_oe %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls2_oe <- evaluate_model(x = df_owls2_oe_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls2_oe_heatmap <- contrasts_heatmap(x = list_owls2_oe$contrasts)

plt_owls2_oe_heatmap <- list_owls2_oe_heatmap$plot


plt_owls2_oe_scatter <- regression_scatter(model = list_owls2_oe, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls2_oe_scatter <- plt_owls2_oe_scatter +
labs(y = "OWLS-2 Oral Expression")

plt_owls2_oe <- plt_owls2_oe_scatter + plt_owls2_oe_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS-2 Oral Expression vs. Regression Status")

outfile <- "owls2_oe.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls2_oe)
invisible(dev.off())

plt_owls2_oe
```

------------------------------------------------------------------------

### Listening Comprehension

```{r}
file <- "data/raw/Language/OWLS/Listening Comprehension standard score 2nd edition.xlsx"
df_owls2_lc <- readxl::read_excel(file) %>% 
  select(ID = indexid, score = numeric_value)

df_owls2_lc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r}
df_owls2_lc_lm <- df_owls2_lc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls2_lc <- evaluate_model(x = df_owls2_lc_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls2_lc_heatmap <- contrasts_heatmap(x = list_owls2_lc$contrasts)

plt_owls2_lc_heatmap <- list_owls2_lc_heatmap$plot


plt_owls2_lc_scatter <- regression_scatter(model = list_owls2_lc, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls2_lc_scatter <- plt_owls2_lc_scatter +
labs(y = "OWLS-2 Listening Comprehension")

plt_owls2_lc <- plt_owls2_lc_scatter + plt_owls2_lc_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS-2 Listening Comprehension vs. Regression Status")

outfile <- "owls2_lc.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls2_lc)
invisible(dev.off())

plt_owls2_lc
```

------------------------------------------------------------------------

### Oral Language Composite

```{r}
file <- "data/raw/Language/OWLS/Oral Language Composite standard score 2nd edition.xlsx"
df_owls2_olc <- readxl::read_excel(file) %>% 
  select(ID = indexid, score = numeric_value)

df_owls2_olc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r}
df_owls2_olc_lm <- df_owls2_olc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls2_olc <- evaluate_model(x = df_owls2_olc_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls2_olc_heatmap <- contrasts_heatmap(x = list_owls2_olc$contrasts)

plt_owls2_olc_heatmap <- list_owls2_olc_heatmap$plot


plt_owls2_olc_scatter <- regression_scatter(model = list_owls2_olc, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls2_olc_scatter <- plt_owls2_olc_scatter +
labs(y = "OWLS-2 Oral Language Composite")

plt_owls2_olc <- plt_owls2_olc_scatter + plt_owls2_olc_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS-2 Oral Language Composite vs. Regression Status")

outfile <- "owls2_olc.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls2_olc)
invisible(dev.off())

plt_owls2_olc
```

## OWLS

### Oral Expression

```{r}
file <- "data/raw/Language/OWLS/OWLS_OWLOESS Oral Expression.xlsx"
df_owls_oe <- readxl::read_excel(file) %>% 
  select(ID = indexid, score = numeric_value)

df_owls_oe %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r}
df_owls_oe_lm <- df_owls_oe %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls_oe <- evaluate_model(x = df_owls_oe_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls_oe_heatmap <- contrasts_heatmap(x = list_owls_oe$contrasts)

plt_owls_oe_heatmap <- list_owls_oe_heatmap$plot


plt_owls_oe_scatter <- regression_scatter(model = list_owls_oe, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls_oe_scatter <- plt_owls_oe_scatter +
labs(y = "OWLS Oral Expression")

plt_owls_oe <- plt_owls_oe_scatter + plt_owls_oe_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS Oral Expression vs. Regression Status")

outfile <- "owls_oe.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls_oe)
invisible(dev.off())

plt_owls_oe
```

------------------------------------------------------------------------

### Listening Comprehension

```{r}
file <- "data/raw/Language/OWLS/OWLS_OWLLCSS Listening Comprehension.xlsx"
df_owls_lc <- readxl::read_excel(file) %>% 
  select(ID = indexid, score = numeric_value)

df_owls_lc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r}
df_owls_lc_lm <- df_owls_lc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls_lc <- evaluate_model(x = df_owls_lc_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls_lc_heatmap <- contrasts_heatmap(x = list_owls_lc$contrasts)

plt_owls_lc_heatmap <- list_owls_lc_heatmap$plot


plt_owls_lc_scatter <- regression_scatter(model = list_owls_lc, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls_lc_scatter <- plt_owls_lc_scatter +
labs(y = "OWLS Listening Comprehension")

plt_owls_lc <- plt_owls_lc_scatter + plt_owls_lc_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS Listening Comprehension vs. Regression Status")

outfile <- "owls_lc.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls_lc)
invisible(dev.off())

plt_owls_lc
```

------------------------------------------------------------------------

### Oral Composite

```{r}
file <- "data/raw/Language/OWLS/OWLS_OWLOCSS Oral Composite.xlsx"
df_owls_oc <- readxl::read_excel(file) %>% 
  select(ID = indexid, score = numeric_value)

df_owls_oc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r}
df_owls_oc_lm <- df_owls_oc %>% 
  select(ID, y = score) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls_oc <- evaluate_model(x = df_owls_oc_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls_oc_heatmap <- contrasts_heatmap(x = list_owls_oc$contrasts)

plt_owls_oc_heatmap <- list_owls_oc_heatmap$plot


plt_owls_oc_scatter <- regression_scatter(model = list_owls_oc, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls_oc_scatter <- plt_owls_oc_scatter +
labs(y = "OWLS Oral Composite")

plt_owls_oc <- plt_owls_oc_scatter + plt_owls_oc_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS Oral Composite vs. Regression Status")

outfile <- "owls_oc.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls_oc)
invisible(dev.off())

plt_owls_oc
```

## OWLS combined

### Oral Expression

```{r}
df_owls_combined_oe <- df_regressive_autism %>% 
  select(ID, Language, Other) %>% 
  left_join(df_owls2_oe, by = "ID") %>% 
  rename(owls2_score = score) %>% 
  left_join(df_owls_oe, by = "ID") %>% 
  rename(owls_score = score) %>% 
  mutate(score = ifelse(!is.na(owls2_score), owls2_score, owls_score)) %>% 
  select(-owls2_score, -owls_score)


df_owls_combined_oe_lm <- df_owls_combined_oe %>% 
  rename(y = score) %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls_combined_oe <- evaluate_model(x = df_owls_combined_oe_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls_combined_oe_heatmap <- contrasts_heatmap(x = list_owls_combined_oe$contrasts)

plt_owls_combined_oe_heatmap <- list_owls_combined_oe_heatmap$plot


plt_owls_combined_oe_scatter <- regression_scatter(model = list_owls_combined_oe, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls_combined_oe_scatter <- plt_owls_combined_oe_scatter +
labs(y = "Oral Expression")

plt_owls_combined_oe <- plt_owls_combined_oe_scatter + plt_owls_combined_oe_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS Combined Oral Expression vs. Regression Status")

outfile <- "owls_combined_oe.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls_combined_oe)
invisible(dev.off())

plt_owls_combined_oe
```

### Listening Comprehension

```{r}
df_owls_combined_lc <- df_regressive_autism %>% 
  select(ID, Language, Other) %>% 
  left_join(df_owls2_lc, by = "ID") %>% 
  rename(owls2_score = score) %>% 
  left_join(df_owls_lc, by = "ID") %>% 
  rename(owls_score = score) %>% 
  mutate(score = ifelse(!is.na(owls2_score), owls2_score, owls_score)) %>% 
  select(-owls2_score, -owls_score)

df_owls_combined_lc_lm <- df_owls_combined_lc %>% 
  rename(y = score) %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls_combined_lc <- evaluate_model(x = df_owls_combined_lc_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls_combined_lc_heatmap <- contrasts_heatmap(x = list_owls_combined_lc$contrasts)

plt_owls_combined_lc_heatmap <- list_owls_combined_lc_heatmap$plot


plt_owls_combined_lc_scatter <- regression_scatter(model = list_owls_combined_lc, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls_combined_lc_scatter <- plt_owls_combined_lc_scatter +
labs(y = "Listening Comprehension")

plt_owls_combined_lc <- plt_owls_combined_lc_scatter + plt_owls_combined_lc_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS Combined Listening Comprehension vs. Regression Status")

outfile <- "owls_combined_lc.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls_combined_lc)
invisible(dev.off())

plt_owls_combined_lc
```

### Oral Language Composite

```{r}
df_owls_combined_olc <- df_regressive_autism %>% 
  select(ID, Language, Other) %>% 
  left_join(df_owls2_olc, by = "ID") %>% 
  rename(owls2_score = score) %>% 
  left_join(df_owls_oc, by = "ID") %>% 
  rename(owls_score = score) %>% 
  mutate(score = ifelse(!is.na(owls2_score), owls2_score, owls_score)) %>% 
  select(-owls2_score, -owls_score)

df_owls_combined_olc_lm <- df_owls_combined_olc %>% 
  rename(y = score) %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_owls_combined_olc <- evaluate_model(x = df_owls_combined_olc_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_owls_combined_olc_heatmap <- contrasts_heatmap(x = list_owls_combined_olc$contrasts)

plt_owls_combined_olc_heatmap <- list_owls_combined_olc_heatmap$plot


plt_owls_combined_olc_scatter <- regression_scatter(model = list_owls_combined_olc, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_owls_combined_olc_scatter <- plt_owls_combined_olc_scatter +
labs(y = "Oral Language Composite")

plt_owls_combined_olc <- plt_owls_combined_olc_scatter + plt_owls_combined_olc_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "OWLS Combined Oral Language Composite vs. Regression Status")

outfile <- "owls_combined_olc.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_owls_combined_olc)
invisible(dev.off())

plt_owls_combined_olc
```

## Controlling for IQ

```{r}
file <- "data/raw/IQ/aggregate_global_ability_estimate___all_scores_2026-04-29T21_57_22.803Z.xlsx"
df_performance_IQ <- readxl::read_excel(file) %>% 
  select(ID = indexid, general_ability_composite_estimate, nonverbal_score)
```

```{r}
df_ctopp_pa_IQ <- df_ctopp_pa %>% 
  left_join(df_performance_IQ, by = "ID") %>% 
  filter(!is.na(nonverbal_score))

df_ctopp_pa_IQ %>% 
  group_by(Language, Other) %>% 
  count()
```

```{r}
df_ctopp_rn_IQ <- df_ctopp_rn %>% 
  left_join(df_performance_IQ, by = "ID") %>% 
  filter(!is.na(nonverbal_score))

df_ctopp_rn_IQ %>% 
  group_by(Language, Other) %>% 
  count()
```

```{r}
df_owls2_olc_IQ <- df_owls2_olc_lm %>% 
  left_join(df_performance_IQ, by = "ID") %>% 
  filter(!is.na(nonverbal_score))
df_owls2_olc_IQ %>% 
  group_by(Language, Other) %>% 
  count()
```

This is not feasible.

------------------------------------------------------------------------

# Repetitive behaviours

To evaluate repetitive behaviours, we used the **RBS-R**. The subset of participants with RBS-R scores breaks down as follows:

```{r}
file <- "data/processed/RBS-R/RBS.csv"
df_rbs <- read_csv(file, show_col_types = FALSE)

df_rbs %>% 
  select(ID, y = RBSR_RBSCPT) %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

## RBS-R Overall

```{r fig.width = 9}
df_rbs_all <- df_rbs %>% 
  select(ID, y = RBSR_RBSALLT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_all <- evaluate_model(x = df_rbs_all, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_all_heatmap <- contrasts_heatmap(x = list_rbs_all$contrasts)

plt_rbs_all_heatmap <- list_rbs_all_heatmap$plot


plt_rbs_all_scatter <- regression_scatter(model = list_rbs_all, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_all_scatter <- plt_rbs_all_scatter +
labs(y = "RBS-R Overall")

plt_rbs_all <- plt_rbs_all_scatter + plt_rbs_all_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Overall vs. Regression Status")

outfile <- "rbs_all.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_all)
invisible(dev.off())

plt_rbs_all
```

## RBS-R original sub-domains

### Compulsive Behaviour

```{r fig.width = 9}
df_rbs_cpt <- df_rbs %>% 
  select(ID, y = RBSR_RBSCPT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_cpt <- evaluate_model(x = df_rbs_cpt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_cpt_heatmap <- contrasts_heatmap(x = list_rbs_cpt$contrasts)

plt_rbs_cpt_heatmap <- list_rbs_cpt_heatmap$plot


plt_rbs_cpt_scatter <- regression_scatter(model = list_rbs_cpt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          ylims = c(0, 25))

plt_rbs_cpt_scatter <- plt_rbs_cpt_scatter +
labs(y = "RBS-R Compulsive Behaviour")

plt_rbs_cpt <- plt_rbs_cpt_scatter + plt_rbs_cpt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Compulsive Behaviour vs. Regression Status")

outfile <- "rbs_cpt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_cpt)
invisible(dev.off())

plt_rbs_cpt
```

### Restricted Behaviour

```{r fig.width = 9}
df_rbs_rst <- df_rbs %>% 
  select(ID, y = RBSR_RBSRST) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_rst <- evaluate_model(x = df_rbs_rst, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_rst_heatmap <- contrasts_heatmap(x = list_rbs_rst$contrasts)

plt_rbs_rst_heatmap <- list_rbs_rst_heatmap$plot


plt_rbs_rst_scatter <- regression_scatter(model = list_rbs_rst, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_rst_scatter <- plt_rbs_rst_scatter +
labs(y = "RBS-R Restricted Behaviour")

plt_rbs_rst <- plt_rbs_rst_scatter + plt_rbs_rst_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Restricted Behaviour vs. Regression Status")

outfile <- "rbs_rst.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_rst)
invisible(dev.off())

plt_rbs_rst
```

### Ritualistic Behaviour

```{r fig.width = 9}
df_rbs_rtt <- df_rbs %>% 
  select(ID, y = RBSR_RBSRTT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_rtt <- evaluate_model(x = df_rbs_rtt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_rtt_heatmap <- contrasts_heatmap(x = list_rbs_rtt$contrasts)

plt_rbs_rtt_heatmap <- list_rbs_rtt_heatmap$plot


plt_rbs_rtt_scatter <- regression_scatter(model = list_rbs_rtt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_rtt_scatter <- plt_rbs_rtt_scatter +
labs(y = "RBS-R Ritual Behaviour")

plt_rbs_rtt <- plt_rbs_rtt_scatter + plt_rbs_rtt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Ritual Behaviour vs. Regression Status")

outfile <- "rbs_rtt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_rtt)
invisible(dev.off())

plt_rbs_rtt
```

### Self-Injurious Behaviour

```{r fig.width = 9}
df_rbs_sit <- df_rbs %>% 
  select(ID, y = RBSR_RBSSIT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_sit <- evaluate_model(x = df_rbs_sit, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_sit_heatmap <- contrasts_heatmap(x = list_rbs_sit$contrasts)

plt_rbs_sit_heatmap <- list_rbs_sit_heatmap$plot


plt_rbs_sit_scatter <- regression_scatter(model = list_rbs_sit, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_sit_scatter <- plt_rbs_sit_scatter +
labs(y = "RBS-R Self-Injurious Behaviour")

plt_rbs_sit <- plt_rbs_sit_scatter + plt_rbs_sit_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Self-Injurious Behaviour vs. Regression Status")

outfile <- "rbs_sit.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_sit)
invisible(dev.off())

plt_rbs_sit
```

### Sameness Behaviour

```{r fig.width = 9}
df_rbs_smt <- df_rbs %>% 
  select(ID, y = RBSR_RBSSMT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_smt <- evaluate_model(x = df_rbs_smt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_smt_heatmap <- contrasts_heatmap(x = list_rbs_smt$contrasts)

plt_rbs_smt_heatmap <- list_rbs_smt_heatmap$plot


plt_rbs_smt_scatter <- regression_scatter(model = list_rbs_smt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_smt_scatter <- plt_rbs_smt_scatter +
labs(y = "RBS-R Sameness Behaviour")

plt_rbs_smt <- plt_rbs_smt_scatter + plt_rbs_smt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Sameness Behaviour vs. Regression Status")

outfile <- "rbs_smt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_smt)
invisible(dev.off())

plt_rbs_smt
```

### Stereotyped Behaviour

```{r fig.width = 9}
df_rbs_stt <- df_rbs %>% 
  select(ID, y = RBSR_RBSSTT) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_stt <- evaluate_model(x = df_rbs_stt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_stt_heatmap <- contrasts_heatmap(x = list_rbs_stt$contrasts)

plt_rbs_stt_heatmap <- list_rbs_stt_heatmap$plot


plt_rbs_stt_scatter <- regression_scatter(model = list_rbs_stt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_stt_scatter <- plt_rbs_stt_scatter +
labs(y = "RBS-R Stereotyped Behaviour")

plt_rbs_stt <- plt_rbs_stt_scatter + plt_rbs_stt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Stereotyped Behaviour vs. Regression Status")

outfile <- "rbs_stt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_stt)
invisible(dev.off())

plt_rbs_stt
```

## RBS-R five-factor model

In the five-factor model, the Ritualistic and Sameness sub-domains are summed together. The remaining sub-domains are left as is.

```{r fig.width = 9}
df_rbs_rit_smt <- df_rbs %>% 
  mutate(y = RBSR_RBSRTT + RBSR_RBSSMT) %>% 
  select(ID, y) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_rit_smt <- evaluate_model(x = df_rbs_rit_smt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_rit_smt_heatmap <- contrasts_heatmap(x = list_rbs_rit_smt$contrasts)

plt_rbs_rit_smt_heatmap <- list_rbs_rit_smt_heatmap$plot


plt_rbs_rit_smt_scatter <- regression_scatter(model = list_rbs_rit_smt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_rit_smt_scatter <- plt_rbs_rit_smt_scatter +
labs(y = "RBS-R Ritualistic/Sameness Behaviour")

plt_rbs_rit_smt <- plt_rbs_rit_smt_scatter + plt_rbs_rit_smt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Ritualistic/Sameness Behaviour vs. Regression Status")

outfile <- "rbs_5_factor_rit_smt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_rit_smt)
invisible(dev.off())

plt_rbs_rit_smt
```

## RBS-R four-factor model

In the five-factor model, the Compulsive, Ritualistic and Sameness sub-domains are summed together. The remaining sub-domains are left as is.

```{r fig.width = 9}
df_rbs_cpt_rit_smt <- df_rbs %>% 
  mutate(y = RBSR_RBSCPT + RBSR_RBSRTT + RBSR_RBSSMT) %>% 
  select(ID, y) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_cpt_rit_smt <- evaluate_model(x = df_rbs_cpt_rit_smt, type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_cpt_rit_smt_heatmap <- contrasts_heatmap(x = list_rbs_cpt_rit_smt$contrasts)

plt_rbs_cpt_rit_smt_heatmap <- list_rbs_cpt_rit_smt_heatmap$plot


plt_rbs_cpt_rit_smt_scatter <- regression_scatter(model = list_rbs_cpt_rit_smt, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4))

plt_rbs_cpt_rit_smt_scatter <- plt_rbs_cpt_rit_smt_scatter +
labs(y = "RBS-R Compulsive/Ritualistic/Sameness Behaviour")

plt_rbs_cpt_rit_smt <- plt_rbs_cpt_rit_smt_scatter + plt_rbs_cpt_rit_smt_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS-R Compulsive/Ritualistic/Sameness Behaviour vs. Regression Status") 

outfile <- "rbs_4_factor_cpt_rit_smt.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_cpt_rit_smt)
invisible(dev.off())

plt_rbs_cpt_rit_smt
```

## RBS-R endorsed

```{r}
file <- "data/raw/RBS-R/Overall number of items endorsed.xlsx"
df_rbs_endorsed <- readxl::read_excel(file)

df_rbs_endorsed_lm <- df_rbs_endorsed %>% 
  select(ID = indexid, y = numeric_value) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_rbs_endorsed <- evaluate_model(x = df_rbs_endorsed_lm,
                                       type = "mixed-effects")

# Generate heatmap from group contrasts
list_rbs_endorsed_heatmap <- contrasts_heatmap(x = list_rbs_endorsed$contrasts)

plt_rbs_endorsed_heatmap <- list_rbs_endorsed_heatmap$plot


plt_rbs_endorsed_scatter <- regression_scatter(model = list_rbs_endorsed, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          ylims = c(0, 45),
                                          ybreaks = seq(0, 100, by = 10))

plt_rbs_endorsed_scatter <- plt_rbs_endorsed_scatter +
labs(y = "RBS Items Endorsed")

plt_rbs_endorsed <- plt_rbs_endorsed_scatter + plt_rbs_endorsed_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "RBS Endorsed vs. Regression Status")

outfile <- "rbs_endorsed.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_rbs_endorsed)
invisible(dev.off())

plt_rbs_endorsed
```

# CBCL Externalizing Problems

```{r}
file <- "data/processed/Externalizing/externalizing.csv"
df_cbcl_ep <- read_csv(file, show_col_types = FALSE)

df_cbcl_ep %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(CBCL_EP_TS), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r fig.width = 9}
df_cbcl_ep_lm <- df_cbcl_ep %>% 
  select(ID, y = CBCL_EP_TS) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_cbcl_ep <- evaluate_model(x = df_cbcl_ep_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_cbcl_ep_heatmap <- contrasts_heatmap(x = list_cbcl_ep$contrasts)

plt_cbcl_ep_heatmap <- list_cbcl_ep_heatmap$plot


plt_cbcl_ep_scatter <- regression_scatter(model = list_cbcl_ep, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          ylims = c(30, 90),
                                          ybreaks = seq(0, 100, by = 10))

plt_cbcl_ep_scatter <- plt_cbcl_ep_scatter +
labs(y = "CBCL Externalizing Problems T-score")

plt_cbcl_ep <- plt_cbcl_ep_scatter + plt_cbcl_ep_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "CBCL Externalizing Problems vs. Regression Status")

outfile <- "cbcl_ep.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"),
    height = unit(4.5, "in"))
print(plt_cbcl_ep)
invisible(dev.off())

plt_cbcl_ep
```

# CBCL Internalizing Problems

```{r}
file <- "data/processed/Internalizing/internalizing.csv"
df_cbcl_ip <- read_csv(file, show_col_types = FALSE)

df_cbcl_ip %>% 
  inner_join(df_regressive_autism %>% 
               select(ID, Language, Other),
             by = "ID") %>% 
  filter(!is.na(CBCL_IP_TS), !is.na(Language), !is.na(Other)) %>% 
  group_by(ID) %>% 
  sample_n(size = 1) %>% 
  ungroup() %>% 
  compute_group_summaries(groups = df_regressive_groups)
```

```{r fig.width = 9}
df_cbcl_ip_lm <- df_cbcl_ip %>% 
  select(ID, y = CBCL_IP_TS) %>% 
  inner_join(df_regressive_autism %>% 
              select(ID, Language, Other),
            by = "ID") %>% 
  filter(!is.na(y), !is.na(Language), !is.na(Other))

list_cbcl_ip <- evaluate_model(x = df_cbcl_ip_lm, type = "mixed-effects")

# Generate heatmap from group contrasts
list_cbcl_ip_heatmap <- contrasts_heatmap(x = list_cbcl_ip$contrasts)

plt_cbcl_ip_heatmap <- list_cbcl_ip_heatmap$plot


plt_cbcl_ip_scatter <- regression_scatter(model = list_cbcl_ip, 
                                          groups = df_regressive_groups,
                                          point_alpha_values = c(0.22, 0.4, 0.4, 0.4),
                                          ylims = c(30, 90),
                                          ybreaks = seq(0, 100, by = 10))

plt_cbcl_ip_scatter <- plt_cbcl_ip_scatter +
labs(y = "CBCL Internalizing Problems T-score")

plt_cbcl_ip <- plt_cbcl_ip_scatter + plt_cbcl_ip_heatmap +
  plot_layout(widths = c(0.7, 0.3)) +
  plot_annotation(title = "CBCL Internalizing Problems vs. Regression Status")

outfile <- "cbcl_ip.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile, 
    width = unit(10, "in"), 
    height = unit(4.5, "in"))
print(plt_cbcl_ip)
invisible(dev.off())

plt_cbcl_ip
```

# Correcting for multiple comparisons

```{r}
list_results_init <- list("Adaptive Function Composite" = list_adaptive,
                          "Social Adaptive Function" = list_adaptive_soc,
                          "Full-scale IQ" = list_IQ,
                          "ADOS CSS" = list_ADOS_CSS,
                          # "ADOS OTS" = list_ADOS_OTS,
                          "ADHD" = list_ADHD,
                          "Anxiety" = list_anxiety,
                          "Anxiety CBCL" = list_anxiety_cbcl,
                          "Anxiety RCADS" = list_anxiety_rcads,
                          "Anxiety SPENCE" = list_anxiety_spencep,
                          "Depression" = list_depression,
                          "Depression CBCL" = list_depression_cbcl,
                          "Depression RCADS" = list_depression_rcads,
                          "Sleep" = list_sleep,
                          "Seizures" = list_seizures,
                          # "Prematurity" = list_prematurity,
                          "SSP" = list_SSP_TOT,
                          "SRS" = list_SRS,
                          "SCQ" = list_scq,
                          "CCC2 Pragmatic Language" = list_lang_v1_prag,
                          "CCC2 Structural Language" = list_lang_v1_struct,
                          "CTOPP Phonological Awareness" = list_ctopp_pa,
                          "CTOPP Phonological Memory" = list_ctopp_pm,
                          "CTOPP Rapid Naming" = list_ctopp_rn,
                          "OWLS Oral Expression" = list_owls_combined_oe,
                          "OWLS Listening Comprehension" = list_owls_combined_lc,
                          "OWLS Oral Language Composite" = list_owls_combined_olc,
                          "RBS Overall" = list_rbs_all,
                          "RBS Stereotyped" = list_rbs_stt,
                          "RBS Sameness" = list_rbs_smt,
                          "RBS Self-Injurious" = list_rbs_sit,
                          "RBS Ritualistic" = list_rbs_rtt,
                          "RBS Restricted" = list_rbs_rst,
                          "RBS Compulsive" = list_rbs_cpt,
                          "RBS Endorsed" = list_rbs_endorsed,
                          "CBCL Internalizing" = list_cbcl_ip,
                          "CBCL Externalizing" = list_cbcl_ep)

list_results_all <- vector(mode = "list", length = length(list_results_init))
names(list_results_all) <- names(list_results_init)
for (i in 1:length(list_results_all)) {
  
  x <- list_results_init[[i]]$contrasts #%>% 
  type <- list_results_init[[i]]$type
  
  if (type %in% c("linear", "mixed-effects")) {
    x <- x %>% 
      select(-q.value) %>% 
      rename(ratio = t.ratio)
  } else if (type == "logistic") {
    x <- x %>% 
      select(-null, -q.value) %>% 
      rename(estimate = odds.ratio, ratio = z.ratio) 
  }
  
  x$variable <- names(list_results_all)[i]
  
  list_results_all[[i]] <- x
}

df_results_all <- bind_rows(list_results_all)

df_results_all <- df_results_all %>% 
  unite(col = "Label", Comparison, Reference, sep = " vs. ", remove = FALSE) %>% 
  mutate(Comparison = factor(Comparison, levels = c(regressive_group_lvls, "Any")),
         Reference = factor(Reference, levels = c(regressive_group_lvls, "Any")),
         variable = factor(variable, levels = names(list_results_all)))
```

## All group comparisons

```{r}
# threshold_lwr = -log10(0.05)
# threshold_upr = 10
# 
# comparison_lvls <- df_corrected %>% 
#   select(Label, Comparison, Reference) %>% 
#   distinct() %>% 
#   arrange(Reference, Comparison) %>% 
#   pull(Label)
# 
# df_corrected_1 <- df_corrected %>% 
#   filter(Label %in% comparison_lvls) %>% 
#   mutate(Label = factor(Label, levels = comparison_lvls)) %>% 
#   mutate(q.value = p.adjust(p.value, method = "fdr"),
#          NLQ = -log10(q.value)) %>% 
#   select(Label, variable, q.value, NLQ)
# 
# plt_results_1 <- ggplot(df_corrected_1, aes(x = Label, y = fct_rev(variable), fill = NLQ)) +
#   geom_tile() +
#       scale_fill_gradientn(
#       colours = c("grey80", viridis::magma(256, begin = 0.2, end = 0.9)),
#       values  = scales::rescale(c(threshold_lwr, seq(threshold_lwr + 0.001, threshold_upr, length.out = 256))),
#       limits  = c(threshold_lwr, threshold_upr),
#       oob     = scales::squish,        # forces NLQ <= thr to thr
#       na.value = "white"
#     ) +
#   scale_x_discrete(expand = expansion()) +
#   scale_y_discrete(expand = expansion()) +
#   labs(x = "Comparison",
#        y = NULL,
#        fill = "-log10(q-value)") + 
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 30, hjust = 1.0))
# 
# outfile <- "results_all_1.pdf"
# outfile <- file.path(output_dir, outfile)
# pdf(file = outfile, 
#     width = unit(7, "in"), 
#     height = unit(5, "in"))
# print(plt_results_1)
# invisible(dev.off())
# 
# plt_results_1
```

# Results table

```{r}
list_group_summaries <- vector(mode = "list", length = length(list_results_init))
names(list_group_summaries) <- names(list_results_init)
for (i in 1:length(list_group_summaries)) {
  
  if (list_results_init[[i]]$type == "mixed-effects") {
    df_i <- attributes(list_results_init[[i]]$model)$frame
  } else {
    df_i <- list_results_init[[i]]$model$model
  }
  
  df_i <- df_i %>% 
    left_join(df_regressive_groups, by = c("Language", "Other")) %>% 
    mutate(Group2 = ifelse(Group == "None", "None", "Any"))
  
  df_stats_i <- bind_rows(
    df_i %>% 
      group_by(Group) %>% 
      summarise(mean = mean(y), SD = sd(y)) %>% 
      ungroup(), 
    df_i %>% 
      group_by(Group2) %>% 
      summarise(mean = mean(y), SD = sd(y)) %>% 
      ungroup() %>% 
      rename(Group = Group2) %>% 
      filter(Group == "Any")
  )
  
  if (list_results_init[[i]]$type == "mixed-effects") {
    df_stats_i$n <- df_i %>% pull(ID) %>% unique() %>% length()
  } else {
    df_stats_i$n <- nrow(df_i)
  }
  
  list_group_summaries[[i]] <- df_stats_i
  
}

df_group_summaries <- bind_rows(list_group_summaries, .id = "measure")

```

```{r}
df_results <- df_results_all %>% 
  mutate(comparison_mean = 0, 
         comparison_sd = 0, 
         reference_mean = 0,
         reference_sd = 0,
         n = 0)

for (i in 1:nrow(df_results)) {
  
  measure_name <- df_results[[i, "variable"]]
  comparison_group <- as.character(df_results[[i, "Comparison"]])
  reference_group <- as.character(df_results[[i, "Reference"]])
  
  df_comparison_group <- df_group_summaries %>% 
    filter(measure == measure_name,
           Group == comparison_group) 
  
  df_reference_group <- df_group_summaries %>% 
    filter(measure == measure_name,
           Group == reference_group) 
  
  df_results[[i, "comparison_mean"]] <- df_comparison_group[["mean"]]
  df_results[[i, "comparison_sd"]] <- df_comparison_group[["SD"]]
  df_results[[i, "reference_mean"]] <- df_reference_group[["mean"]]
  df_results[[i, "reference_sd"]] <- df_reference_group[["SD"]]
  df_results[[i, "n"]] <- df_group_summaries %>% 
    filter(measure == measure_name) %>% 
    pull(n) %>% 
    unique()
  
}

```

## All "Any vs. None" comparisons

```{r}
df_results_export <- df_results %>%
  filter(Comparison == "Any", Reference == "None") %>% 
  arrange(variable, Reference, Comparison) %>% 
  mutate(q.value = p.adjust(p.value, method = "fdr")) %>% 
  mutate(`Comparison Group Mean (SD)` = paste0(round(comparison_mean, 2), " (", round(comparison_sd, 2), ")"),
         `Reference Group Mean (SD)` = paste0(round(reference_mean, 2), " (", round(reference_sd, 2), ")"),
         `Model Estimate (SE)` = paste0(round(estimate, 2), " (", round(SE, 2), ")")) %>% 
  select(Measure = variable, `Sample Size` = n, Contrast = Label, `Reference Group Mean (SD)`, `Comparison Group Mean (SD)`, `Model Estimate (SE)`, p.value, q.value)

df_results_export
```

```{r}
outfile <- "results.csv"
outfile <- file.path("data", outfile)
write_csv(df_results_export, outfile)
```

## Results table 1

```{r}
measures_table_1 <- c("Adaptive Function Composite", "Full-scale IQ", "ADOS CSS",
                      "ADHD", "Anxiety", "Depression", "Sleep", "Seizures", 
                      "SSP", "SRS", "SCQ", 
                      "CCC2 Pragmatic Language", "CCC2 Structural Language",
                      "RBS Overall", "RBS Endorsed", "CBCL Internalizing", "CBCL Externalizing")

df_results_table_1 <- df_results_export %>% 
  filter(Measure %in% measures_table_1) %>% 
  rename(`Non-regressive Mean (SD)` = `Reference Group Mean (SD)`,
         `Regressive Mean (SD)` = `Comparison Group Mean (SD)`) %>%  
  select(-Contrast)


outfile <- "results_table_1.csv"
outfile <- file.path("data", outfile)
write_csv(df_results_table_1, outfile)
```

## Results table 2

```{r}
df_results_table_2 <- df_results_export %>% 
  anti_join(df_results_table_1, by = "Measure") %>% 
  select(-q.value) %>% 
    rename(`Non-regressive Mean (SD)` = `Reference Group Mean (SD)`,
         `Regressive Mean (SD)` = `Comparison Group Mean (SD)`) %>%  
  select(-Contrast)


outfile <- "results_table_2.csv"
outfile <- file.path("data", outfile)
write_csv(df_results_table_2, outfile)
```
