---
title: "Regressive Autism Analysis"
author: "Antoine Beauchamp"
format: html
editor: visual
---

# Initialization

```{r packages}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(patchwork))
suppressPackageStartupMessages(library(rcartocolor))
suppressPackageStartupMessages(library(RColorBrewer))
```

```{r functions}
bootstrap_sample_estimate <- function(x, groups = NULL, estimate = "mean", B = 1000, set_seed = TRUE) {
  
  if (estimate == "mean") {
    estimator <- mean
  } else if (estimate == "median") {
    estimator <- median
  } else if (estimate == "sd") {
    estimator <- sd
  } else {
    stop()
  }
  
  n_groups <- ifelse(is.null(groups), 1, length(unique(groups)))
  if (n_groups > 1) {
    if (!is.factor(groups)) {
      stop("groups must be factor")
    }
  }
  groups_lvls <- levels(groups)
  
  bootstrap_samples <- matrix(data = 0, nrow = B, ncol = n_groups)
  colnames(bootstrap_samples) <- groups_lvls
  for (i in 1:nrow(bootstrap_samples)) {
    if (n_groups == 1) {
      if (set_seed) {set.seed(i)}
      bootstrap_samples[[i]] <- estimator(sample(x = x, size = length(x), 
                                                 replace = TRUE))
    } else {
      x_split <- split(x = x, f = groups)
      n_split <- lapply(x_split, length)
      if (set_seed) {set.seed(i)}
      x_split_sample <- mapply(FUN = sample, x = x_split, size = n_split, 
                               MoreArgs = list(replace = TRUE))
      bootstrap_samples[i,] <- sapply(X = x_split_sample, FUN = estimator)
    }
  }
  
  return(bootstrap_samples)
  
}

bootstrap_sample_estimate_ci <- function(x, groups = NULL, estimate = "mean", 
                                         interval = c(0.025, 0.975), B = 1000, 
                                         set_seed = TRUE) {
  bootstrap_samples <- bootstrap_sample_estimate(x = x, groups = groups, estimate = estimate,
                                                 B = B, set_seed = set_seed)
  bootstrap_ci <- apply(bootstrap_samples, MARGIN = 2, quantile, interval)
  bootstrap_ci <- t(bootstrap_ci)
  colnames(bootstrap_ci) <- c("lower", "upper")
  return(bootstrap_ci)
}

group_summary <- function(x, groups, B = 1000) {
  
  means <- split(x = x, f = groups) %>% 
    sapply(mean) %>% 
    matrix(ncol = 1, nrow = length(levels(groups)))
  colnames(means) <- "mu"
  
  ci <- bootstrap_sample_estimate_ci(x = x, groups = groups, B = B)
  
  out <- cbind(means, ci)
  rownames(out) <- levels(groups)
  
  return(out)
  
}
```

```{r import}
# Path to processed data directory
data_dir <- "data/processed/"

output_dir <- "figures"

# Import processed data
data_file <- "regressive_autism_data_bool.csv"
data_file <- file.path(data_dir, data_file)
df_regressive_autism <- read_csv(data_file, show_col_types = FALSE)
df_regressive_autism
```

# Analysis

## Regressive autism numbers

```{r regressive-autism-numbers}
n_total <- nrow(df_regressive_autism)

# Compute sample sizes for the different regressive groups
df_regressive_autism_numbers <- df_regressive_autism %>% 
  select(ID, starts_with("Regressive")) %>% 
  column_to_rownames("ID") %>% 
  as.matrix() %>% 
  colSums() %>% 
  enframe(name = "Group", value = "Number") %>% 
  mutate(Group = str_remove(Group, "Regressive_"),
         Group = str_replace(Group, "_", " ")) %>% 
  mutate(Proportion = round(Number/n_total, 3)) %>% 
  bind_rows(tibble(Group = "Total", Number = n_total, Proportion = 1))

# Export to file
outfile <- "regressive_autism_numbers.csv"
outfile <- file.path("data", outfile)
write_csv(x = df_regressive_autism_numbers, file = outfile)
```

## Association between adaptive function and regressive status

```{r adaptive-function-model}
# Filter for participants with adaptive function scores
df_adaptive <- df_regressive_autism %>% 
  select(ID, contains("Regressive"), AdaptiveScore) %>% 
  filter(!is.na(AdaptiveScore))

# Filter participants with no regression. This will serve as the control group
df_adaptive_non_regressive <- df_adaptive %>%
  filter(Regressive_None) %>% 
  select(ID, AdaptiveScore) %>% 
  mutate(Regressive = FALSE)

# Regression group columns to include
cols_regressive <- c("Regressive_Strictly_Language", "Regressive_Strictly_Other", 
                     "Regressive_Both", "Regressive_Any")
list_adaptive_models <- vector(mode = "list", length = length(cols_regressive))
names(list_adaptive_models) <- c("Language", "Other", "Both", "Any")
for (i in 1:length(cols_regressive)) {
  
  # Extract filter for regressive group
  idx <- df_adaptive[[cols_regressive[i]]]
  
  # Filter rows and subset columns
  cols_subset <- c("ID", "AdaptiveScore", cols_regressive[i])
  df_adaptive_regressive <- df_adaptive[idx, cols_subset]
  colnames(df_adaptive_regressive) <- c("ID", "AdaptiveScore", "Regressive")
  
  # Bind case and control data frames
  df_adaptive_model <- bind_rows(df_adaptive_regressive, 
                                 df_adaptive_non_regressive)
  
  # Fit linear model
  adaptive_model <- lm(AdaptiveScore ~ Regressive, data = df_adaptive_model)
  
  # Save outputs
  list_adaptive_models[[i]] <- list(data = df_adaptive_model,
                                    model = broom::tidy(adaptive_model))
  
}
```

```{r adaptive-function-plot}
annotation_y <- 135

# adaptive_titles <- c("Language regressive", 
#                      "Other skill regressive", 
#                      "Language and other skill regressive",
#                      "Language or other skill regressive")
adaptive_titles <- c("Language", 
                     "Other skill", 
                     "Language and other skill",
                     "Language or other skill")

list_adaptive_plts <- vector(mode = "list", length = length(list_adaptive_models))
names(list_adaptive_plts) <- names(list_adaptive_models)
for (i in 1:length(list_adaptive_plts)) {
  
  df_adaptive_plt <- list_adaptive_models[[i]][["data"]]
  
    df_adaptive_plt <- df_adaptive_plt %>% 
    mutate(Regressive = ifelse(Regressive, "Yes", "No"),
           Regressive = factor(Regressive))
  
  df_adaptive_plt_summary <- group_summary(x = df_adaptive_plt$AdaptiveScore, 
                                       groups = df_adaptive_plt$Regressive)
  df_adaptive_plt_summary <- df_adaptive_plt_summary %>% 
    as_tibble(rownames = "Regressive") %>% 
    mutate(Regressive = factor(Regressive))
  
  df_adaptive_annotation <- list_adaptive_models[[i]][["model"]] %>% 
    filter(term == "RegressiveTRUE") %>% 
    mutate(p.label = ifelse(p.value < 0.001, 
                            "p < 0.001", paste0("p = ", round(p.value, 3))),
           t.label = as.character(round(statistic, 2)),
           t.label = paste0("t = ", t.label)) %>% 
    select(p.label, t.label) %>% 
    pivot_longer(cols = c("p.label", "t.label"), 
                 names_to = "statistic", 
                 values_to = "label") %>% 
    mutate(x = 1.5, y = ifelse(statistic == "p.label", 
                               annotation_y + 4, annotation_y + 9))  
  
  set.seed(123)
  plt_adaptive <- ggplot(df_adaptive_plt, aes(x = Regressive, y = AdaptiveScore)) +
    geom_jitter(size = 1, width = 0.3, height = 0, alpha = 0.15, col = "grey20") + 
        geom_crossbar(data = df_adaptive_plt_summary, 
                  mapping = aes(x = Regressive, y = mu, ymin = lower, ymax = upper),
                  alpha = 0.1, col = "red3", fill = "red3") + 
    # geom_boxplot(alpha = 0.1, outliers = FALSE, col = "red3", fill = "red3") +
    annotate(geom = "segment", x = "No", xend = "Yes", y = annotation_y, color = "grey40") +
    geom_text(data = df_adaptive_annotation, aes(x = x, y = y, label = label),
              size = 3.5, color = "grey30") +
    coord_cartesian(ylim = c(20, 145)) + 
    scale_x_discrete(labels = c("Non-regressive", "Regressive")) +
    scale_y_continuous(breaks = seq(0, 200, by = 10)) + 
    labs(x = NULL,
         y = "Adaptive Function Composite Score",
         title = adaptive_titles[i]) + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  if (i > 1) {
    plt_adaptive <- plt_adaptive +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }
  
  list_adaptive_plts[[i]] <- plt_adaptive
}


fig_adaptive <- list_adaptive_plts[[1]] | list_adaptive_plts[[2]] | list_adaptive_plts[[3]] | list_adaptive_plts[[4]]

outfile <- "adaptive_function.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(8, "in"),
    height = unit(6, "in"))
print(fig_adaptive)
dev.off()
```

## Association between IQ and regressive status

```{r IQ-model}
# Filter for participants with IQ scores
df_IQ <- df_regressive_autism %>% 
  select(ID, contains("Regressive"), IQ) %>% 
  filter(!is.na(IQ))

# Filter participants with no regression. This will serve as the control group
df_IQ_non_regressive <- df_IQ %>%
  filter(Regressive_None) %>% 
  select(ID, IQ) %>% 
  mutate(Regressive = FALSE)

# Regression group columns to include
cols_regressive <- c("Regressive_Strictly_Language", "Regressive_Strictly_Other", 
                     "Regressive_Both", "Regressive_Any")
list_IQ_models <- vector(mode = "list", length = length(cols_regressive))
names(list_IQ_models) <- c("Language", "Other", "Both", "Any")
for (i in 1:length(cols_regressive)) {
  
  # Extract filter for regressive group
  idx <- df_IQ[[cols_regressive[i]]]
  
  # Filter rows and subset columns
  cols_subset <- c("ID", "IQ", cols_regressive[i])
  df_IQ_regressive <- df_IQ[idx, cols_subset]
  colnames(df_IQ_regressive) <- c("ID", "IQ", "Regressive")
  
  # Bind case and control data frames
  df_IQ_model <- bind_rows(df_IQ_regressive, 
                                 df_IQ_non_regressive)
  
  # Fit linear model
  IQ_model <- lm(IQ ~ Regressive, data = df_IQ_model)
  
  # Save outputs
  list_IQ_models[[i]] <- list(data = df_IQ_model,
                                    model = broom::tidy(IQ_model))
  
}
```

```{r IQ-plot}
annotation_y <- 160

# IQ_titles <- c("Language regressive", 
#                      "Other skill regressive", 
#                      "Language and other skill regressive",
#                      "Language or other skill regressive")
IQ_titles <- c("Language", 
               "Other skill", 
               "Language and other skill",
               "Language or other skill")

list_IQ_plts <- vector(mode = "list", length = length(list_IQ_models))
names(list_IQ_plts) <- names(list_IQ_models)
for (i in 1:length(list_IQ_plts)) {
  
  df_IQ_plt <- list_IQ_models[[i]][["data"]]
  
    df_IQ_plt <- df_IQ_plt %>% 
    mutate(Regressive = ifelse(Regressive, "Yes", "No"),
           Regressive = factor(Regressive))
  
  df_IQ_plt_summary <- group_summary(x = df_IQ_plt$IQ, 
                                       groups = df_IQ_plt$Regressive)
  df_IQ_plt_summary <- df_IQ_plt_summary %>% 
    as_tibble(rownames = "Regressive") %>% 
    mutate(Regressive = factor(Regressive))
  
  df_IQ_annotation <- list_IQ_models[[i]][["model"]] %>% 
    filter(term == "RegressiveTRUE") %>% 
    mutate(p.label = ifelse(p.value < 0.001, 
                            "p < 0.001", paste0("p = ", round(p.value, 3))),
           t.label = as.character(round(statistic, 2)),
           t.label = paste0("t = ", t.label)) %>% 
    select(p.label, t.label) %>% 
    pivot_longer(cols = c("p.label", "t.label"), 
                 names_to = "statistic", 
                 values_to = "label") %>% 
    mutate(x = 1.5, y = ifelse(statistic == "p.label", 
                               annotation_y + 4, annotation_y + 9))  
  
  set.seed(123)
  plt_IQ <- ggplot(df_IQ_plt, aes(x = Regressive, y = IQ)) +
    geom_jitter(size = 1, width = 0.3, height = 0, alpha = 0.2, col = "grey20") + 
        geom_crossbar(data = df_IQ_plt_summary, 
                  mapping = aes(x = Regressive, y = mu, ymin = lower, ymax = upper),
                  alpha = 0.1, col = "red3", fill = "red3") + 
    # geom_boxplot(alpha = 0.1, outliers = FALSE, col = "red3", fill = "red3") +
    annotate(geom = "segment", x = "No", xend = "Yes", y = annotation_y, color = "grey40") +
    geom_text(data = df_IQ_annotation, aes(x = x, y = y, label = label),
              size = 3.5, color = "grey30") +
    coord_cartesian(ylim = c(40, 170)) + 
    scale_x_discrete(labels = c("Non-regressive", "Regressive")) +
    scale_y_continuous(breaks = seq(0, 200, by = 10)) + 
    labs(x = NULL,
         y = "Full-Scale IQ",
         title = IQ_titles[i]) + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  if (i > 1) {
    plt_IQ <- plt_IQ +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }
  
  list_IQ_plts[[i]] <- plt_IQ
}


fig_IQ <- list_IQ_plts[[1]] | list_IQ_plts[[2]] | list_IQ_plts[[3]] | list_IQ_plts[[4]]

outfile <- "IQ.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(8, "in"),
    height = unit(6, "in"))
print(fig_IQ)
dev.off()
```

## Association between ADOS and regressive status

```{r}
nrow(df_regressive_autism)
```

There are 5,682 participants

```{r}
sum(!is.na(df_regressive_autism$ADOS))
```

3,616 participants have ADOS scores

```{r}
df_regressive_autism %>% 
  filter(!is.na(ADOS)) %>% 
  mutate(ADOS_zero = ADOS == 0) %>% 
  group_by(ADOS_zero) %>% 
  count()
```

3,227 participants have non-zero ADOS scores 389 have zero scores

### Association with zeros included

```{r ados-model}
# Filter for participants with ADOS scores
df_ADOS <- df_regressive_autism %>% 
  select(ID, contains("Regressive"), ADOS) %>% 
  filter(!is.na(ADOS))

# Filter participants with no regression. This will serve as the control group
df_ADOS_non_regressive <- df_ADOS %>%
  filter(Regressive_None) %>% 
  select(ID, ADOS) %>% 
  mutate(Regressive = FALSE)

# Regression group columns to include
cols_regressive <- c("Regressive_Strictly_Language", "Regressive_Strictly_Other", 
                     "Regressive_Both", "Regressive_Any")
list_ADOS_models <- vector(mode = "list", length = length(cols_regressive))
names(list_ADOS_models) <- c("Language", "Other", "Both", "Any")
for (i in 1:length(cols_regressive)) {
  
  # Extract filter for regressive group
  idx <- df_ADOS[[cols_regressive[i]]]
  
  # Filter rows and subset columns
  cols_subset <- c("ID", "ADOS", cols_regressive[i])
  df_ADOS_regressive <- df_ADOS[idx, cols_subset]
  colnames(df_ADOS_regressive) <- c("ID", "ADOS", "Regressive")
  
  # Bind case and control data frames
  df_ADOS_model <- bind_rows(df_ADOS_regressive, 
                             df_ADOS_non_regressive)
  
  # Fit linear model
  ADOS_model <- lm(ADOS ~ Regressive, data = df_ADOS_model)
  
  # Save outputs
  list_ADOS_models[[i]] <- list(data = df_ADOS_model,
                                model = broom::tidy(ADOS_model))
  
}
```

```{r ados-plot}
annotation_y <- 30

# adaptive_titles <- c("Language regressive", 
#                      "Other skill regressive", 
#                      "Language and other skill regressive",
#                      "Language or other skill regressive")
ADOS_titles <- c("Language", 
                     "Other skill", 
                     "Language and other skill",
                     "Language or other skill")

list_ADOS_plts <- vector(mode = "list", length = length(list_ADOS_models))
names(list_ADOS_plts) <- names(list_ADOS_models)
for (i in 1:length(list_ADOS_plts)) {

  df_ADOS_plt <- list_ADOS_models[[i]][["data"]] 
  
  df_ADOS_plt <- df_ADOS_plt %>% 
    mutate(Regressive = ifelse(Regressive, "Yes", "No"),
           Regressive = factor(Regressive))
  
  df_ADOS_plt_summary <- group_summary(x = df_ADOS_plt$ADOS, 
                                       groups = df_ADOS_plt$Regressive)
  df_ADOS_plt_summary <- df_ADOS_plt_summary %>% 
    as_tibble(rownames = "Regressive") %>% 
    mutate(Regressive = factor(Regressive))

df_ADOS_annotation <- list_ADOS_models[[i]][["model"]] %>% 
    filter(term == "RegressiveTRUE") %>% 
    mutate(p.label = ifelse(p.value < 0.001, 
                            "p < 0.001", paste0("p = ", round(p.value, 3))),
           t.label = as.character(round(statistic, 2)),
           t.label = paste0("t = ", t.label)) %>% 
    select(p.label, t.label) %>% 
    pivot_longer(cols = c("p.label", "t.label"), 
                 names_to = "statistic", 
                 values_to = "label") %>% 
    mutate(x = 1.5, y = ifelse(statistic == "p.label", 
                               annotation_y + 1, annotation_y + 2.5))  
  
  set.seed(123)
  plt_ADOS <- ggplot(df_ADOS_plt, aes(x = Regressive, y = ADOS)) +
    geom_jitter(size = 1, width = 0.3, height = 0, alpha = 0.15, col = "grey20") + 
    geom_crossbar(data = df_ADOS_plt_summary, 
                  mapping = aes(x = Regressive, y = mu, ymin = lower, ymax = upper),
                  alpha = 0.1, col = "red3", fill = "red3") + 
    # geom_boxplot(alpha = 0.1, outliers = FALSE, col = "red3", fill = "red3") +
    annotate(geom = "segment", x = "No", xend = "Yes", y = annotation_y, color = "grey40") +
    geom_text(data = df_ADOS_annotation, aes(x = x, y = y, label = label),
              size = 3.5, color = "grey30") +
    coord_cartesian(ylim = c(0, 35)) + 
    scale_x_discrete(labels = c("Non-regressive", "Regressive")) +
    scale_y_continuous(breaks = seq(0, 200, by = 10)) + 
    labs(x = NULL,
         y = "ADOS Overall Total Score",
         title = ADOS_titles[i]) + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  if (i > 1) {
    plt_ADOS <- plt_ADOS +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }
  
  list_ADOS_plts[[i]] <- plt_ADOS
  
}


fig_ADOS <- list_ADOS_plts[[1]] | list_ADOS_plts[[2]] | list_ADOS_plts[[3]] | list_ADOS_plts[[4]]

outfile <- "ADOS_regression_with_zeros.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(8, "in"),
    height = unit(6, "in"))
print(fig_ADOS)
dev.off()
```

### Association with zeros excluded

```{r ados-model}
# Filter for participants with ADOS scores
df_ADOS <- df_regressive_autism %>% 
  select(ID, contains("Regressive"), ADOS) %>% 
  filter(!is.na(ADOS))

df_ADOS <- df_ADOS %>% 
  filter(ADOS > 0)

# Filter participants with no regression. This will serve as the control group
df_ADOS_non_regressive <- df_ADOS %>%
  filter(Regressive_None) %>% 
  select(ID, ADOS) %>% 
  mutate(Regressive = FALSE)

# Regression group columns to include
cols_regressive <- c("Regressive_Strictly_Language", "Regressive_Strictly_Other", 
                     "Regressive_Both", "Regressive_Any")
list_ADOS_models <- vector(mode = "list", length = length(cols_regressive))
names(list_ADOS_models) <- c("Language", "Other", "Both", "Any")
for (i in 1:length(cols_regressive)) {
  
  # Extract filter for regressive group
  idx <- df_ADOS[[cols_regressive[i]]]
  
  # Filter rows and subset columns
  cols_subset <- c("ID", "ADOS", cols_regressive[i])
  df_ADOS_regressive <- df_ADOS[idx, cols_subset]
  colnames(df_ADOS_regressive) <- c("ID", "ADOS", "Regressive")
  
  # Bind case and control data frames
  df_ADOS_model <- bind_rows(df_ADOS_regressive, 
                             df_ADOS_non_regressive)
  
  # Fit linear model
  ADOS_model <- lm(ADOS ~ Regressive, data = df_ADOS_model)
  
  # Save outputs
  list_ADOS_models[[i]] <- list(data = df_ADOS_model,
                                model = broom::tidy(ADOS_model))
  
}
```

```{r ados-plot}
annotation_y <- 30

# adaptive_titles <- c("Language regressive", 
#                      "Other skill regressive", 
#                      "Language and other skill regressive",
#                      "Language or other skill regressive")
ADOS_titles <- c("Language", 
                     "Other skill", 
                     "Language and other skill",
                     "Language or other skill")

list_ADOS_plts <- vector(mode = "list", length = length(list_ADOS_models))
names(list_ADOS_plts) <- names(list_ADOS_models)
for (i in 1:length(list_ADOS_plts)) {

  df_ADOS_plt <- list_ADOS_models[[i]][["data"]] 
  
  df_ADOS_plt <- df_ADOS_plt %>% 
    mutate(Regressive = ifelse(Regressive, "Yes", "No"),
           Regressive = factor(Regressive))
  
  df_ADOS_plt_summary <- group_summary(x = df_ADOS_plt$ADOS, 
                                       groups = df_ADOS_plt$Regressive)
  df_ADOS_plt_summary <- df_ADOS_plt_summary %>% 
    as_tibble(rownames = "Regressive") %>% 
    mutate(Regressive = factor(Regressive))

df_ADOS_annotation <- list_ADOS_models[[i]][["model"]] %>% 
    filter(term == "RegressiveTRUE") %>% 
    mutate(p.label = ifelse(p.value < 0.001, 
                            "p < 0.001", paste0("p = ", round(p.value, 3))),
           t.label = as.character(round(statistic, 2)),
           t.label = paste0("t = ", t.label)) %>% 
    select(p.label, t.label) %>% 
    pivot_longer(cols = c("p.label", "t.label"), 
                 names_to = "statistic", 
                 values_to = "label") %>% 
    mutate(x = 1.5, y = ifelse(statistic == "p.label", 
                               annotation_y + 1, annotation_y + 2.5))  
  
  set.seed(123)
  plt_ADOS <- ggplot(df_ADOS_plt, aes(x = Regressive, y = ADOS)) +
    geom_jitter(size = 1, width = 0.3, height = 0, alpha = 0.15, col = "grey20") + 
    geom_crossbar(data = df_ADOS_plt_summary, 
                  mapping = aes(x = Regressive, y = mu, ymin = lower, ymax = upper),
                  alpha = 0.1, col = "red3", fill = "red3") + 
    # geom_boxplot(alpha = 0.1, outliers = FALSE, col = "red3", fill = "red3") +
    annotate(geom = "segment", x = "No", xend = "Yes", y = annotation_y, color = "grey40") +
    geom_text(data = df_ADOS_annotation, aes(x = x, y = y, label = label),
              size = 3.5, color = "grey30") +
    coord_cartesian(ylim = c(0, 35)) + 
    scale_x_discrete(labels = c("Non-regressive", "Regressive")) +
    scale_y_continuous(breaks = seq(0, 200, by = 10)) + 
    labs(x = NULL,
         y = "ADOS Overall Total Score",
         title = ADOS_titles[i]) + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  if (i > 1) {
    plt_ADOS <- plt_ADOS +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }
  
  list_ADOS_plts[[i]] <- plt_ADOS
  
}


fig_ADOS <- list_ADOS_plts[[1]] | list_ADOS_plts[[2]] | list_ADOS_plts[[3]] | list_ADOS_plts[[4]]

outfile <- "ADOS_regression_nonzero.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(8, "in"),
    height = unit(6, "in"))
print(fig_ADOS)
dev.off()
```

```{r}
tmp <- df_regressive_autism |> 
  filter(!is.na(ADOS)) |> 
  mutate(ADOS_zero = ADOS == 0)


tmp %>% 
  group_by(ADOS_zero, Regressive_Strictly_Language) %>% 
  count()
```

```{r}
chisq.test(x = tmp$Regressive_Strictly_Language, y = tmp$ADOS_zero)
```

```{r}
chisq.test(x = tmp$Regressive_Strictly_Other, y = tmp$ADOS_zero)
```

```{r}
cols_regressive <- c("Regressive_Strictly_Language", "Regressive_Strictly_Other", 
                     "Regressive_Both", "Regressive_Any")
df_ADOS_zeros_chi2 <- tibble(regression = cols_regressive,
                             chi2 = 0, pval = 0)
for (i in 1:nrow(df_ADOS_zeros_chi2)) {
  
  x <- tmp[[cols_regressive[i]]]
  y <- tmp[["ADOS_zero"]]
  
  chisq_out <- chisq.test(x = x, y = y, simulate.p.value = TRUE, B = 5000)
  
  df_ADOS_zeros_chi2[[i, "chi2"]] <- chisq_out$statistic
  df_ADOS_zeros_chi2[[i, "pval"]] <- chisq_out$p.value
  
}

df_ADOS_zeros_chi2
```

```{r ados-plot}
annotation_y <- 0.95

# adaptive_titles <- c("Language regressive", 
#                      "Other skill regressive", 
#                      "Language and other skill regressive",
#                      "Language or other skill regressive")
ADOS_titles <- c("Language", 
                     "Other skill", 
                     "Language and other skill",
                     "Language or other skill")

list_ADOS_zero_plts <- vector(mode = "list", length = nrow(df_ADOS_zeros_chi2))
for (i in 1:length(list_ADOS_zero_plts)) {
  
  cols <- c("ID", cols_regressive[i], "ADOS_zero")
  df_ADOS_zero_plt <- tmp[,cols]
  colnames(df_ADOS_zero_plt) <- c("ID", "Regressive", "ADOS_zero")
  
  # df_ADOS_zero_plt <- df_ADOS_zero_plt %>% 
  #   group_by(Regressive, ADOS_zero) %>% 
  #   count() %>% 
  #   ungroup() %>% 
  #   mutate(ADOS_nonzero = !ADOS_zero)
  
    df_ADOS_zero_plt <- df_ADOS_zero_plt %>% 
    group_by(Regressive) %>% 
    mutate(n_per_group = n()) %>% 
    ungroup() %>% 
    group_by(Regressive, ADOS_zero) %>%  
    mutate(n_per_zero_per_group = n()) %>%  
    ungroup() %>% 
    mutate(prop_per_zero_per_group = n_per_zero_per_group/n_per_group) %>% 
    mutate(ADOS_nonzero = !ADOS_zero) %>% 
    select(Regressive, ADOS_nonzero, n_per_group, n_per_zero_per_group, prop_per_zero_per_group) %>% 
    distinct() %>% 
    arrange(Regressive, ADOS_nonzero)
  
  df_ADOS_zero_annotation <- df_ADOS_zeros_chi2[i, ] %>% 
        mutate(p.label = ifelse(pval < 0.001, 
                            "p < 0.001", paste0("p = ", round(pval, 3)))) %>% 
    select(p.label) %>% 
    mutate(x = 1.5, y = annotation_y + 0.04)

  plt_ADOS_zero <- ggplot(df_ADOS_zero_plt, aes(x = Regressive, fill = ADOS_nonzero, y = prop_per_zero_per_group)) + 
    geom_col(position = "dodge") +
      annotate(geom = "segment", x = FALSE, xend = TRUE, y = annotation_y, color = "grey40") +
    geom_text(data = df_ADOS_zero_annotation, aes(x = x, y = y, label = p.label),
              inherit.aes = FALSE, 
              size = 3.5, color = "grey30") +
    scale_x_discrete(labels = c("Non-regressive", "Regressive")) +
    scale_fill_discrete(labels = c("ADOS = 0", "ADOS > 0")) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
    labs(x = NULL,
         y = "Proportion of participants per regression group",
         fill = NULL, 
         title = ADOS_titles[i]) + 
    theme_bw() +
    theme(title = element_text(size = 9, hjust = 0.5))
  
  
  if (i > 1) {
    plt_ADOS_zero <- plt_ADOS_zero +
      theme(axis.title.y = element_blank(),
            axis.text.y = element_blank(),
            axis.ticks.y = element_blank())
  }
  
  list_ADOS_zero_plts[[i]] <- plt_ADOS_zero
  
}

fig_ADOS_zero <- (list_ADOS_zero_plts[[1]] | list_ADOS_zero_plts[[2]] | list_ADOS_zero_plts[[3]] | list_ADOS_zero_plts[[4]]) +
  plot_layout(guides = "collect")

outfile <- "ADOS_zero_regression.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(10, "in"),
    height = unit(6, "in"))
print(fig_ADOS_zero)
dev.off()
```

```{r}
  cols <- c("ID", cols_regressive[i], "ADOS_zero")
  df_ADOS_zero_plt <- tmp[,cols]
  colnames(df_ADOS_zero_plt) <- c("ID", "Regressive", "ADOS_zero")
  
  df_ADOS_zero_plt %>% 
    group_by(Regressive) %>% 
    mutate(n_per_group = n()) %>% 
    ungroup() %>% 
    group_by(Regressive, ADOS_zero) %>%  
    mutate(n_per_zero_per_group = n()) %>%  
    ungroup() %>% 
    mutate(prop_per_zero_per_group = n_per_zero_per_group/n_per_group) %>% 
    mutate(ADOS_nonzero = !ADOS_zero) %>% 
    select(Regressive, ADOS_nonzero, n_per_group, n_per_zero_per_group, prop_per_zero_per_group) %>% 
    distinct() %>% 
    arrange(Regressive, ADOS_nonzero)
```

```{r}
tmp_adaptive <- tmp %>% 
  filter(!is.na(AdaptiveScore)) %>% 
  mutate(ADOS_zero = ifelse(ADOS_zero, "Yes", "No"),
         ADOS_zero = factor(ADOS_zero))

model_ADOS_zero_adaptive <- summary(lm(AdaptiveScore ~ ADOS_zero, data = tmp_adaptive))

df_ADOS_zero_adaptive_summary <- group_summary(tmp_adaptive$AdaptiveScore,
                                               groups = tmp_adaptive$ADOS_zero)
df_ADOS_zero_adaptive_summary <- df_ADOS_zero_adaptive_summary %>% 
  as_tibble(rownames = "ADOS_zero") %>% 
  mutate(ADOS_zero = factor(ADOS_zero))


set.seed(123)
plt_ADOS_zero_adaptive <- ggplot(tmp_adaptive, aes(x = ADOS_zero, y = AdaptiveScore)) +
  geom_jitter(size = 1, width = 0.3, height = 0, alpha = 0.4, col = "grey20") + 
  geom_crossbar(data = df_ADOS_zero_adaptive_summary, 
                mapping = aes(x = ADOS_zero, y = mu, ymin = lower, ymax = upper),
                alpha = 0.1, col = "red3", fill = "red3") + 
  annotate(geom = "segment", x = "No", xend = "Yes", y = 135, color = "grey40") +
  annotate(geom = "text", x = 1.5, y = 140, label = "p < 0.001") + 
  scale_x_discrete(labels = c("ADOS > 0", "ADOS = 0")) +
  scale_y_continuous(breaks = seq(0, 200, by = 10)) +
  labs(x = "Binarized ADOS score",
       y = "Adaptive Function Composite Score") + 
  theme_bw() 

outfile <- "ADOS_zero_adaptive_function.pdf"
outfile <- file.path(output_dir, outfile)
pdf(file = outfile,
    width = unit(6, "in"),
    height = unit(6, "in"))
print(plt_ADOS_zero_adaptive)
dev.off()
```

```{r}
tmp_IQ <- tmp %>% 
  filter(!is.na(IQ)) %>% 
  mutate(ADOS_zero = ifelse(ADOS_zero, "Yes", "No"),
         ADOS_zero = factor(ADOS_zero))

tmp_IQ %>% 
  group_by(ADOS_zero) %>% 
  count()
```

Only 14 people with 0 on ADOS and IQ scores.

```{r}
tmp_IQ %>% 
  filter(ADOS_zero == "Yes") %>% 
  select(IQ) %>% 
  arrange(desc(IQ))
```

The scores that do exist are low.

### ADI-R autism diagnosis

```{r}
path_ADIR <- "data/raw/ADI-R/"

file_ADIR_dx_1995 <- "ADI1995_ADIAFFT_all_cutoff.xlsx"
file_ADIR_dx_1995 <- file.path(path_ADIR, file_ADIR_dx_1995)
df_ADIR_dx_1995 <- read_excel(path = file_ADIR_dx_1995)

file_ADIR_dx_wps <- "ADIWPS_ADIAFFT_all_cutoff.xlsx"
file_ADIR_dx_wps <- file.path(path_ADIR, file_ADIR_dx_wps)
df_ADIR_dx_wps <- read_excel(path = file_ADIR_dx_wps)

df_ADIR_dx_1995 <- df_ADIR_dx_1995 %>% 
  anti_join(df_ADIR_dx_wps, by = "indexid")

df_ADIR_dx <- bind_rows(df_ADIR_dx_1995 %>% 
                          select(ID = indexid, score = numeric_value),
                        df_ADIR_dx_wps %>% 
                          select(ID = indexid, score = numeric_value))

df_ADIR_dx
```

```{r}
df_ADOS <- df_regressive_autism %>% 
  select(ID, contains("Regressive"), ADOS) %>% 
  filter(!is.na(ADOS))

df_ADOS_zeros <- df_ADOS %>% 
  filter(ADOS == 0)

df_ADOS_zeros <- df_ADOS_zeros %>% 
  left_join(df_ADIR_dx, by = "ID") %>% 
  select(ID, ADOS, score)

df_ADOS_zeros %>% 
  filter(!is.na(score)) %>% 
  nrow()
```

```{r}
df_ADOS_zeros %>% 
  filter(!is.na(score)) %>% 
  group_by(score) %>% 
  count()
```

```{r}
nrow(df_ADOS)
```

389 participants with ADOS = 0 312 participants with missing ADI-R cutoff. How does that make sense? 70 with cutoff of 4

```{r}
df_ADOS_zeros_missing <- df_ADOS_zeros %>% 
  filter(is.na(score))
```

```{r}
df_ADOS_zeros_missing <- df_ADOS_zeros %>% 
  filter(is.na(score)) %>% 
  select(ID, ADOS)

path_ADIR <- "data/raw/ADI-R/"

files <- c("Onset"="ADIWPS_ADIAFAB_cuttoff_1.xlsx",
           "RRB"="ADIWPS_ADIAFBEH_cuttoff_3.xlsx",
           "Communication"="ADIWPS_ADIAFCOM_cutoff_7-8.xlsx",
           "Social"="ADIWPS_ADIAFSOC_cutoff_10.xlsx")

for (i in 1:length(files)) {
  file <- file.path(path_ADIR, files[i])
  
  df <- read_excel(file)
  
  df <- df %>% 
    select(ID = indexid, cutoff = numeric_value) %>% 
    mutate(cutoff = cutoff == 1)
  
  colnames(df) <- c("ID", paste0("Cutoff_", names(files)[i]))
  
  df_ADOS_zeros_missing <- df_ADOS_zeros_missing %>% 
    left_join(df, by = "ID")
}
```

```{r}
rows_num_missing <- df_ADOS_zeros_missing %>% 
  select(starts_with("Cutoff")) %>% 
  as.matrix() %>% 
  is.na() %>% 
  rowSums() 

idx_missing <- rows_num_missing == 4

sum(idx_missing)
```

87 of the 312 have no data here.

Of the remaining 225:

```{r}
df_ADOS_zeros_missing_with_cutoffs <- df_ADOS_zeros_missing[!idx_missing,]
df_ADOS_zeros_missing_with_cutoffs <- df_ADOS_zeros_missing_with_cutoffs %>% 
  mutate(n_cutoffs = Cutoff_Onset + Cutoff_RRB + Cutoff_Communication + Cutoff_Social)

df_ADOS_zeros_missing_with_cutoffs %>% 
  group_by(n_cutoffs) %>% 
  count()
```

```{r}
df_ADOS_zeros_missing_with_cutoffs %>% 
  filter(n_cutoffs == 3)
```

```{r}
df_ADOS_zeros_missing_with_cutoffs %>% 
  filter(n_cutoffs == 2)
```

```{r}
df_ADOS_zeros_missing_with_cutoffs %>% 
  filter(n_cutoffs == 1)
```

```{r}
df_ADOS_zeros_missing_with_cutoffs %>% 
  filter(n_cutoffs == 4) %>% 
  left_join(df_ADIR_dx, by = "ID")
```

```{r}
df_ADOS_zeros_missing[idx_missing,]
```
